---
title: "MAIN-MARSHAL"
format: html
editor: visual
---

```{r, include=FALSE}
# knitr::opts_chunk$set(echo = FALSE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # Set working directory to the current file

options(rstudio.help.showDataPreview = FALSE)
MPath <- "./CRB-MARSHAL/"

libs <- c("fmsb", "SciViews", "pander", "visreg", "readxl", "EnvStats", "FactoMineR", "factoextra", "knitr", "data.table", "reticulate", "xml2", "tidyverse", "dplyr", "viridis", "Hmisc", "ggplot2", "gridExtra", "outliers", "Matrix", "emmeans")

for(pk in libs) {
  library(pk, character.only = T)
}

# Custom functions
rm(list = ls()) # clean worshop


MPath <- "./CRB-MARSHAL/"

source(paste0(MPath,"inputs/io_function.R")) # CROOTBOX
source(paste0(MPath, "Get_SUF.R")) # MARSHAL
source(paste0(MPath, "SUF.R"))
source(paste0(MPath, "Hydrus.R"))

# GRANAR2_path <- "GRANAR/R/GRANAR2/"
TRoot_path <- "FUNCTIONS/T-Root/"

# for (i in list.files(GRANAR2_path)) {
#   print(i)
#   source(paste0(GRANAR2_path, i))
# }

for (i in list.files(TRoot_path)) {
  # print(i)
  source(paste0(TRoot_path, i))
  
}

# source("Data_preparation.R")

Plants <- read.csv("Data/Anatomy/Plants.csv")[,-1]
Segments <- read.csv("Data/Anatomy/Segments.csv")[,-1]
CrossSections <- read.csv("Data/Anatomy/CrossSections.csv")[,-1]
anatomy1 <- read.csv("Data/Anatomy/anatomy1.csv")[,-1]
anatomy2 <- read.csv("Data/Anatomy/anatomy2.csv")[,-1]
Parameters <- read.csv("Data/Anatomy/Parameters.csv")[,-1]

date <- Sys.Date()
```

# Data initialization

```{r}
file <- "Data/CRB-MARSHAL/Tomato_root3.txt"
RS_1 <- read.csv("Data/CRB-MARSHAL/RootSystem.csv")[,-1]
RS_2 <- read.csv("Data/CRB-MARSHAL/RootSystem_tomato2.csv")
RS_3 <- read.csv("Data/CRB-MARSHAL/RootSystem_tomato3.csv")
RS_maize <- read.csv("Data/CRB-MARSHAL/RootSystem_maize.csv")

RS_4 <- read.csv("Data/CRB-MARSHAL/RS_Tomato_60_1.csv")
RS_5 <- read.csv("Data/CRB-MARSHAL/RS_Tomato_60_2.csv")
```

# Process rough root system

Go through Root_System folder and load root systems

```{r}
# RS_path <- "CRB-MARSHAL/inputs/Root_Systems/"
# 
# for(file_i in list.files(RS_path, pattern = ".txt")){
#   print(file_i)
#   RS_name <- strsplit(file_i, split = ".txt")[[1]]
#     
#   RS_m <- fread(paste0(RS_path, file_i))
# 
#   # We invert z2
#   RS_m$z3 <- min(RS_m$z2[RS_m$type == 1]) - RS_m$z2 + max(RS_m$z2[RS_m$type == 1])
#   
#   write.csv(x = RS_m,
#             file = paste0(RS_path, RS_name, ".csv"),
#             row.names = F)
# }
```

# Run MARSHAL

## Define kr and kx coefficients

```{r}
# Coefficients of the regression equations
kr_coef <- read.csv("Data/CRB-MARSHAL/kr_coef_full.csv")
kx_coef <- read.csv("Data/CRB-MARSHAL/Kx_coef_full.csv")
kr_coef_mono <- read.csv("Data/CRB-MARSHAL/kr_coef_full_mono.csv")
```

```{r}
timing <- c(7, 25) # Timing of maturation
psi_Collar = -15000
my_soil = data.frame(id = c(1,2,3,4),
                     z = c(0, -10, -20, -30),
                     psi = c(-300, -300, -300, -300))

# Conductivities tables (basically templates because we will modfy them later)
# dico_conductivities1 <- read.csv("CRB-MARSHAL/inputs/conductivities2.csv")
dico_conductivities <- read.csv("CRB-MARSHAL/inputs/conductivities2_2.csv")
mono_conductivities <- read_xlsx("CRB-MARSHAL/inputs/conds2.xlsx")
```

We run 4 scenarios :

-   S1 : Tomato deposition levels (lignin cap then sub exo at 7 days then sub endo at 25 days) and secondary growth

-   S2 : Remove sub exo : only endo CS until 25 days, still with SG -\> kr is increased

-   S3 : Remove sub exo and no SG -\> kr is same as S1 and Kx stays low!

-   (S2bis) : Swith endo and exo : first endo is suberized at 7 days, then exo sub at 25 days, to test if exo act as endo

-   (S4) :

### 30 old RS

```{r}
path_30 <- "CRB-MARSHAL/inputs/Root_Systems/30/"

RSHA_table_30 <- tibble()
Krs_table_30 <- tibble()
RSHA_id <- 1

S1_30_full <- MARSHAL_LOOP(path_30, scenario = "S1")
S2_30_full <- MARSHAL_LOOP(path_30, scenario = "S2")
S3_30_full <- MARSHAL_LOOP(path_30, scenario = "S3")
S2b_30_full <- MARSHAL_LOOP(path_30, scenario = "S2b")
S4_30_full <- MARSHAL_LOOP(path_30, scenario = "S4")

Krs_table_30 <- RSHA_table_30 %>% 
  rbind(S1_30_full[[2]]%>% mutate(Scenario = "S1")) %>%
  rbind(S2_30_full[[2]]%>% mutate(Scenario = "S2")) %>%
  rbind(S3_30_full[[2]]%>% mutate(Scenario = "S3")) 

RSHA_table_30 <- RSHA_table_30 %>% 
  rbind(S1_30_full[[1]]%>% mutate(Scenario = "S1")) %>%
  rbind(S2_30_full[[1]]%>% mutate(Scenario = "S2")) %>%
  rbind(S3_30_full[[1]]%>% mutate(Scenario = "S3")) 

# write.csv(RSHA_table_30, "Results/RSHA/RSHA_table_30.csv", row.names = F)
# write.csv(Krs_table_30, "Results/RSHA/Krs_table_30.csv", row.names = F)
```

### 60 old RS

```{r}
path_60 <- "CRB-MARSHAL/inputs/Root_Systems/60/"

RSHA_table_60 <- tibble()
Krs_table_60 <- tibble()

S1_60_full <- MARSHAL_LOOP(path_60, scenario = "S1")
S2_60_full <- MARSHAL_LOOP(path_60, scenario = "S2")
S3_60_full <- MARSHAL_LOOP(path_60, scenario = "S3")
S2b_60_full <- MARSHAL_LOOP(path_60, scenario = "S2b")
S4_60_full <- MARSHAL_LOOP(path_60, scenario = "S4")

Krs_table_60 <- RSHA_table_60 %>% 
  rbind(S1_60_full[[2]]%>% mutate(Scenario = "S1")) %>%
  rbind(S2_60_full[[2]]%>% mutate(Scenario = "S2")) %>%
  rbind(S3_60_full[[2]]%>% mutate(Scenario = "S3")) 

RSHA_table_60 <- RSHA_table_60 %>% 
  rbind(S1_60_full[[1]]%>% mutate(Scenario = "S1")) %>%
  rbind(S2_60_full[[1]]%>% mutate(Scenario = "S2")) %>%
  rbind(S3_60_full[[1]]%>% mutate(Scenario = "S3")) 

# write.csv(RSHA_table_60, "Results/RSHA/RSHA_table_60.csv", row.names = F)
# write.csv(Krs_table_60, "Results/RSHA/Krs_table_60.csv", row.names = F)
```

## Load Results

```{r}
RSHA_table_30 <- read.csv("Results/RSHA/RSHA_table_30.csv")
RSHA_table_60 <- read.csv("Results/RSHA/RSHA_table_60.csv")
Krs_table_30 <- read.csv("Results/RSHA/Krs_table_30.csv")
Krs_table_60 <- read.csv("Results/RSHA/Krs_table_60.csv")
```

## Stat Analysis

### Stats- 30 days

```{r}
Krs_lm_30 <- lm(data = Krs_table_30 %>% filter(Scenario %in% c("S1", "S2", "S3")), formula = Krs ~ Scenario)
summary(Krs_lm_30)
anova(Krs_lm_30)
Krs_means_30 <- emmeans(Krs_lm_30, specs = pairwise ~ Scenario)
Krs_means_30 <- as_tibble(Krs_means_30$emmeans)

mean_S1 <- Krs_means_30$emmean[Krs_means_30$Scenario == "S1"]
mean_S2 <- Krs_means_30$emmean[Krs_means_30$Scenario == "S2"]
mean_S3 <- Krs_means_30$emmean[Krs_means_30$Scenario == "S3"]

print(paste0("DIfference between S1 and S2 : ", (mean_S1-mean_S2)*100/mean_S1))
print(paste0("DIfference between S1 and S3 : ", (mean_S1-mean_S3)*100/mean_S1))
```

### Stats - 60 days

```{r}
Krs_lm_60 <- lm(data = Krs_table_60 %>% filter(Scenario %in% c("S1", "S2", "S3")), formula = Krs ~ Scenario)
summary(Krs_lm_60)
anova(Krs_lm_60)
Krs_means_60 <- emmeans(Krs_lm_60, specs = pairwise ~ Scenario)
Krs_means_60 <- as_tibble(Krs_means_60$emmeans)

mean_S1 <- Krs_means_60$emmean[Krs_means_60$Scenario == "S1"]
mean_S2 <- Krs_means_60$emmean[Krs_means_60$Scenario == "S2"]
mean_S3 <- Krs_means_60$emmean[Krs_means_60$Scenario == "S3"]

print(paste0("DIfference between S1 and S2 : ", (mean_S1-mean_S2)*100/mean_S1))
print(paste0("DIfference between S1 and S3 : ", (mean_S1-mean_S3)*100/mean_S1))
```

# Various Plots

```{r}
# S1_60 <- RSHA_table_60%>%filter(RSHA_id == "Tomato_60_1" & Scenario == "S1")
# S2_60 <- RSHA_table_60%>%filter(RSHA_id == "Tomato_60_1" & Scenario == "S2")
# S3_60 <- RSHA_table_60%>%filter(RSHA_id == "Tomato_60_1" & Scenario == "S3")
```

## Plot Krs

### 30 days old

```{r}
t <- Krs_table_30[c("Krs", "Scenario")] %>% 
  group_by(Scenario) %>%
  summarise(mean_Krs = mean(Krs),
            sd_Krs = sd(Krs))

barplot_30 <- ggplot(data = t %>% filter(Scenario %in% c("S1", "S2", "S3"))) + 
  geom_errorbar(aes(x = Scenario, 
                    ymin = (mean_Krs-sd_Krs)*1e9, 
                    ymax = (mean_Krs+sd_Krs)*1e9
                    ),
                width = 0.1) +
  geom_col(aes(x = Scenario, y = mean_Krs*1e9, fill = Scenario)) +
  ylab("Krs [10E-9 m3 s-1 MPa-1]") +
  theme_test() +
  theme(legend.position = "none")

# svg("plots/CRB-MARSHAL/Barplot_30.svg", width = 2, height = 3)
barplot_30
# dev.off()
  
```

### 60 days old

```{r}
t <- Krs_table_60[c("Krs", "Scenario")] %>% 
  group_by(Scenario) %>%
  summarise(mean_Krs = mean(Krs),
            sd_Krs = sd(Krs))

pander(t)

barplot_60 <- ggplot(data = t %>% filter(Scenario %in% c("S1", "S2", "S3"))) + 
  geom_errorbar(aes(x = Scenario, 
                    ymin = (mean_Krs-sd_Krs)*1e9, 
                    ymax = (mean_Krs+sd_Krs)*1e9
                    ),
                width = 0.1) +
  geom_col(aes(x = Scenario, y = mean_Krs*1e9, fill = Scenario)) +
  ylab("Krs [10E-9 m3 s-1 MPa-1]") +
  theme_test() +
  theme(legend.position = "none")

# svg("plots/CRB-MARSHAL/Barplot_60.svg", width = 2, height = 3)
barplot_60
# dev.off()
```

## Plot Hydraulic Properties

```{r}
HP_curves <- ggplot(data = RSHA_table_60%>%filter(RSHA_id == "Tomato_60_1")) +
  geom_vline(aes(xintercept = 30), alpha = 0.2, size = 1) +
  
  geom_line(aes(x = time2, 
                y = kr*1e5,
                color = Scenario),
            linewidth = 1.5,
            linetype = 1) +
  
  geom_line(aes(x = time2, 
                y = kr * 2 * 3.1415 * radius * 1e5,
                color = Scenario),
            linewidth = 1,
            linetype = 1,
            alpha = 0.5) +
  
  geom_line(aes(x = time2,
                y = radius*10),
            color = "red4") +
  
  geom_line(aes(x = time2,
                y = kx*1e2,
                color = Scenario),
            linewidth = 1,
            linetype = 3) +

  facet_wrap(~Scenario) +
  ylim(0, 15) +
  xlab("Root Age [d]") +
  ylab(" ") +
  theme_test()

HP_curves

# svg("plots/CRB-MARSHAL/HP_curves.svg", width = 9, height = 3)
HP_curves
# dev.off()
```

```{r}
test <- RSHA_table_60 %>% filter(RSHA_id == "Tomato_60_1") %>%
  mutate(kr = kr*1e5,
         kx = kx*1e2,
         Kr = kr * 2 * 3.1415 * radius) %>%
  gather(kr, kx, Kr, key = "HP_type", value = "HP_value")
```

```{r}
HP_curves2 <- ggplot(data = test) +
  geom_line(aes(x = time2, y = HP_value, linetype = HP_type, color = Scenario),
            linewidth = 0.8) +
  facet_wrap(~Scenario) +
  xlab("Root Age [d]") +
  ylab("") +
  theme_test()

# svg("plots/CRB-MARSHAL/HP_curves2.svg", width = 9, height = 3)
HP_curves2
# dev.off()
```

## Plot Root Systems

```{r}
RS_kr_30_plot <- ggplot(RSHA_table_30%>%filter(RSHA_id == "Tomato_30_1" & Scenario %in% c("S1", "S2", "S3"))) +
  geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2, linewidth = radius, color = kr)) +
  # geom_segment(data = S2_30, aes(x = x1, y = z1, xend = x2, yend = z2, linewidth = radius, color = kr)) +
  facet_wrap(~Scenario, nrow = 1) +
  scale_color_viridis() +
  scale_linewidth_continuous(range = c(0.5, 1)) +
  coord_fixed() +
  theme_test()

# svg("plots/CRB-MARSHAL/RS_kr_30.svg", width = 7, height = 3.5)
# png("plots/CRB-MARSHAL/RS_kr_30.png", width = 7, height = 3.5, units = "in", res = 300)
RS_kr_30_plot
# dev.off()



RS_kr_60_plot <- ggplot(RSHA_table_60 %>% 
                          filter(RSHA_id == "Tomato_60_1" & 
                                   Scenario %in% c("S1", "S2", "S3")
                                 )
                        ) +
  geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2, linewidth = radius, color = kr)) +
  # geom_segment(data = S2_30, aes(x = x1, y = z1, xend = x2, yend = z2, linewidth = radius, color = kr)) +
  facet_wrap(~Scenario, nrow = 1) +
  scale_color_viridis() +
  scale_linewidth_continuous(range = c(0.5, 1)) +
  coord_fixed() +
  theme_test() 

# svg("plots/CRB-MARSHAL/RS_kr_60.svg", width = 7, height = 3.5)
# png("plots/CRB-MARSHAL/RS_kr_60.png", width = 7, height = 3.5, units = "in", res = 400)
RS_kr_60_plot
# dev.off()
```

Plot only one :

```{r}
p <- ggplot(data = RSHA_table_60 %>% filter(Scenario == "S1" & RSHA_id == "Tomato_60_2")) +
  geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2, linewidth = radius, color = kr)) +
  scale_color_viridis() +
  scale_linewidth_continuous(range = c(0.5, 1)) +
  coord_fixed() +
  theme_test() 

png("Figures Clean/Example_RSHA.png", width = 4, height = 5, units = "in", res = 300)
p
dev.off()
```

Try to plot both :

```{r}
p1 <- RSHA_table_30 %>% 
  filter(RSHA_id == "Tomato_30_1" & Scenario %in% c("S1", "S2", "S3")) %>%
  mutate(Age = "30") %>% rbind(
    RSHA_table_60 %>% 
  filter(RSHA_id == "Tomato_60_1" & Scenario %in% c("S1", "S2", "S3")) %>%
  mutate(Age = "60")
  )

RSHA_both_plot <- ggplot(p1) +
  geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2, linewidth = radius, color = kr)) +
  # geom_segment(data = S2_30, aes(x = x1, y = z1, xend = x2, yend = z2, linewidth = radius, color = kr)) +
  facet_wrap(~Age+Scenario, nrow = 2) +
  scale_color_viridis() +
  scale_linewidth_continuous(range = c(0.5, 1)) +
  coord_fixed() +
  xlab("x [cm]") +
  ylab("z [cm]") +
  theme_test() 

# svg("plots/CRB-MARSHAL/RSHA_Both_Plot.svg") 
# png("plots/CRB-MARSHAL/RSHA_Both_Plot.png",units = "in", width = 6, height = 6, res = 600) 
RSHA_both_plot
# dev.off()
```

## SUF profile

```{r}
SUF_profile_plot <- function(data){
  p <- ggplot(data) +
  geom_ribbon(aes(x = xbin, 
                    ymin = mean_sum_SUF - sd_sum_SUF,
                    ymax = mean_sum_SUF + sd_sum_SUF,
                    fill = Scenario),
              alpha = 0.2) +
  geom_line(aes(x = xbin, y = mean_sum_SUF, color = Scenario)) +
  # geom_point(aes(x = xbin, y = mean_sum_SUF, color = Scenario)) +
  
  xlab("Soil Depth [cm]") +
  ylab(" ") +
  ggtitle("Cummulated SUF per 1cm soil layer") +
  theme_test()  
  
  return(p)
}

RSHA_30_suf <- RSHA_table_30 %>% 
  mutate(xbin = round(z2)) %>%
  group_by(xbin, RSHA_id, Scenario) %>%
  summarise(sum_SUF = sum(suf)) %>%
  group_by(xbin, Scenario) %>%
  summarise(mean_sum_SUF = mean(sum_SUF),
            sd_sum_SUF = sd(sum_SUF))%>%
  mutate(Age = "30")

RSHA_60_suf <- RSHA_table_60 %>% 
  mutate(xbin = round(z2)) %>%
  group_by(xbin, RSHA_id, Scenario) %>%
  summarise(sum_SUF = sum(suf)) %>%
  group_by(xbin, Scenario) %>%
  summarise(mean_sum_SUF = mean(sum_SUF),
            sd_sum_SUF = sd(sum_SUF)) %>%
  mutate(Age = "60")

# svg("plots/CRB-MARSHAL/SUF_profile_30.svg", width = 4, height = 2)
SUF_profile_plot(RSHA_30_suf) 
# dev.off()

# svg("plots/CRB-MARSHAL/SUF_profile_60.svg", width = 4, height = 2)
SUF_profile_plot(RSHA_60_suf)
# dev.off()


```

```{r}
med1 <- median(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"]) 
med2 <- median(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S2"]) 
med3 <- median(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S3"]) 

mad1 <- mad(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"]) 
mad2 <- mad(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S2"]) 
mad3 <- mad(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S3"]) 
# quantile(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"], probs = 0.5)

SUF_stats <- tibble(Scenario = c("S1", "S2", "S3"),
                    Median = c(median(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"]),
                                 median(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S2"]),
                                 median(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S3"])),
                    Mad = c(mad(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"]),
                                 mad(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S2"]),
                                 mad(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S3"])),
                    Mean = c(mean(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"]),
                                 mean(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S2"]),
                                 mean(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S3"])),
                    SD = c(sd(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"]),
                                 sd(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S2"]),
                                 sd(RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S3"]))
)
                    

pander(SUF_stats)
```

### Stat test

KS-test to see if distribution is normal

```{r}
# K-S test to test if data is nor
ks.test(x = RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S1"],
        y = RSHA_30_suf$mean_sum_SUF[RSHA_30_suf$Scenario == "S3"])

# 
```

```{r}
RSHA_both_suf <- rbind(RSHA_30_suf, RSHA_60_suf)

p <- ggplot(RSHA_both_suf) +
  
  geom_line(aes(x = xbin, y = mean_sum_SUF, color = Scenario)) +
  
  # geom_ribbon(aes(x = xbin,
  #                   ymin = mean_sum_SUF - sd_sum_SUF,
  #                   ymax = mean_sum_SUF + sd_sum_SUF,
  #                   fill = Scenario),
  #             alpha = 0.4) +
  
  geom_errorbar(aes(x = xbin,
                    ymin = mean_sum_SUF - sd_sum_SUF,
                    ymax = mean_sum_SUF + sd_sum_SUF,
                    color = Scenario),
              alpha = 0.4,
              width = 0.1) +
  
  
  geom_point(aes(x = xbin, y = mean_sum_SUF, color = Scenario)) +
  
  # geom_point(aes(x = xbin, y = mean_sum_SUF, color = Scenario)) +
  facet_wrap(~Age, ncol = 1) +
  
  xlab("Soil Depth [cm]") +
  xlim(-30, -3) +
  ylab(" ") +
  # ggtitle("Cummulated SUF per 1cm soil layer") +
  theme_test()

p

# svg("plots/CRB-MARSHAL/SUF_profile_both.svg", width = 3, height = 4)
# p
# dev.off()
```

```{r}
ggplot(data = RSHA_30_suf) +
  geom_col(aes(x = xbin, y = mean_sum_SUF, fill = Scenario), position = "dodge")
```

# BackUp Codes

```{r}




S1_30 <- RSHA_table_30 %>% filtr()
S2_30 <- S2_30 %>% mutate(S = "2")
S3_30 <- S3_30 %>% mutate(S = "3")
S2b_30 <- S2b_30 %>% mutate(S = "2b")

suf_df1_30 <- data.frame()

make_suf_bar <- function(x = S1_30){
  suf_df1 <- tibble()
  for(x_fac in seq(round(min(x$z2)), 0)){
  # Select a subset
  subs <- x %>% filter(z2 >= x_fac-0.5 & z2 < x_fac+0.5)
  temp_df <- data.frame(x = x_fac,
                        SUF_mean = sum(subs$suf),
                        SUF_sd = sd(subs$suf))
  suf_df1 <- rbind(suf_df1, temp_df)
  }
  return(suf_df1)
}


suf_df1_30 <- make_suf_bar(x = S1_30)
suf_df2_30 <- make_suf_bar(x = S2_30)
suf_df3_30 <- make_suf_bar(x = S3_30)


suf_df1_30$exp <- 1
suf_df2_30$exp <- 2
suf_df3_30$exp <- 3
combined_data_30 <- rbind(suf_df1_30, suf_df2_30, suf_df3_30)

# svg("Plots/SUF_comparaison2.svg", height = 4, width = 6)  
SUF_bar_30 <- ggplot() +
  # geom_bar(data = suf_df1_30, aes(x = x, y = SUF_mean), stat = "identity", fill = "green4", alpha = 0.5) +
  # geom_bar(data = suf_df2_30, aes(x = x, y = SUF_mean), stat = "identity", fill = "orange", alpha = 0.5) +
  # geom_bar(data = suf_df3_30, aes(x = x, y = SUF_mean), stat = "identity", fill = "red4", alpha = 0.5) +
  geom_bar(data = combined_data_30, aes(x = x, y = SUF_mean, fill = as.factor(exp)),
           stat = "identity"
           )+
  # facet_wrap(~as.factor(exp)) +
  # ggtitle("Blue = Tomato | Orange = Monocot") +
  theme_bw()
# dev.off()
print(SUF_bar_30)

# svg("plots/CRB-MARSHAL/SUF_barplot_30.svg", width = 5, height = 3)
SUF_bar_30
# dev.off()
```
