---
title: "MAIN"
author: "Marco D'Agostino"
format: html
editor: source
editor_options: 
  chunk_output_type: inline
---

# INTRODUCTION

This notebook contains the main codes of the project T-ROOT

First we load the packages. NB : you may need to install some of them manually.

```{r, include=F}
options(rstudio.help.showDataPreview = FALSE)
rm(list = ls())

# LOAD FUNCTION
TRoot_path <- "src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path, pattern = ".R")) {
  print(i)
  source(paste0(TRoot_path, i))
}

pkg_list <- c("fmsb", "packcircles", "pander", "readxl", "visreg", "EnvStats", "factoextra", "data.table",
              "reticulate", "xml2", "tidyverse", "plyr", "deldir", "viridis", "Hmisc", "devtools", "ggplot2",
              "gridExtra", "dplyr", "cowplot", "stats", "emmeans", "corrplot", "sf", "SciViews")

load_packages(pkg_list)

# Change your path here to Github files
GRANAR_path <- "C:/Users/mdagostino/Desktop/GITHUB/granar/R/"

for (i in list.files(GRANAR_path, pattern = ".R")) {
  print(i)
  source(paste0(GRANAR_path, i))
}

# source("Data_preparation.R")

Plants        <- read.csv("Data/Anatomy/Plants.csv")
Segments      <- read.csv("Data/Anatomy/Segments.csv")
CrossSections <- read.csv("Data/Anatomy/CrossSections.csv")
anatomy1      <- read.csv("Data/Anatomy/anatomy1.csv")
anatomy2      <- read.csv("Data/Anatomy/anatomy2.csv")
Parameters    <- read.csv("Data/Anatomy/Parameters.csv")[,-1]
Anatomy_Full  <- read.csv("Data/Anatomy/Anatomy_Full.csv")

date          <- Sys.Date()
```

Now we need to load all necessary libraries

-   *GRANAR* libraries : I advise to get them directly from GITHUB

-   Specific functions for this notebook : load all functions in FUNCTIONS/T-Root path

Other folders :

-   *Data* : contains all data used in these scripts

-   *MECHA* : contains all codes to run MECHA

-   *Params* : contains all quantified experimental cross sections in the form of GRANAR input parameters

-   *Virtual Anatomies* : contains generated virtual anatomies from Params, in the form of pdf for visualization and xm for structural data

-   *CRB-MARSHAL* : contains all codes and data to run CRootBox and MARSHAL

Here we load an convert quantification data (in the form of *xlsx* files in *Data/Quantifications* folder) into GRANAR parameters (params). The params will be stored both into single *xml* files (in the folder *Params*) directly usible into GRANAR, and into the big table Anatomy2. The file *Data_Preparation.R* automatically load and treat data from *Data/Quantifications*.

-   *Plants* contains IDs, ages and lengths of each roots
-   *Segments* contains informations about segments of each root
-   *CrossSections* contains IDs and informations about each cross section
-   *anatomy1* contains all quantifiation data
-   *anatomy2* contains all values of all GRANAR params for each cross section
-   *Parameters* contains information about the measured and GRANAR params

# 0) Analysis of quantifications

This part load and analyse the cross section quantifications.

## Visualization of data per param

*anatomy_visual()* is a function to plot quantifications per param. Each graph is a param, each line is a root, each point is a measure.

In addition, we use the function *plot_correlations_data()* to plot correlations.

```{r}
anatomy2_2 <- merge(anatomy2, Parameters[,c(3,1,2)])

source("FUNCTIONS/T-Root/anatomy_stats_visu.R")

p1 <- anatomy_visual(anatomy2_2, CrossSections)
# svg(filename=paste0("Plots/Anatomy_data_visu_",Sys.Date(),".svg"), width = 12, height = 18)
p1
# dev.off()
```

All anatomical data in standard table ; Create Anatomy_Full.csv

```{r}
# HVR2 <- anatomy2 %>% filter(CS_id == anatomy2$CS_id[1])                   # subset that will be used in the loop                                                # create output dataframe
# HVR3 <- data.frame(CS_id = unique(anatomy2$CS_id))
# 
# # initiate loop
# for (i in seq(1:length(HVR2[,1]))) {
#   temp_param <- HVR2$param_id[i]
#   # print(paste0(i," temp_param : ", temp_param))
#   temp_HVR <- anatomy2 %>% filter(param_id == temp_param)            # contains all values for one particular parameter
#   y_df <- data.frame(temp_HVR$value)
#   colnames(y_df) <- temp_param
#   HVR3 <- cbind(HVR3, y_df)                                                   # final dataframe with all data in columns
# }
# 
# Anatomy_Full <- HVR3
# Anatomy_Full$radius <- (Anatomy_Full$cortex_cell_diameter * Anatomy_Full$cortex_n_layers) + 
#   (Anatomy_Full$endodermis_cell_diameter * Anatomy_Full$endodermis_n_layers) +
#   (Anatomy_Full$epidermis_cell_diamete * Anatomy_Full$epidermis_n_layers) +
#   (Anatomy_Full$exodermis_cell_diameter * Anatomy_Full$exodermis_n_layers) +
#   # (Anatomy_Full$pericycle_cell_diameter * Anatomy_Full$pericycle_n_layers) +
#   # (Anatomy_Full$phloem_cell_diameter * Anatomy_Full$phloem_n_layers) +
#   (Anatomy_Full$stele_layer_diameter)/2
#   
# 
# Anatomy_Full <- merge(Anatomy_Full, CrossSections)
# write.csv(Anatomy_Full, "Data/Anatomy/Anatomy_Full.csv", row.names = F)
```

## Radius Analysis

Here we see that radius can be approximated as constant till 25 days, at 0.199 mm. Then, after 25 days, it can be approximated using : $r = exp(-7.59 + 0.23x)$

```{r}
# Set secondary growth treshold
treshold <- 25

# Linear model
radius_lm1 <- lm(data = Anatomy_Full%>%filter(age < treshold), formula = radius ~ 1)
summary(radius_lm1)
mrad <- radius_lm1$coefficients[1]

radius_lm2 <- lm(data = Anatomy_Full%>%filter(age >= treshold), formula = ln(radius) ~ age)
summary(radius_lm2)

alpha <- radius_lm2$coefficients[1]
beta <- radius_lm2$coefficients[2]

# Create an example dataframe to store the regression
test <- data.frame(x = seq(1,30))
test$radius <- 1
mrad <- 0.2
for(i in seq(1, length(test$x))){
  if(test$x[i] < treshold){
    test$radius[i] <- mrad
  }else{
    temp <- exp(alpha +  beta*test$x[i])
    if(temp <= mrad){test$radius[i] <- mrad}
    else{test$radius[i] <- temp}
    
  }
}

# PLot datapoints + regression
radius_plot <- ggplot() +
  geom_point(data = Anatomy_Full, aes(x = age, y = radius), size = 2) + 
  geom_line(data = test, aes(x = x, y = radius), linetype = 2, color = "red", linewidth = 1.2) +
  xlab("Age [d]") +
  ylab("Radius [mm]") +
  theme_bw()

svg("Plots/Radius_Plot.svg", width = 4, height = 3)
radius_plot
dev.off()
```

## Correlations

```{r}
prm <- c("cortex_n_layers", 
         "endodermis_cell_diameter", 
         "exodermis_cell_diameter",
         "pericycle_cell_diameter",
         "phloem_cell_diameter",
         "phloem_n_layers",
         "phloem_proportion",
         "stele_cell_diameter",
         "stele_layer_diameter",
         "stele_n_layers",
         "stele_SD",
         "xylem_cell_diameter",
         "xylem_max_size",
         "xylem_n_cells",
         "radius",
         "age")

png(filename = "plots/Correlations.png", width = 10, height = 10, units = "in", res = 100)
pcor <- corrplot(cor(Anatomy_Full[prm]), method = "number", diag = F, type = "upper")
dev.off()
```

## Parameter regressions

See Regressions2.rmd

# 1) GRANAR

GRANAR is the generator of root anatomy in R (Heymans 2021).

Run the following chunks to checks if all is good with GRANAR.\
Examples of parameter files are in \*/Params/.

## Load params

```{r}
# xml <- "Params/examples/B73_taproot_2021.xml"
xml <- "Params/P14_F_To_C02_Z10_04.xml"

param1 <- read_param_xml(xml)
param1 <- param1 %>% 
  rbind(tibble(name = "secondarygrowth",
               type = "param",
               value = "0")) %>%
  rbind(tibble(name = "phloem",
               type = "n_layers",
               value = 0))
# param2 <- read_param_xml(xml2)

```

## Play with GRANAR

```{r, warning=F}
# PRIMARY GROWTH
sim1 <- create_anatomy(parameters = param1, verbatim = F)

# svg("maize_anatomy_test.svg")
plot_anatomy(sim1)
# dev.off()

# SECONDARY GROWTH
# sim2 <- create_anatomy(parameters = param2, verbatim = F)
# plot_anatomy(sim2)
```

### Run GRANAR for all data

And store anatomies in Anatomies/data/

```{r, include=F, eval=F}
path <- "Virtual Anatomies/data2/"
param_list <- list.files("Params/", pattern = ".xml")

for(param_i in param_list){
  print(param_i)
  param_temp <- read_param_xml(paste0("Params/",param_i))
  try(expr = {
      sim_temp <- create_anatomy(parameters = param_temp, verbatim = F)
      write_anatomy_xml(sim = sim_temp, path = paste0(path, param_i))
      
      p <- plot_anatomy(sim_temp)
      ggexport(p, 
               filename = paste0(path, 
                                 strsplit(param_i, ".xml")[[1]],
                                 ".pdf"),
               plot=image) 
    }
  )
}
```

# 2) MECHA

MECHA is the solver of local conductivities (Couvreur 2018)

Set up steps to run it in local :

1.  Open **ANACONDA NAVIGATOR**

2.  Create a new environment with **python 3.7** (in this work it is called "**MECHA2**")\
    conda create -n MECHA2 python=3.7

3.  Open the console of this environment and enter the following :\
    conda install numpy\
    conda install scipy\
    conda install matplotlib\
    conda install lxml\
    conda install pip\
    pip install networkx==1.9.1

4.  Open *MECHAv4_septa_temp_V2.py* and change directories to the current path (in the form "*C:/.../MECHA/"*)

To run MECHA, we first load the root of interest by changing *current_root*. Next we run the MECHA file.

By default, MECHA can simulate different scenarios : \*

-   **B0 : No apoplastic barriers**

-   **B1 : Endodermal Casparian strip (radial walls)**

-   **B2 : Endodermal suberization except at passage cells**

-   **B3 : Endodermis full suberization**

-   **B4 : Endodermis full suberization and exodermal Casparian strip (radial walls)**

-   **B5 : Endo- and exodermal Casparian strips (radial walls)**

-   **B6 : Exodermis full suberization and endodermal Casparian strip (radial walls)**

-   **B7 : Exodermal Casparian strip (radial walls)**

-   **B8 : Endo and exodermal suberization**

-   **B9: Lignin Cap and endodermal CS**

Here we choose to compute scenarios 0, 1, 5 and 6. You can change the simulated scenarios in *MECHA/Projects/granar/in/Maize_Geometry.xml* in line 19.

```{r}
anatomy_file <- "MECHA/cellsetdata/sorghum_7cm.xml"
file.copy(anatomy_file, "MECHA/cellsetdata/")
file.rename(paste0("MECHA/cellsetdata/", anatomy_file), "MECHA/cellsetdata/current_root.xml")

test <- get_root_section(anatomy_file)
ggplot(test) +
    # geom_polygon(aes_string("x", "y", group="id_cell", fill=col), colour="white") +
    geom_polygon(aes(x = x, y = y, fill = type, group = id_cell),
                 color = "white") +
    theme_classic() +
    coord_fixed() +
    theme(axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank())
```

```{r, eval=FALSE}
# Change current_root with the desired anatomy
# write_anatomy_xml(sim1, "MECHA/cellsetdata/current_root.xml")

#========================================================
library(reticulate)
use_condaenv("GRANAR-MECHA") # choose python environment 
sys <- import("sys", convert=T)
# try(py_run_file("MECHA/MECHAv4_TRoot.py"))
conds <- run_mecha()

#========================================================
rp <- "MECHA/Projects/granar/out/Tomato/Root/Project_Test/results/"
# Flux0 <- ApoSymp(paste0(rp,"Macro_prop_0,0.txt"))
# Flux1 <- ApoSymp(paste0(rp,"Macro_prop_1,1.txt"))
# Flux2 <- ApoSymp(paste0(rp,"Macro_prop_5,5.txt"))
# Flux3 <- ApoSymp(paste0(rp,"Macro_prop_6,6.txt"))
# Flux4 <- ApoSymp(paste0(rp,"Macro_prop_4,4.txt"))
Flux5 <- ApoSymp(paste0(rp,"Macro_prop_5,5.txt")) # Endodermal & exodermal Casparian strips
Flux8 <- ApoSymp(paste0(rp,"Macro_prop_8,8.txt")) # Exodermis full suberized and endodermis full suberized
Flux9 <- ApoSymp(paste0(rp,"Macro_prop_9,9.txt")) # Lignin Cap

# plot_water_flux(Flux0, apobar = 0)
# plot_water_flux(Flux1, apobar = 1)
# plot_water_flux(Flux2, apobar = 1)
# plot_water_flux(Flux3, apobar = 1)
# plot_water_flux(Flux4, apobar = 3)
plot_water_flux(Flux5, apobar = 3)
plot_water_flux(Flux8, apobar = 3)
plot_water_flux(Flux9, apobar = 3)
```

Run MECHA for all quantified anatomies

```{r, eval= F}
# anat_path <- "Virtual Anatomies/data 14-12-2023/"
# list_anat <- list.files(path= anat_path, pattern = ".xml")
# output_path <- "MECHA/Projects/granar/out/Tomato/Root/Project_Test/results/"
# 
# Q_Conductivities <- tibble()
# 
# # Loop for anatomies
# for(temp_name in list_anat){
#   print(temp_name)
#   temp_conds <- run_mecha(anatomy_file = temp_name, 
#                           anatomy_path = anat_path, 
#                           output_path = output_path)
#   Q_Conductivities <- rbind(Q_Conductivities, temp_conds)  
# }

```

```{r}
# # Loading results
# path_results <- "Results/Quantified_Anatomies/"
# list_conds <- list.files(path_results, pattern = ".csv")
# Conds <- tibble()
# for(file in list_conds){
#   temp_cond <- read.csv(paste0(path_results, file))
#   Conds <- rbind(Conds, temp_cond)
# }
```

# 3) VIRTUAL ROOTS

In order to study the influence of anatomy on conductivities, we need to generate virtual roots. Here we define *virtual root* as a set of values of each GRANAR parameters at a given age (day). One virtual root contains values of GRANAR parameters at different ages (one node is a set of GRANAR params corresponding to a given age in the root). Theses values are calculated based on a regression of quantifications and a random factor defined by the user. It can be a percentage of the regression value (alpha) or the standart error of the regression from the data (sigma).

For that, we first compute stats to find regression equations with the function *Make_Regression()*. The file *Regressions* contains equations and sigmas for each param.

Next, we generate virtual roots with the function *Make_Virtual_Roots()*. The file *Virtual_Roots* contains all generated virtual roots. *Make_Virtual_Roots()* take the regression functions for each param, compute the param value corresponding to each node, and ad a random residual corresponding to the standart error of the regression. E.G : for cortex_n_layers, the reg equation is : $-0.05407*X + 3.63181 + sd$ where X is the node, and $sd$ the random residual. $sd$ is drawn in a normal distribution of mean 0 and sigma the standart deviation of the regression of the param : $sd \sim R(0, \sigma_{param})$.

NB : we can also add some randomness using the method $alpha$, which simply compute the value of the param per node and add a residual that is a percentage of the mean value of the param at that node.

Finally, we can plot and save the results using the *Virtual_Roots_Visu()* function.

To see full the statistical results and developments, see *Regressions.Rmd*.

NB : there are 3 Make_Virtual_Root files in the R code folder :

-   *Make_Virtual_Roots_old.R* is the first code made. It generates fixed nodes along the root, and DOES NOT take into account causality between parameters (for ex xylem_max \< xylem_mean).\
    This code works with an old version of *Regression* table that does not yet add sd into regression equations. Just don't use this version .

-   *Make_Virtual_Roots.R* generates **FIXED** nodes along the root and takes into account causality between parameters.

-   *Make_Virtual_Roots2.R* generates **RANDOM** nodes along the root, and takes into account causality between parameters.

### Set simulation parameters

```{r, eval = F}
n_nodes <- 30   #30
n_roots <- 50   #30
method <- "sigma"
alpha <- 0.15
```

### Load tables

```{r, eval = F}
# Regressions <- Make_Regression(anatomy2)
# write.csv(Regressions, "Data/Regressions.csv")
# Regressions <- read.csv("Data/Regressions.csv")

# source("Regressions_Auto.R")
```

### Create Regressions

```{r}
source("Regressions_Auto.R")

reg_plots <- wrap_plots(plot_list, ncol = 3)
print(reg_plots)
ggsave(filename = "plots/regressions/Regression_plots.svg", 
       plot = reg_plots, device = "svg", width = 10, height = 15, units = "in")
```

### Generation of Virtual_Roots

The principle here is that we build simple regression functions for each GRANAR parameter. For ex, the function *phloem_proportion()* returns a regressed value of phloem proportion for a given x.

```{r, eval = F}
Virtual_Roots3 <- Make_Virtual_Roots3(Parameters,
                                    n_nodes,
                                    n_roots,
                                    method,
                                    alpha)

# Virtual_Roots <- Virtual_Roots3
# write.csv(Virtual_Roots3, paste0("Data/Virtual_Root_", Sys.Date(), "_", n_nodes,"x",n_roots,".csv"))
```

### Visualisation

NB : You can add colors to points by changing code of *Virtual_Root_Visu.R* so that each virtual root has a color

```{r}
Virtual_Roots3 <- read.csv("Data/Virtual Roots/Virtual_Root_2023-07-31_30x50.csv")

source("FUNCTIONS/T-Root/Virtual_Roots_Visu.R")
p3_3 <- Virtual_Roots_Visu2(Virtual_Roots3)

p3_3
ggsave(filename=paste0("Plots/Virtual_roots3_",Sys.Date(),"_n",n_nodes,"_r",n_roots,".png"), 
       plot = p3_3,
       width = 8, height = 12, device = "png", units = "in", dpi = 300)
```

# 4) GRANAR-MECHA LOCAL

The final results of this project were generated with this chunk

Here we generate GRANAR anatomies for each node of the virtual roots and run MECHA.\
This is done with the function *Make_Virtual_Anatomies()*.

We enter a table of Virtual_Roots, and the function outputs a table of computed conductivities per cross-section and per scenario.

```{r, echo = F, include = F}
# LOAD VIRTUAL ROOTS
Virtual_Roots3 <- read.csv("Data/Virtual Roots/")
# Virtual_Roots_test <- Virtual_Roots3%>%filter(root == "root1", x == 0)

# SET DIRECTORIES
mecha <- "MECHA/MECHAv4_TRoot.py"
output <- "MECHA/Projects/granar/out/Tomato/Root/Project_Test/results/"

#==================================================================================
#==================================================================================
use_condaenv("GRANAR-MECHA")
source("FUNCTIONS/T-Root/Make_Virtual_Anatomies.R")
# source("GRANAR/R/T-Root/Make_Virtual_Anatomies_light.R")

VR_conductivities <- Make_Virtual_Anatomies(Virtual_Roots3,
                                            MECHA_path = mecha,
                                            output_path = output,
                                            anatomy_path = "Results/12-01-2023/Anatomies/", result_path = "Results/12-01-2023/Conductivities/",
                                            done_path = "Results/12-01-2023/done/")
#==================================================================================
#==================================================================================

# write.csv(VR_conductivities, paste0("Data/VR_conductivities_", date, "_n", nodes, "_r", roots, "_a", a*100,".csv"))

```

## Generate GRANAR anatomies :

```{r}
# LOAD VIRTUAL ROOTS
Virtual_Roots <- read.csv("Data/Virtual Roots/Virtual_Root_2023-07-17_30x20.csv")
# Virtual_Roots_test <- Virtual_Roots%>%filter(root == "root1", x == 1 | x == 3)
```

Run all GRANAR anatomies and save XML files :

```{r, include = F}
source("FUNCTIONS/T-Root/Make_Virtual_Anatomies_G.R")
Make_Virtual_Anatomies_G(Virtual_Roots = Virtual_Roots,
                         template = "Data/template.xml", 
                         export_path_xml = "Results/12-01-2023/Anatomies/",
                         export_path_pdf = "Results/12-01-2023/Anatomies_PDF/"
                         )
```

Then run MECHA for each Cross Section and kAQP scenarios

```{r, eval = F}
# Setup
mecha <- "MECHA/MECHAv4_TRoot.py"
output <- "MECHA/Projects/granar/out/Tomato/Root/Project_Test/results/"
h_path <- "MECHA/Projects/granar/in/Tomato_Hydraulics.xml"
AQP_list <- seq(from = 0.0001, to = 0.001, length.out = 10)
# AQP_list <- c(0.00043)

use_condaenv("GRANAR-MECHA") # choose MECHA environment

source("FUNCTIONS/T-Root/Make_Virtual_Anatomies_M.R")
Make_Virtual_Anatomies_M(Virtual_Roots = Virtual_Roots,
                         anatomy_path = "Results/12-01-2023/Anatomies/", 
                         MECHA_path = "MECHA/MECHAv4_TRoot.py", 
                         output_path = output,
                         conds_path = "Results/12-01-2023/Conductivities/",
                         done_path = "Results/12-01-2023/done/",
                         hydraulic_path = h_path, 
                         AQP_list = AQP_list)
```

# 5) GRANAR-MECHA CECI

In this part we create jobs to send to HPC, and load result data. We used that method because GRANAR was 10x slower than before optimized update.

## Instructions, computing and data extraction
 
global scratch : */auto/globalscratch/users/m/d/mdago/\
*main dir : */home/users/m/d/mdago/*

Instructions :

-   Create a table Virtual_Roots with the code above, with the desired parameters (n_roots and n_nodes)

-   Then execute in local the script Make_my_jobs.R to generate the job files, the R files and the data that will be used.

```{r, eval = F}
# Virtual_Roots <- Virtual_Roots3
source("FUNCTIONS/T-Root/Make_my_jobs2.R")
```

-   Each job will run one script R that will call one csv table. Here we generate 2x50 jobs that will compute 1 roots each (total of 50 roots).
-   Load the data from VR_loop to the folder of the CISM.
-   Load the jobs and R files to the CISM.
-   Then run on the CISM the job "Loop_jobs.sh" like this: **sbatch Loop_jobs.sh** .
-   Don't forget to be in the right directory, and if necessary to convert Loop_jobs into unix (with dos2unix). Tips : you can convert all files at once using "dos2unix \*.job"
-   To cancel a job : *scancel jobid* or *scancel -u login*
-   Once computing is done, download the file Results

Analyse results of simulation (deprecated)

```{r, eval=FALSE}
rpath <- "results/02-06-2023/"

res <- c()
rlist <- list.files(paste0(rpath), pattern = ".out")
for (i in rlist) {
  # print(i)
  temp_r <- read_file(paste0(rpath, i))
  temp_r <- str_split(temp_r, pattern = "\n")
  temp_r <- temp_r[1]

  temp_r2 <- NULL
  for (j in seq(1, length(temp_r[[1]]))) {
    # print(row)
    row <- temp_r[[1]][j]
    if(row == "`summarise()` ungrouping output (override with `.groups` argument)"){
      # print(row)
    }else{
      temp_r2 <- c(temp_r2, row)
    }
  }

  res <- c(res, temp_r2)
}

sink(paste0(rpath, "results.txt"))
print(res)
sink()
```

Open all results files and merged them into *Conductivities* (to do the first time after running a simulation) :

```{r, eval = F}
rpath <- "results/31-07-2023/"  # Most recent results
clist <- list.files(paste0(rpath), pattern = ".csv")
Conductivities <- data.frame()
for (c in seq(1, length(clist))) {
  print(c)
  temp_c <- read.csv(paste0(rpath,clist[c]))[,-1]
  Conductivities <- rbind(Conductivities, temp_c)
}

write.csv(Conductivities, paste0("Data/Conductivities_", date,".csv"), row.names = F)
```

Extract data from VR_loop to re-build Virtual_Roots

```{r, eval=FALSE}
# Recreate Virtual_Roots table from csv data files in VR_loop/
Virtual_Roots <- data.frame()
ls <- list.files("Data/VR_loop", pattern = "csv")
for (file in ls) {
  temp_df <- read.csv(paste0("Data/VR_loop/", file))[,-1]
  Virtual_Roots <- rbind(Virtual_Roots, temp_df)
}

# write.csv(Virtual_Roots, paste0("Data/Virtual_Roots3_",date,".csv"))
```

# Root lengths

```{r}
head(Plants)

Plants$days2 <- as.factor(Plants$days)

# LENGTHS
ggplot(data = Plants, aes(color = days2)) +
  geom_point(aes(x = days2, y = length)) +
  geom_boxplot(aes(x = days2, y = length)) + 
  # facet_wrap(~days) +
  theme_bw() +
  ggtitle("Root length (cm")

#GROWTH RATE
ggplot(data = Plants, aes(color = days2)) +
  geom_point(aes(x = days2, y = growth_rate)) +
  geom_boxplot(aes(x = days2, y = growth_rate)) +
  theme_bw() +
  ggtitle("Growth rate (cm/d)")
```

# CellSet

Collect all CellSet anatomies

```{r}
CellSet_full <- tibble()
for(i in list.files("CellSet/Anatomies Clean/", pattern = ".xml")){
  print(i)
  temp <- get_root_section(paste0("CellSet/Anatomies Clean/", i))
  id <- strsplit(i, split = ".xml")[[1]]
  temp$CS_id <- id
  CellSet_full <- rbind(CellSet_full, temp)
}

# Merge with identifyers
CellSet_full <- merge(CellSet_full, CrossSections)

CellSet_full$id_cell <- as.character(CellSet_full$id_cell)

# Replace names
CellSet_full <- CellSet_full %>% 
  mutate(type = recode(type, 
                       "columella3" = "xylem",
                       "general" = "exodermis",
                       "rootcapl2" = "intercellular"))

write.csv(x = CellSet_full, file = "CellSet/CellSet_full.csv", row.names = F)
```

```{r}

# plot_anatomy(test, col = "type")
g <- ggplot(data = CellSet_full) +
  geom_polygon(aes_string("x", "y", group="id_cell", fill="type"), colour="white") +
  scale_fill_manual(
    values = c("cambium" = "#f8766dff",
           "companion_cell" = "#d89000ff",
           "cortex" = "#a3a500ff",
           "endodermis" = "#39b600ff",
           "epidermis" = "#00bf7dff",
           "exodermis" = "#00bfc4ff",
           "pericycle" = "#00b0f6ff",
           "phloem" = "#9590ffff",
           "stele" = "#e76bf3ff",
           "xylem" = "#ff62bcff")
  ) +
  facet_wrap(~CS_id) +
  coord_fixed() +
  theme_classic()

svg("CellSet/Full.svg", width = 20, height = 20)
g
dev.off()
```

Compute cells radius and area :

```{r}
subset <- CellSet_full %>% filter(CS_id == "B04_B_To_C01_Z20_01" & id_cell == "58")
subset <- subset[c("id_cell", "x", "y")]

# Convert dataframe to a spatial object
sf <- st_as_sf(subset, coords = c("x", "y")) %>% st_set_crs(32615)

plot(sf)

# sf2 <- st_cast(sf, "POLYGON")

st_area(sf$)

# print(result)
```

```{r}
Sizes <- read.csv("CellSet/size.csv", sep = ";")
ggplot(data = Sizes) +
  geom_jitter(aes(x = Label, y = Area)) 
```

# Random Stuff

```{r}
test <- anatomy2 %>% 
  filter(CS_id == "B04_B_To_C01_Z20_01") %>%
  merge(Parameters) %>% 
  subset(select = c("name", "type", "value"))

sim1 <- create_anatomy(parameters = test)
plot_anatomy(sim1)

anatomy_clean <- anatomy2 %>%
  merge(Parameters) %>%
  merge(CrossSections) %>%
  subset(select = c("name", "type", "value", "CS_id", "age"))

# write.csv(anatomy_clean, "Data/Anatomy/Anatomy_clean.csv", row.names = F)

Reg <- Make_Regression(anatomy2)
```

```{r}
test <- tibble(x = rep(1:30, each = 10),
               y = NA)

for(i in seq(1, length(test$x))){
  test$y[i] <- epidermis_cell_diameter(test$x[i])
}

plot(test$x, test$y)
```

```{r}
p <- ggplot(data = Virtual_Roots3) +
  geom_point(aes(x = x, y = y, color = name),
             alpha = 0.5) +
  facet_wrap(~name+type, scales = "free_y") +
  theme_bw()

png("plots/Virtual_Roots_full_13-03.png", units = "in", height = 10, width = 12, res = 500)
p
dev.off()

VR_used <- read.csv("Data/Virtual Roots/Virtual_Root_2023-07-17_30x20.csv")
p2 <- ggplot(data = VR_used) +
  geom_point(aes(x = x, y = y, color = name), 
             alpha = 0.5) +
  facet_wrap(~name+type, scales = "free_y") +
  theme_test()

png("plots/Virtual_Roots_full_old.png", units = "in", height = 10, width = 12, res = 500)
p2
dev.off()
```
