---
title: "RESULTS ANALYSIS"
format: html
editor: source
editor_options: 
  chunk_output_type: inline
---

```{r Load Packages, include=F}
DIR_path <- getwd()
options(rstudio.help.showDataPreview = FALSE)
rm(list = ls())

TRoot_path <- "src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path)) {
  print(i)
  source(paste0(TRoot_path, i))
}

pkg_list <- c("fmsb", 
              "packcircles", 
              "pander", 
              "readxl", 
              "visreg", 
              "EnvStats", 
              "factoextra", 
              "data.table",
              "reticulate", 
              "xml2", 
              "tidyverse", 
              "plyr", 
              "deldir", 
              "viridis", 
              "Hmisc", 
              # "devtools", 
              "ggplot2",
              "gridExtra", 
              "dplyr", 
              "cowplot", 
              "stats", 
              "emmeans", 
              "corrplot", 
              "sf", 
              "SciViews")

load_packages(pkg_list)

simu_path <- "Results/12-01-2023/"
```

# EXTRACT AND PRE-PROCESS RESULTS 

## Extract Data from jobs 

```{r, eval = F}
path <- "Results/12-01-2023/Conductivities/"
l <- list.files(path, pattern = ".csv")
Conductivities <- data.frame()

for(i in l){
  # print(i)
  temp_df <- read.csv(paste0(path, i))
  Conductivities <- rbind(Conductivities, temp_df)
}
# Correct a bug that make Kx weird for b9 (the bug is fixed in scripts, but remains in results files)
Conductivities$Kx[Conductivities$Barrier == "b9"] <- Conductivities$Kx[Conductivities$Barrier == "b5"]

write.csv(Conductivities, file = "Results/12-01-2023/Conductivities_full.csv", row.names = F)
```

Plot and count the number of successfull simulations.
We have basically 20 roots x 31 days = 620 combinations, 
and for MECHA 10 kAQP x 10 barriers = 100.
But we filter to have only 30 days and 6 barriers : 

```{r}
Conductivities         <- read.csv("Results/12-01-2023/Conductivities_full.csv")
Conductivities         <- Conductivities %>% filter(X > 0 & Barrier %in% c("b1", "b2", "b4", "b6", "b8", "b9"))
Conductivities$Root_ID <- sapply(Conductivities$Root, function(i) unlist(str_split(string = i, pattern = "root"))[2])

ggplot(data = Conductivities, aes(x = X, y = Root_ID)) + geom_point() + theme_bw()
```

Create Conductivity_Dico and Conductivity_Mono.
The function *set_conductivities* process and convert to the right units : 

* kr is converted to $m s^{-1} MPa^{-1}$

* Kx is converted to $m^3 s^{-1} MPa^{-1}$

```{r, eval = F}
Virtual_Roots  <- read.csv("Data/Virtual Roots/Virtual_Root_2023-07-17_30x20.csv")
Barriers       <- read_xlsx("Data/Barriers.xlsx")
Conductivities <- read.csv(file = paste0(simu_path, "Conductivities_full.csv"))

source("src/FUNCTIONS/T-Root/Functions.R")
#==================================================================================
# Clean data and create dico and mono
Conductivities_processed          <- set_conductivities(Conductivities, Barriers = c("b1", "b3", "b4", "b6", "b9", "b8"))

#==================================================================================
# Change maturation stage name :
Conductivities_processed$Barrier  <- as.factor(Conductivities_processed$Barrier)
Conductivities_processed          <- left_join(Conductivities_processed, Barriers[c("Barrier", "Barrier_Name")])
#==================================================================================
# Check that the data is okey (black points have to be +- homogenous) :
ggplot(data = Conductivities_processed, aes(x = x, y = root)) +
  geom_point() +
  ggtitle("Conductivities") +
  theme_bw()

# Export
write.csv(Conductivities_processed, file = paste0("Data/Conductivities_processed.csv"), row.names = F)
```

Create Data Full

```{r, eval = F, include = F}
Parameters     <- read.csv("Data/Anatomy/Parameters.csv")
Virtual_Roots <- read.csv("Data/Virtual Roots/Virtual_Root_2023-07-17_30x20.csv")
Virtual_Roots <- left_join(Virtual_Roots, Parameters[c("name", "type", "param_id")])

data_full1 <- left_join(Conductivities_processed, Virtual_Roots)
data_full1$kAQP <- as.factor(data_full1$kAQP)

Combinations <- unique(data_full1[c("root", "x", "kAQP", "Barrier_Name")]) %>% mutate(Combination_ID = paste0(root, "_", x, "_", kAQP, "_", Barrier_Name))

# Isolate Kr, Kx, kr, radius per COmbination_ID
data_full2 <- left_join(data_full1, Combinations)
data_full2 <- unique(data_full2[c("Kr", "Kx", "kr", "radius", "Combination_ID")])

# Isolate parameters per Combination_ID
data_full3 <- left_join(data_full1, Combinations)
data_full3 <- unique(data_full3[c("Combination_ID", "param_id", "y")])
data_full3 <- data_full3 %>% spread(key = param_id, value = y)

# Join both
data_final <- left_join(data_full2, data_full3)
data_final <- left_join(data_final, Combinations)

# Export final database
write.csv(data_final, "Data/DATA_FULL_FINAL.csv", row.names = F)
```

# LOAD PRE-PROCESSED DATA

```{r Load Data}
Conductivities_processed <- read.csv("Data/Conductivities_processed.csv")
Anatomy_Full             <- read.csv("Data/Anatomy/Anatomy_Full.csv")
Data_Full                <- read.csv("Data/DATA_FULL_FINAL.csv")
Parameters               <- read.csv("Data/Anatomy/Parameters.csv")

# Remove day zero
Conductivities_processed <- Conductivities_processed %>% filter(x != 0)
Data_Full <- Data_Full %>% filter(x != 0)
```

# VISUAL ANALYSIS

## Plot pure data

```{r Plot Pure Data}
# kr vs kAQP
kAQP_plot1 <- ggplot(data = Conductivities_processed,
                     aes(x=(kAQP*10000), 
                         y = kr*1e08,
                         color = Barrier_Name))+
  geom_point(aes(x = kAQP*10000),
             position = "jitter",
             alpha = 0.05) +
  # geom_boxplot(aes(x = as.factor(kAQP*10000), y = kr, color = Barrier))+
  # facet_wrap(~Barrier) +
  # scale_color_viridis() +
  geom_smooth(linewidth = 2) +
  ylab(expression(k[r] ~ 10^{8} ~ "[" * m ~ MPa^{-1} ~ s^{-1}*"]")) +
  # xlab("kAQP [10e-04 cm hPA-1 d-1]") +
  xlab(expression(kAQP ~ 10^{-4} ~ "[" * cm ~ hPa^{-1} ~ d^{-1} * "]")) +
  ylim(2, 12) +
  theme_test() 
  # theme(legend.position = "none")
kAQP_plot1
# ggsave(filename = "plots/AQP_influence.svg", plot = kAQP_plot1, device = "svg", width = 4, height = 3, units = "in")
#============================================================================
# kr
kr_plot1 <- ggplot(data = Conductivities_processed,
       aes(x = x, 
           y = kr*10^8,
           color = kAQP*1e7)) +
  geom_point(alpha = 0.5, position = "jitter") +
  facet_wrap(~Barrier_Name) +
  scale_color_viridis() +
  # geom_smooth(aes(x = x, y = radius/5000000), color = "red") +
  # ylim(0, 3e-08) +
  ylab(expression(k[r] ~ 10^{-8} ~ "[" ~ m~ s^{-1} ~ MPa^{-1} ~ "]")) +
  labs(color = expression(kAQP ~  "[" ~ 10^{-7} ~ m ~ s^{-1} ~ MPa^{-1} ~ "]")) +
  xlab("Age [d]") +
  # ggtitle("Hydraulic Radial conductivity") +
  theme_bw()
kr_plot1
#============================================================================
# Kr_plot1 <- ggplot(data = Conductivities_processed,
#        aes(x = x, 
#            y = Kr,
#            color = kAQP*1e7)) +
#   geom_jitter(alpha = 0.2) +
#   facet_wrap(~Barrier_Name) +
#   scale_color_viridis() +
#   ylab(expression(K[r] ~ "[" ~ m^{3} ~ s^{-1} ~ MPa^{-1} ~ "]")) + 
#   xlab("Age [d]") +
#   # ylim(0, 3e-08) +
#   labs(color = expression(kAQP ~  "[" ~ 10^{-7} ~ m ~ s^{-1} ~ MPa^{-1} ~ "]")) +
#   theme_dark()
# Kr_plot1
#============================================================================
# Radius
Radius_plot1 <- ggplot(data = Conductivities_processed,
                       aes(x = x, y = radius)) +
  geom_point(alpha = 0.01) +
  # geom_smooth() +
  theme_test() +
  ylab("Radius [mm]") +
  xlab("Age [d]") 

Radius_plot1
#============================================================================
# Perimeter
Perimeter_plot1 <- ggplot(data = Conductivities_processed,
                       aes(x = x, y = perimeter)) +
  geom_point(alpha = 0.01) +
  # geom_smooth() +
  theme_test() +
  ylab("Perimeter [cm]") +
  xlab("Age [d]") 

Perimeter_plot1
#============================================================================
# Kx
kx_plot1 <- ggplot(data = Conductivities_processed%>%
                     filter(Barrier_Name == "T1" & kAQP == min(Conductivities_processed$kAQP)),
       aes(x = x, 
           y = Kx,
           color = radius)) +
  geom_point(alpha = 1) +
  # geom_smooth(method = "lm") +
  scale_y_log10() +
  # geom_smooth(method = "lm", se = T) +
  scale_color_viridis(option = "magma", direction = 1) +
  # ylim(0, 3e-08) +
  ylab(expression(ln(K[x]) ~ "[" ~ m^{4} ~ s^{-1} ~ hPa^{-1} ~ "]")) +
  xlab("Age [d]") +
  labs(color = "Radius [cm]") +
  # ggtitle("Hydraulic axial conductance") +
  theme_bw()
kx_plot1
```

Export plots

```{r Export graphs, eval = F, include=F}
svg("Plots/kAQP_1.svg", height = 4, width = 6)
kAQP_plot1
dev.off()

png("Plots/kr_plot_1.png", height = 5, width = 8, units = "in", res = 300)
kr_plot1 
dev.off()

png("Plots/Kx_plot_1.png", height = 3, width = 5, units = "in", res = 300)
kx_plot1
dev.off()

svg("Plots/Kr_plot_1.svg", height = 5, width = 8)
Kr_plot1
dev.off()

svg("Plots/Radius_plot_1.svg", height = 5, width = 8)
Radius_plot1
dev.off()

svg("Plots/Perimeter_plot_1.svg", height = 3, width = 8)
Perimeter_plot1
dev.off()
```

# Statistical Analysis per variable

## 0) Global Correlations

```{r Correlations}
library(corrplot)

print(colnames(Data_Full))

Data_Full_2cor <- Data_Full %>% 
  select(-any_of(c("endodermis_n_layers", 
                   "epidermis_n_layers",
                   "pericycle_n_layers",
                   "xylem_n_files", 
                   "exodermis_n_layers",
                   "Combination_ID", 
                   "root", 
                   "Barrier_Name",
                   "Barrier")
  ))

Data_Full_2cor <- as_tibble(scale(Data_Full_2cor))
                   

# svg(filename = "plots/Results_Correlations.svg", width = 7, height = 7)
corrplot(cor(Data_Full_2cor), method = 'color')
# dev.off()
```

## 1) Effect of Radius

### 1.1) Regression of radius from quantification data

```{r Radius plot}
radius_df <- Anatomy_Full[c("age", "radius")]

# PLot
r_plot2 <- ggplot(data = radius_df, aes(x = age, y = radius))+
  # ylim(0, 0.8) +
  geom_point() +
  # geom_smooth(formula = y~x) +
  theme_bw() +
  ggtitle("Radius of the data")

# svg(filename = paste0("Plots/Radius_data.svg"), width = 5, height = 5)
r_plot2
# dev.off()
```

To regress that, we split in two half : - If x is \< 25, we consider the radius as constant = 0.188 - If x is \>= 25, we consider exponential function

```{r Radius Regression}
# FIRST STAGE
radius_df1 <- radius_df %>% filter(age < 25)
radius_df2 <- radius_df %>% filter(age >= 25)
radius_df2$radius_ln <- ln(radius_df2$radius)
summary(radius_df1$radius)

rlm1 <- lm(data = radius_df1, formula = radius ~ 1)
summary(rlm1)

# SECOND STAGE
rlm2 <- lm(data = radius_df2, formula = radius_ln ~ age)
summary(rlm2)
plot(rlm2)
visreg(rlm2)
```

Okey, so this is nice. With these two regression function, we coded the "radius" function.

### 1.2) Effect of radius on kr

Here we start by looking at the relation between kr, root age and root radius, per Maturation Stage, at fixed kAQP (= 4e-04). We split in two : between 0 and 25 days their is \~linear increase in kr. After 25 days, kr drops linarly.

```{r Effect of radius on kr}
# =============================================================================
subset1 <- Conductivities_processed %>% filter(x < 25)
subset2 <- Conductivities_processed %>% filter(x >= 25)

subset1_1 <- subset1%>%filter(kAQP == "4e-04")
subset2_1 <- subset2%>%filter(kAQP == "4e-04")

cor(subset1$kr, subset1$radius)
cor(subset2$kr, subset2$radius)

#===============================================================================
# Individual MS

MS_indi <- ggplot(data = Conductivities_processed%>%filter(kAQP == "4e-04")) +
  geom_point(aes(x = x, y = kr), color = "blue", alpha = 0.3) + 
  # geom_smooth(aes(x = x, y = kr), color = "blue") +
  geom_smooth(data = subset1_1, aes(x = x, y = kr), color = "blue", method = "lm") +
  geom_smooth(data = subset2_1, aes(x = x, y = kr), color = "blue", method = "lm") +
  
  geom_point(aes(x = x, y = radius/(1e07)), color = "red",alpha = 0.3) +
  geom_smooth(aes(x= x , y =radius/(1e07)), color = "red") +
  facet_wrap(~Barrier) +
  ggtitle("Full Timeline") +
  theme_test()
  
MS_indi

#===============================================================================
MS_indi2 <- ggplot(data = subset1_1) +
  geom_point(aes(x = x, y = kr), color = "blue", alpha = 0.3) +
  geom_smooth(aes(x = x, y = kr), color = "blue", method = 'lm') +
  
  geom_point(aes(x = x, y = radius/(1e07)), color = "red", alpha = 0.3) +
  geom_smooth(aes(x= x , y =radius/(1e07)), color = "red", method = 'lm') +
  facet_wrap(~Barrier) +
  ggtitle("First Stage") +
  theme_test()
MS_indi2

#===============================================================================
MS_indi3 <- ggplot(data = subset2_1) +
  geom_point(aes(x = x, y = kr), color = "blue", alpha = 0.3) + 
  geom_smooth(aes(x = x, y = kr), color = "blue", method = 'lm') +
  
  geom_point(aes(x = x, y = radius/(1e07)), color = "red", alpha = 0.3) +
  geom_smooth(aes(x= x , y =radius/(1e07)), color = "red", method = 'lm') +
  facet_wrap(~Barrier) +
  ggtitle("Second Stage") +
  theme_test()
MS_indi3
```

Simple linear model ? Just to see in constant kAQP and MS Not efficient

```{r}
print("FIRST PHASE")
rad_lm <- lm(data = subset1_1, formula = kr ~ x + radius + Barrier)
summary(rad_lm)
anova(rad_lm)

print("SECOND PHASE")
rad_lm <- lm(data = subset2_1, formula = kr ~ x + radius + Barrier + radius:Barrier)
summary(rad_lm)
anova(rad_lm)
```

## 2) Influence of Aquaporins

```{r}
ggplot(data = Conductivities_processed) +
  geom_jitter(aes(x = kAQP*10000, y = kr, color = Barrier), alpha = 0.1) +
  geom_smooth(aes(x = kAQP*10000, y = kr, color = Barrier)) +
  # facet_wrap(~Barrier) +
  
  theme_test()

kAQP_lm <- lm(data = Conductivities_processed, formula = kr ~ kAQP*Barrier)
anova(kAQP_lm)
```

## 3) Influence of Deposition Levels

Globally, we clearly see that all maturation stages are different and significantly.

```{r}
ggplot(data = Conductivities_processed) +
  # geom_jitter(aes(x = kAQP, 
  #                 y = kr*10^8, 
  #                 color = Barrier_Name),
  #             alpha = 0.75) +
  geom_boxplot(aes(x = as.factor(kAQP), y = kr*10^8, fill = Barrier_Name)) +
  ylab("Kr [10^-8]") +
  xlab("kAQP") +
  theme_classic() + theme(axis.text.x     = element_text(size = 8, angle = 90, hjust = 1, vjust = 0.5),) 
```


```{r}
# MS_subset <- Conductivities %>% filter(kAQP == 5e-04)
MS_all <- ggplot(data = Conductivities_processed) +
  
  geom_jitter(aes(x = Barrier_Name, 
                  y = kr*10^08, 
                  color = kAQP), 
              width = 0.1, 
              alpha = 0.1) +
  
  geom_violin(aes(x = Barrier_Name, 
                  y = kr*10^08), 
              alpha = 0.1,
              draw_quantiles = "0.5") +

  # geom_boxplot(aes(x = Barrier_Name, 
  #                  y = kr*10^8),
  #              width = 0.5,
  #              alpha = 0.5) +
  
  xlab("Maturation Stage") +
  ylab(expression(k[r] ~ "[" ~ 10^{-08} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  # scale_fill_manual(values=c("white","white","white", "grey", "grey", "grey")) +
  scale_color_viridis() +
  
  theme_classic() 
  # ggtitle("Radial Hydraulic Conductivity per hydrophobic deposition level") 
  # theme(legend.position = "none") 

MS_all
ggsave(filename = "Plots/Maturation_Stages_All.png", plot = MS_all, device = "png", 
       width = 5, height = 4, dpi = 300, units = "in")

# svg("Plots/Maturation_Stages_All.svg", height = 4, width = 5)
# MS_all
# dev.off()
```

Stats :

```{r}
MS_lm <- lm(data = Conductivities_processed, formula = kr ~ Barrier_Name)

summary(MS_lm)
anova(MS_lm)
emmeans(MS_lm, specs = pairwise ~ Barrier_Name)

# visreg(MS_lm)

DL_pred <- tibble(DL = c("M1", "M2", "M3", "T1", "T2", "T3"),
                  Estimate = MS_lm$coefficients)

DL_pred2 <- tibble(DL2 = c("M1", "M2", "M3", "T1", "T2", "T3"),
                  Estimate2 = MS_lm$coefficients)

EM <- emmeans(MS_lm, specs = pairwise ~ Barrier_Name)
DL_mean <- as_tibble(EM$emmeans)
DL_contrast <- as_tibble(EM$contrasts)
```

Some interesting stats :

```{r}
mean_M1 <- DL_mean$emmean[DL_mean$Barrier_Name == "M1"]
mean_M2 <- DL_mean$emmean[DL_mean$Barrier_Name == "M2"]
mean_M3 <- DL_mean$emmean[DL_mean$Barrier_Name == "M3"]
mean_T1 <- DL_mean$emmean[DL_mean$Barrier_Name == "T1"]
mean_T2 <- DL_mean$emmean[DL_mean$Barrier_Name == "T2"]
mean_T3 <- DL_mean$emmean[DL_mean$Barrier_Name == "T3"]

print(paste0("Difference between T1 and M1 [%] : ", (mean_M1-mean_T1)*100/mean_M1))
print(paste0("Difference between T2 and T1 [%] : ", (mean_T1-mean_T2)*100/mean_T1))
print(paste0("Difference between T3 and T1 [%] : ", (mean_T1-mean_T3)*100/mean_T1))
print(paste0("Difference between M2 and M3 [%] : ", (mean_M2-mean_M3)*100/mean_M2))
```

# COMPLETE STATISTICAL ANALYSIS

## 1) Radial conductivity

```{r}
# lm_kr0 <- lm(data = Conductivities_processed, formula = kr ~ x + radius + Barrier + kAQP + kAQP:Barrier)
lm_kr0 <- lm(data = Data_Full 
             # %>% filter(Barrier_Name %in% c("T1", "T2", "T3"))
             , 
             formula = kr ~ 
               x + 
               radius + 
               Barrier_Name + 
               kAQP + 
               kAQP:Barrier_Name 
               # cortex_n_layers + 
               # endodermis_cell_diameter +
               # cortex_cell_diameter + 
               # stele_layer_diameter
               )
summary(lm_kr0)
anova(lm_kr0)
emmeans(lm_kr0, specs = pairwise ~ Barrier_Name:kAQP)
```

```{r}
# IN CASE OF ALL DEPOSITION LEVELS
coefficients_kr <- tibble(a = lm_kr0$coefficients[1],
                          x = lm_kr0$coefficients[2],
                          r = lm_kr0$coefficients[3],
                          M2 = lm_kr0$coefficients[4],
                          M3 = lm_kr0$coefficients[5],
                          T1 = lm_kr0$coefficients[6],
                          T2 = lm_kr0$coefficients[7],
                          T3 = lm_kr0$coefficients[8],
                          kAQP = lm_kr0$coefficients[9],
                          M2_kAQP = lm_kr0$coefficients[10],
                          M3_kAQP = lm_kr0$coefficients[11],
                          T1_kAQP = lm_kr0$coefficients[12],
                          T2_kAQP = lm_kr0$coefficients[13],
                          T3_kAQP = lm_kr0$coefficients[14])

# IN CASE OF ONLY TOMATO DL
# coefficients_kr <- tibble(a = lm_kr0$coefficients[1],
#                           x = lm_kr0$coefficients[2],
#                           r = lm_kr0$coefficients[3],
#                           T2 = lm_kr0$coefficients[4],
#                           T3 = lm_kr0$coefficients[5],
#                           kAQP = lm_kr0$coefficients[6],
#                           T2_kAQP = lm_kr0$coefficients[7],
#                           T3_kAQP = lm_kr0$coefficients[8])
                    
pander(coefficients_kr)
write.csv(coefficients_kr, "./Data/kr_coefficients.csv", row.names = F)
```

```{r}
source("src/FUNCTIONS/T-Root/Functions.R")
kr_reg_df <- Data_Full[c("kr", "Combination_ID", "x", "radius", "Barrier_Name", "kAQP")] 
kr_reg_df$kr_reg <- NaN

for(i in 1:nrow(kr_reg_df)){
  kr_reg_df$kr_reg[i] <- kr_reg(x = kr_reg_df$x[i], 
                                MS = kr_reg_df$Barrier_Name[i]
                                , kAQP = kr_reg_df$kAQP[i]
                                , radius = kr_reg_df$radius[i]
                                , coef = coefficients_kr)
}

cor <- cor.test(kr_reg_df$kr, kr_reg_df$kr_reg)
print(cor)
kr_test <- lm(data = kr_reg_df, formula = kr_reg~kr)
summary(kr_test)

ggplot(kr_reg_df) +
  geom_point(aes(x = kr, y = kr_reg, color = x),
             alpha = 0.4) +
  geom_smooth(aes(x = kr, y = kr_reg), method = "lm", color = "red") +
  coord_fixed() +
  # xlim(-27, -18) +
  # ylim(-27, -18) +
  geom_abline() +
  scale_color_viridis() +
  ggtitle(paste0("Correlation : ", round(cor$estimate, digits = 2),
                 " | R2 = ", 
                 round(summary(kr_test)$r.squared, digits = 2)
                 )
          ) +
  xlab("kr") + ylab("kr*") +
  theme_classic()


```

Let's compute final coefficients for the regression equation :

$$
k_r^* \cdot 10^8 = 
  \begin{cases}
    \alpha_{T1} + \beta \cdot t + \gamma \cdot r + \delta_{T1} \cdot kAQP & \text{if} & DL = T1 \\
    \alpha_{T2} + \beta \cdot t + \gamma \cdot r + \delta_{T2} \cdot kAQP & \text{if} & DL = T2  \\
    \alpha_{T3} + \beta \cdot t + \gamma \cdot r + \delta_{T3} \cdot kAQP & \text{if} & DL = T3
  \end{cases}
$$

```{r}
# T1 :
cat("alpha_T1 : ", (coefficients_kr$a)*1e8, "(x 10e-8) \n")
cat("alpha_T2 : ", (coefficients_kr$a + coefficients_kr$T2)*1e8, "(x 10e-8) \n")
cat("alpha_T3 : ", (coefficients_kr$a + coefficients_kr$T3)*1e8, "(x 10e-8) \n")
cat("\n")
cat("beta : ", (coefficients_kr$x)*1e8, "(x 10e-8) \n")
cat("gamma : ", (coefficients_kr$r)*1e8, "(x 10e-8) \n")
cat("\n")
cat("delta_T1 : ", (coefficients_kr$kAQP)*1e8*1e-06, "(x 10e-8 x 10e6) \n")
cat("delta_T2 : ", (coefficients_kr$kAQP + coefficients_kr$T2_kAQP)*1e8*1e-6, "(x 10e-8 x 10e6) \n")
cat("delta_T3 : ", (coefficients_kr$kAQP + coefficients_kr$T3_kAQP)*1e8*1e-5, "(x 10e-8 x 10e5) \n")
```
This is very nice. So we see different informations : \
* The whole linear model is significant at R2 = 0.918 \
* On the ANOVA, all variables are significant \ 
* The less significant factor is T2 (p = 0.0178).\

Really nice !

## 2) Axial Kr

```{r}
Kx_lm <- lm(data = Data_Full%>%filter(Barrier_Name == "T1" & kAQP == 1.1570e-07), 
            formula = ln(Kx) ~ radius + x)

summary(Kx_lm)
anova(Kx_lm)
plot(Kx_lm)

coefficients_Kx <- tibble(a   = Kx_lm$coefficients[1],
                          r   = Kx_lm$coefficients[2],
                          x   = Kx_lm$coefficients[3],
                          xms = Kx_lm$coefficients[4])
write.csv(coefficients_Kx, "./Data/Kx_coefficients.csv", row.names = F)
```

$$
ln(K_x^*) = \alpha + \beta \cdot t + \gamma \cdot r
$$

```{r}
cat("alpha = ", coefficients_Kx$a, "\n")
cat("beta = ", coefficients_Kx$x, "\n")
cat("gamma = ", coefficients_Kx$r, "\n")
```

```{r}
Kx_reg <- Data_Full[c("Kx", "Combination_ID", "x", "radius", "xylem_max_size")] %>% 
  mutate(Kx_reg = exp(coefficients_Kx$a + coefficients_Kx$r*radius + coefficients_Kx$x*x))

ggplot(Kx_reg) +
  geom_point(aes(x = ln(Kx), y = ln(Kx_reg), color = x)) +
  geom_smooth(aes(x = ln(Kx), y = ln(Kx_reg)), method = "lm", color = "red") +
  coord_fixed() +
  xlim(-26.5, -18) +
  ylim(-26.5, -18) +
  xlab("ln(Kx)") + ylab("ln(Kx*)") +
  geom_abline() +
  scale_color_viridis() +
  theme_classic()
  
# ==============================================================================
```

# PREDICTION CURVES

Here we build and plot conductivities curves that we will apply in MARSHAL.

```{r}
coefficients_kr <- read.csv("./Data/kr_coefficients.csv")
coefficients_Kx <- read.csv("./Data/Kx_coefficients.csv")

source("./src/FUNCTIONS/T-Root/Functions.R")
```

## Scenario 1A : 

* Secondary Growth

* LC + Sub in exo

* Fixed kAQP

```{r}
# Create Reg2
Reg_1A                     <- tibble(x = seq(1:30))
Reg_1A$radius              <- radius_reg(Reg_1A$x)
Reg_1A$radius[Reg_1A$x > 30] <- Reg_1A$radius[Reg_1A$x == 30]
Reg_1A$MS                  <- 0
Reg_1A$kAQP                <- mean(unique(Data_Full$kAQP)) 

# Set maturation stages timing
timing                       <- c(7, 31)
Reg_1A$MS[Reg_1A$x <= timing[1]] <- "T1"
Reg_1A$MS[Reg_1A$x>timing[1]&
          Reg_1A$x<timing[2]]  <- "T2"
Reg_1A$MS[Reg_1A$x >= timing[2]] <- "T3"

Reg_1A$kr <- 0
Reg_1A$Kx <- 0
Reg_1A$Kr <- 0

# Loop for each day
for(i in 1:nrow(Reg_1A)){
  Reg_1A$kr[Reg_1A$x == i] <- kr_reg(x = Reg_1A$x[i], 
                                 MS = Reg_1A$MS[i], 
                                 kAQP = Reg_1A$kAQP[i], 
                                 radius = Reg_1A$radius[i], 
                                 coef = coefficients_kr)
  Reg_1A$Kx[Reg_1A$x == i] <- Kx_reg(x = Reg_1A$x[i], 
                                 radius = Reg_1A$radius[i], 
                                 coef = coefficients_Kx)
}

Reg_1A$Kr <- Reg_1A$kr * 2 *3.1415 * Reg_1A$radius/1000
# 
# Reg_1A$Kx[Reg_1A$x > 30] <- Reg_1A$Kx[Reg_1A$x == 30]

write.csv(Reg_1A, "./Data/conds_scenarios/1A.csv")
```

```{r}
Reg_plot <- ggplot(data = Reg_1A) +
  geom_line(aes(x = x, y = kr*1e8), color = "red", linewidth = 1) +
  geom_line(aes(x = x, y = Kx*1e9), color = "blue", linewidth = 1) +
  geom_line(aes(x = x, y = Kr*1e11), color = "green", linewidth = 1) +
  geom_line(aes(x = x, y = kAQP*1e7), color = "orange", linewidth = 1, linetype = 2) +
  geom_line(aes(x = x, y = radius*1e1), color = "grey", linewidth = 1, linetype = 2) +
  xlim(0, 30) +
  ylim(0, 16) +
  ylab("") +
  theme_test()
Reg_plot

svg("plots/Conds_curves_1A.svg", width = 2, height = 2)
Reg_plot
dev.off()
```

## Scenario 1B :

* Secondary Growth

* LC + Sub in exo

* Decreasing kAQP

```{r}
# Create kAQP function
kAQP_fun <- function(x, th = 10, delta = 1, max = 1.16e-6,  min = 1.16e-7){
  if(x < th){
    kaqp <- max
  }else{
    kaqp <- max - delta*(x - th)*max 
  }
  
  if(kaqp < min){
    kaqp <- min
    }
  
  return(kaqp)
}

# Create Reg_1B
Reg_1B <- tibble(x = seq(1:30))
Reg_1B$radius <- radius_reg(Reg_1B$x)
Reg_1B$radius[Reg_1B$x > 30] <- Reg_1B$radius[Reg_1B$x == 30]
Reg_1B$MS <- 0

# Set maturation stages timing
timing <- c(7, 31)
Reg_1B$MS[Reg_1B$x <= timing[1]] <- "T1"
Reg_1B$MS[Reg_1B$x > timing[1]]   <- "T2"

Reg_1B$kr <- 0
Reg_1B$Kx <- 0
Reg_1B$Kr <- 0

Reg_1B$kAQP <- sapply(Reg_1B$x, kAQP_fun, th = 10, delta = 0.05, max = 1.16e-6,  min = 0)

# Loop for each day
for(i in 1:nrow(Reg_1B)){
  Reg_1B$kr[Reg_1B$x == i] <- kr_reg(x = Reg_1B$x[i], 
                                 MS = Reg_1B$MS[i], 
                                 kAQP = Reg_1B$kAQP[i], 
                                 radius = Reg_1B$radius[i], 
                                 coef = coefficients_kr)
  Reg_1B$Kx[Reg_1B$x == i] <- Kx_reg(x = Reg_1B$x[i], 
                                 radius = Reg_1B$radius[i], 
                                 coef = coefficients_Kx)
}

Reg_1B$Kr <- Reg_1B$kr * 2 *3.1415 * Reg_1B$radius/1000
# Reg_1B$Kx[Reg_1B$x > 30] <- Reg_1B$Kx[Reg_1B$x == 30]

write.csv(Reg_1B, "./Data/conds_scenarios/1B.csv")
# ==============================================================================

Reg_plot <- ggplot(data = Reg_1B) +
  geom_line(aes(x = x, y = kr*1e8), color = "red", linewidth = 1) +
  geom_line(aes(x = x, y = Kx*1e9), color = "blue", linewidth = 1) +
  geom_line(aes(x = x, y = Kr*5e10), color = "green", linewidth = 1) +
  geom_line(aes(x = x, y = kAQP*1e7), color = "orange", linewidth = 1, linetype = 2) +
  geom_line(aes(x = x, y = radius*1e1), color = "grey", linewidth = 1, linetype = 2) +
  ylab("") +
  xlim(0, 30) +
  ylim(0, 16) +
  theme_test()
Reg_plot

svg("plots/Conds_curves_1B.svg", width = 2, height = 2)
Reg_plot
dev.off()
```

## Scenario 2 : No exodermis suberization

Here we simulate the same root (with secondary growth), but with no exodermal suberization

```{r}
source("./src/FUNCTIONS/T-Root/Functions.R")
# Create Reg_2
Reg_2                     <- tibble(x = seq(1:30))
Reg_2$radius              <- radius_reg(Reg_2$x)
Reg_2$radius[Reg_2$x > 30] <- Reg_2$radius[Reg_2$x == 30]
Reg_2$MS                  <- 0
Reg_2$kAQP                <- mean(unique(Data_Full$kAQP)) 

# Set maturation stages timing
timing                       <- c(7, 31)
Reg_2$MS <- "T1"
# Reg_2$MS[Reg_2$x > timing[1]]  <- "T2"

Reg_2$kr <- 0
Reg_2$Kx <- 0
Reg_2$Kr <- 0

# Loop for each day
for(i in 1:nrow(Reg_2)){
  Reg_2$kr[Reg_2$x == i] <- kr_reg(x = Reg_2$x[i], 
                                 MS = Reg_2$MS[i], 
                                 kAQP = Reg_2$kAQP[i], 
                                 radius = Reg_2$radius[i], 
                                 coef = coefficients_kr)
  Reg_2$Kx[Reg_2$x == i] <- Kx_reg(x = Reg_2$x[i], 
                                 radius = Reg_2$radius[i], 
                                 coef = coefficients_Kx)
}

Reg_2$Kr <- Reg_2$kr * 2 *3.1415 * Reg_2$radius/1000

write.csv(Reg_2, "./Data/conds_scenarios/2.csv")
# ==============================================================================

Reg_plot <- ggplot(data = Reg_2) +
  geom_line(aes(x = x, y = kr*1e8), color = "red", linewidth = 1) +
  geom_line(aes(x = x, y = Kx*1e9), color = "blue", linewidth = 1) +
  geom_line(aes(x = x, y = Kr*1e11), color = "green", linewidth = 1) +
  geom_line(aes(x = x, y = kAQP*1e7), color = "orange", linewidth = 1, linetype = 2) +
  geom_line(aes(x = x, y = radius*1e1), color = "grey", linewidth = 1, linetype = 2) +
  xlim(0, 30) +
  ylim(0, 16) +
  ylab("") +
  theme_test()
Reg_plot

svg("plots/Conds_curves_2.svg", width = 2, height = 2)
Reg_plot
dev.off()
```

## Scenario 3 : No secondary growth

Finally, here we simulate root with NO secondary growth and NO exodermal suberization

```{r}
source("./src/FUNCTIONS/T-Root/Functions.R")
# Create Reg_3
Reg_3                     <- tibble(x = seq(1:30))
Reg_3$radius              <- radius_reg(Reg_3$x[1]) # Keep radius constant
Reg_3$MS                  <- 0
Reg_3$kAQP                <- mean(unique(Data_Full$kAQP)) 

# Set maturation stages timing
timing                       <- c(7, 31)
Reg_3$MS <- "T1"
# Reg_3$MS[Reg_3$x > timing[1]]  <- "T2"

Reg_3$kr <- 0
Reg_3$Kx <- 0
Reg_3$Kr <- 0

# Loop for each day
for(i in 1:nrow(Reg_3)){
  Reg_3$kr[Reg_3$x == i] <- kr_reg(x = Reg_3$x[i], 
                                 MS = Reg_3$MS[i], 
                                 kAQP = Reg_3$kAQP[i], 
                                 radius = Reg_3$radius[i], 
                                 coef = coefficients_kr)
  Reg_3$Kx[Reg_3$x == i] <- Kx_reg(x = Reg_3$x[i], 
                                 radius = Reg_3$radius[i], 
                                 coef = coefficients_Kx)
}

Reg_3$Kr <- Reg_3$kr * 2 *3.1415 * Reg_3$radius/1000
# 
# Reg_3$Kx[Reg_3$x > 30] <- Reg_3$Kx[Reg_3$x == 30]

write.csv(Reg_3, "./Data/conds_scenarios/3.csv")
# ==============================================================================

Reg_plot <- ggplot(data = Reg_3) +
  geom_line(aes(x = x, y = kr*1e8), color = "red", linewidth = 1) +
  geom_line(aes(x = x, y = Kx*1e9), color = "blue", linewidth = 1) +
  geom_line(aes(x = x, y = Kr*1e11), color = "green", linewidth = 1) +
  geom_line(aes(x = x, y = kAQP*1e7), color = "orange", linewidth = 1, linetype = 2) +
  geom_line(aes(x = x, y = radius*1e1), color = "grey", linewidth = 1, linetype = 2) +
  xlim(0, 30) +
  ylim(0, 16) +
  ylab("") +
  theme_test()
Reg_plot

svg("plots/Conds_curves_3.svg", width = 2, height = 2)
Reg_plot
dev.off()
```

## Plot all scenarios

```{r}
colors <- c("kAQP"   = "red", 
            "kr"     = "blue", 
            "Kx"     = "orange", 
            "Kr"     = "lightblue4", 
            "radius" = "grey"
            )

plot_scenario <- function(df, color.values, to.scale) {
  # Scale the specified columns and gather them into long format
  
  data2plot <- df 
  for(i in colnames(data2plot)){
    if(i %in% to.scale){
      data2plot[i] = scale(data2plot[i])
    }else{
      if(i %in% c("x", "MS")){
        next
      }else{
        data2plot[i] = 0
      }
    }
  }
  
  data2plot <- data2plot %>% gather(kr, Kr, Kx, kAQP, radius, key = Variable, value = Value)  
  
  # Create the plot
  plot <- ggplot(data2plot) +
    geom_line(aes(x = x, y = Value, color = Variable), 
              linewidth = 2) +
    scale_color_manual(values = color.values) +
    theme_classic() +
    ylab("Value [relative]")

  return(plot)
}

plot_scenario(df = Reg_1A, color.values = colors, to.scale = c("kr", "Kr", "Kx", "radius"))
plot_scenario(df = Reg_1B, color.values = colors, to.scale = c("kr", "Kr", "Kx", "radius", "kAQP"))
plot_scenario(df = Reg_2, color.values = colors, to.scale = c("kr", "Kr", "Kx", "radius"))
plot_scenario(df = Reg_3, color.values = colors, to.scale = c("kr", "Kr", "Kx"))
```

Plot all together

```{r}
Scenarios_df <- Reg_1A %>% mutate(Scenario = "S1A") %>% 
  rbind(Reg_1B %>% mutate(Scenario = "S1B")) %>% 
  rbind(Reg_2 %>% mutate(Scenario = "S2")) %>% 
  rbind(Reg_3 %>% mutate(Scenario = "S3")) 

for(i in c("kr", "Kr", "Kx", "kAQP", "radius")){
  Scenarios_df[i] <- scale(Scenarios_df[i])
}

Scenarios_df <- Scenarios_df %>% 
  gather(kr, Kr, Kx, radius, kAQP, key = Variable, value = Value)

rect_data <- expand.grid(start = 0, end = 0, MS = c("T1", "T2"), Scenario = unique(Scenarios_df$Scenario))

rect_data$start[rect_data$Scenario == "S1A" & rect_data$MS == "T1"] <- 1
rect_data$end[rect_data$Scenario == "S1A" & rect_data$MS == "T1"]   <- 7
rect_data$start[rect_data$Scenario == "S1A" & rect_data$MS == "T2"] <- 8
rect_data$end[rect_data$Scenario == "S1A" & rect_data$MS == "T2"]   <- 30

rect_data$start[rect_data$Scenario == "S1B" & rect_data$MS == "T1"] <- 1
rect_data$end[rect_data$Scenario == "S1B" & rect_data$MS == "T1"]   <- 7
rect_data$start[rect_data$Scenario == "S1B" & rect_data$MS == "T2"] <- 8
rect_data$end[rect_data$Scenario == "S1B" & rect_data$MS == "T2"]   <- 30

rect_data$start[rect_data$Scenario == "S2" & rect_data$MS == "T1"] <- 1
rect_data$end[rect_data$Scenario == "S2" & rect_data$MS == "T1"]   <- 30
rect_data$start[rect_data$Scenario == "S2" & rect_data$MS == "T2"] <- 0
rect_data$end[rect_data$Scenario == "S2" & rect_data$MS == "T2"]   <- 0

rect_data$start[rect_data$Scenario == "S3" & rect_data$MS == "T1"] <- 1
rect_data$end[rect_data$Scenario == "S3" & rect_data$MS == "T1"]   <- 7
rect_data$start[rect_data$Scenario == "S3" & rect_data$MS == "T2"] <- 8
rect_data$end[rect_data$Scenario == "S3" & rect_data$MS == "T2"]   <- 30

library(ggthemes)
S_full_plot <- ggplot(data = Scenarios_df) +
  
  # From an idea of Théo M. Degand (UCLouvain, CCMN)
  geom_rect(data = rect_data, 
            aes(xmin = start, xmax = end, 
                ymin = -Inf, ymax = Inf, 
                fill = MS
                ),
    alpha = 0.2
  ) +
  
  # Display curves
  geom_line(aes(x = x, y = Value, 
                color = Variable),
            linewidth = 1) +
  
  scale_color_manual(values = colors) +
  facet_wrap(~Scenario) +
  ylab("Value [normalised]") +
  xlab("Root age [d]") +
  theme_few() 

ggsave(plot = S_full_plot, filename = "plots/Scenarios_full.svg", device = "svg", width = 5, height = 5)
```

# Error bar plots

Define data : In this chunk we

1\) Create a dataframe where we store mean values and errors bars for constant kAQP == 4e-04

2\) Apply Maturation Stages Timings

```{r}
kAQP_value <- unique(Data_Full$kAQP)[5]

Data_EB <- data.frame()
for(i in unique(Conductivities_processed$x)){
  temp_cdt <- Conductivities_processed %>% filter(x == i & kAQP==kAQP_value)
  for(j in unique(temp_cdt$Barrier_Name)){
    # cat("x = ", i, " | Barrier_Name = ", j, "\n")
    temp_df <- data.frame(x = i, 
                          Barrier_Name = j,
                          kr_mean = mean(temp_cdt$kr[temp_cdt$Barrier_Name == j]),
                          kr_sd = sd(temp_cdt$kr[temp_cdt$Barrier_Name == j]),
                          kr_median = median(temp_cdt$kr[temp_cdt$Barrier_Name == j]),
                          kr_mad = mad(temp_cdt$kr[temp_cdt$Barrier_Name == j]),
                          Kx_mean = mean(temp_cdt$Kx[temp_cdt$Barrier_Name == j]),
                          Kx_sd = sd(temp_cdt$Kx[temp_cdt$Barrier_Name == j]),
                          Kx_median = median(temp_cdt$Kx[temp_cdt$Barrier_Name == j]),
                          Kx_mad = mad(temp_cdt$Kx[temp_cdt$Barrier_Name == j]),
                          Kr_mean = mean(temp_cdt$Kr[temp_cdt$Barrier_Name == j]),
                          Kr_sd = sd(temp_cdt$Kr[temp_cdt$Barrier_Name == j]),
                          Kr_median = median(temp_cdt$Kr[temp_cdt$Barrier_Name == j]),
                          Kr_mad = mad(temp_cdt$Kr[temp_cdt$Barrier_Name == j]))
    Data_EB <- rbind(Data_EB, temp_df)
  }
}

# ================================================================================
Data_EB_timed = Data_EB %>% filter(Barrier_Name == "T1" & x <= 7)
Data_EB_timed = rbind(Data_EB_timed, Data_EB%>% filter(Barrier_Name == "T2" & x <= 20 & x > 7))
Data_EB_timed = rbind(Data_EB_timed, Data_EB%>% filter(Barrier_Name == "T3" & x > 20))
# ================================================================================

# timings :
t0 <- c(0, 7)
t1 <- c(8, 31)
# t2 <- c(25, 30)

m1 <- subset(Data_EB, 
             Barrier_Name == "T1" & x >= t0[1] & x <= t0[2])
m2 <- subset(Data_EB, 
             Barrier_Name == "T2" & x >= t1[1] & x <= t1[2])
# m3 <- subset(Data_EB,
#              Barrier_Name == "T3" & x >= t2[1] & x <= t2[2])




# MERGE
Data_EB_MS <- rbind(m1, m2)
# write_csv(m_full, "Data/m_full.csv")
```

## Fixed kAQP

```{r}
EB_kr <- ggplot(data = Data_EB_MS) + 
  geom_point(aes(x = x, y = kr_median, color = Barrier_Name)) +
  geom_errorbar(mapping=aes(x=x, ymin=kr_median-kr_mad, ymax=kr_median+kr_mad, color = Barrier_Name), 
                width=0.5, 
                linewidth=1,
                alpha = 0.75) + 
  # geom_line(aes(x = x, y = kr_median, color = Barrier)) +
  # geom_smooth(aes(x = x, y = kr_median)) +
  # ylim(2.5e-08, 1.2e-07) +
  theme_test() +
  ggtitle(expression(k[r] ~ "[" ~ 10^{8} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme_test() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
# ==============================================================================
EB_Kx <- ggplot(data = Data_EB_MS) + 
  geom_point(aes(x = x, y = ln(Kx_median), color = Barrier_Name)) +
  geom_errorbar(mapping=aes(x=x, 
                            ymin= ln(Kx_median - Kx_mad), 
                            ymax= ln(Kx_median + Kx_mad), 
                            color = Barrier_Name),
                width=0.5,
                linewidth=1,
                alpha = 0.75) +
  ggtitle(expression(ln(K[x]) ~ "[" ~ cm^{4} ~ hPa^{-1} ~ d^{-1} ~ "]")) +
  theme_test() +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5))
# ==============================================================================
EB_Kr <- ggplot(data = Data_EB_MS) + 
  geom_point(aes(x = x, y = Kr_median, color = Barrier_Name)) +
  geom_errorbar(mapping=aes(x=x, ymin=Kr_median-Kr_mad, ymax=Kr_median+Kr_mad, color = Barrier_Name), 
                width=0.5, 
                linewidth=1,
                alpha = 0.75) + 
  xlab("Age [d]")+
  ggtitle(expression(K[r] ~ "[" ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme_test() +
  theme(axis.title.x=element_blank(), 
        legend.position = "bottom",
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5))

# ==============================================================================
legend <- get_legend(EB_kr + theme(legend.title = element_blank()))
# ==============================================================================

EB_kr
EB_Kx
EB_Kr

# ==============================================================================
pg1 <- plot_grid(EB_kr + theme(legend.position = "none"),
                 EB_Kx + theme(legend.position = "none"),
                 EB_Kr + theme(legend.position = "none"),
          align = 'v',
          labels = 'auto',
          ncol = 1)
pg2 <- plot_grid(pg1 + 
                   theme(plot.margin=unit(c(0,0,-4,0), "cm")), 
                 legend,
                 ncol = 1)
```

Export

```{r, eval=F}
svg("Plots/Error_Bar_Plots2.svg", height = 10, width = 3)
pg2 
dev.off()
```

## Full Plots

```{r}
treshold <- 31


p_kr <- ggplot(data = Data_Full, aes(x = x, y = kr*10^8, color = kAQP*1e7)) +
  geom_jitter(data = Data_Full%>%filter(Barrier_Name == "T1" & x < 7), 
              alpha = 0.4, 
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier_Name == "T2" & x >= 7 & x < treshold), 
              alpha = 0.4,
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier_Name == "T3" & x >= treshold), 
              alpha = 0.4,
              size = 2) +
  scale_color_viridis() +
  xlab("Age [d]") +
  ylab("Radial Conductivity [cm d-1 MPa-1]") +
  labs(color = "kAQP") +
  theme_test() +
  ggtitle(expression(k[r] ~ "[" ~ 10^{-8} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme(panel.background = element_rect(fill = "gray")) +
    theme(axis.title.x=element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
p_kr
#===============================================================================
p_Kx <- ggplot(data = Data_Full%>%
                 filter(Barrier_Name == "T1" & kAQP == kAQP_value), aes(x = x, y = ln(Kx), color = radius)) +
  geom_jitter() +
  scale_color_viridis(option = "magma") +
  xlab("Age [d]") +
  theme_test() +
  ggtitle(expression(ln(K[x]) ~ "[" ~ cm^{4} ~ hPa^{-1} ~ d^{-1} ~ "]")) +
  theme(panel.background = element_rect(fill = "gray")) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5))
p_Kx
#===============================================================================
p_Kr <- ggplot(data = Data_Full, 
               aes(x = x, y = Kr*1e8, color = kAQP*1e7)) +
  geom_jitter(data = Data_Full%>%filter(Barrier_Name == "T1" & x < 7), 
              alpha = 0.4, 
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier_Name == "T2" & x >= 7 & x < treshold), 
              alpha = 0.4,
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier_Name == "T3" & x >= treshold), 
              alpha = 0.4,
              size = 2) +
  scale_color_viridis() +
  xlab("Age [d]") +
  labs(color = "kAQP") +
  theme_test() +
  ggtitle("Radial Kr with observed maturation timings") +
  theme(panel.background = element_rect(fill = "gray")) +
    ggtitle(expression(K[r] ~ "[" ~ 10^{-8} ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme(legend.position = "right",
        # axis.title.x=element_blank(), 
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5)) 
p_Kr

```

```{r, eval = F}
svg("Plots/Points_Plots_full.svg", height = 3, width = 12)
plot_grid(p_kr, p_Kx, p_Kr,
          align = 'h',
          labels = 'auto',
          ncol = 3)
dev.off()

png("Plots/Points_Plots_full.png", height = 3, width = 12, units = "in", res = 300)
plot_grid(p_kr, p_Kx, p_Kr,
          align = 'h',
          labels = 'auto',
          ncol = 3)
dev.off()
```
