---
title: "RESULTS ANALYSIS"
format: html
editor: source
editor_options: 
  chunk_output_type: inline
---

```{r Load Packages, include=F}
options(rstudio.help.showDataPreview = FALSE)

TRoot_path <- "FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path)) {
  print(i)
  source(paste0(TRoot_path, i))
}

pkg_list <- c("fmsb", "packcircles", "pander", "readxl", "visreg", "EnvStats", "factoextra", "data.table",
              "reticulate", "xml2", "tidyverse", "plyr", "deldir", "viridis", "Hmisc", "devtools", "ggplot2",
              "gridExtra", "dplyr", "cowplot", "stats", "emmeans", "corrplot", "sf", "SciViews")

load_packages(pkg_list)

simu_path <- "Results/12-01-2023/"
```

# Load Data

```{r, eval = F}
# path <- "Results/12-01-2023/Conductivities/"
# l <- list.files(path, pattern = ".csv")
# Conductivities <- data.frame()
# 
# for(i in l){
#   # print(i)
#   temp_df <- read.csv(paste0(path, i))
#   Conductivities <- rbind(Conductivities, temp_df)
# }
# # Correct a bug that make Kx weird for b9 (the bug is fixed in scripts, but remains in results files)
# Conductivities$Kx[Conductivities$Barrier == "b9"] <- Conductivities$Kx[Conductivities$Barrier == "b5"]
# 
# write.csv(Conductivities, file = "Results/12-01-2023/Conductivities_full.csv", row.names = F)
```

Load Conductivity file and create Conductivity_Dico and Conductivity_Mono

```{r, eval = F}
# Virtual_Roots <- read.csv("Data/Virtual Roots/Virtual_Root_2023-07-17_30x20.csv")
# 
# Conductivities <- read.csv(file = paste0(simu_path, "Conductivities_full.csv"))
# source("FUNCTIONS/T-Root/Functions.R")
# # Conductivities <- distinct(Conductivities) # To avoid repetitions
# 
# #==================================================================================
# # Clean data and create dico and mono
# Conductivities_dico <- set_conductivities_dico(Conductivities,threshold = 3)
# Conductivities_mono <- set_conductivities_mono(Conductivities, threshold = 3)
# 
# # #==================================================================================
# # # Add Radius [mm]
# # Conductivities_dico$radius <- 10*Conductivities_dico$perimeter/(2*pi) # cm -> mm
# # Conductivities_mono$radius <- 10*Conductivities_mono$perimeter/(2*pi)
# #
# # #==================================================================================
# # # Add Kr
# # Conductivities_dico$Kr <- Conductivities_dico$kr*Conductivities_dico$perimeter
# # Conductivities_mono$Kr <- Conductivities_mono$kr*Conductivities_mono$perimeter
# 
# #==================================================================================
# # Change maturation stage name :
# Conductivities_dico$Barrier <- as.factor(Conductivities_dico$Barrier)
# Conductivities_mono$Barrier <- as.factor(Conductivities_mono$Barrier)
# 
# levels(Conductivities_dico$Barrier) <- c("T2", "T3", "T1")
# levels(Conductivities_mono$Barrier) <- c("M1", "M2", "M3")
# 
# Conductivities_dico <- Conductivities_dico %>% mutate(Barrier = reorder(Barrier, match(Barrier, c("T1", "T2", "T3"))))
# 
# Conductivities_full <- rbind(Conductivities_dico, Conductivities_mono)
# 
# #==================================================================================
# # Check that the data is okey (black points have to be +- homogenous) :
# ggplot(data = Conductivities_dico, aes(x = x, y = root)) +
#   geom_point() +
#   ggtitle("Conductivities") +
#   theme_bw()
# 
# # Export
# write.csv(Conductivities_dico, file = paste0(simu_path, "Conductivities_dico_", Sys.Date(),".csv"), row.names = F)
# write.csv(Conductivities_mono, file = paste0(simu_path, "Conductivities_mono_", Sys.Date(),".csv"), row.names = F)
# # write.csv(Conductivities, file = paste0("Data/Conductivities_", Sys.Date(),".csv"), row.names = F)
```

Create Data Full

```{r, eval = F, include = F}
# Virtual_Roots3 <- read.csv("Data/Virtual Roots/Virtual_Root_2023-07-17_30x20.csv")
# Virtual_Roots3 <- merge(Virtual_Roots3, Parameters[,c(1,2,3)], by = c("name", "type"))
# 
# data_full <- merge(Conductivities_full, Virtual_Roots3, by = c("root", "x"))
# # data_full <- merge(data_full, Parameters[c(1,2,3)])
# # data_full <- data_full %>% filter(Barrier == "T1")
# data_full1 <- data.frame(root = data_full$root,
#                          x = data_full$x,
#                          param_id = data_full$param_id,
#                          name = data_full$name,
#                          type = data_full$type,
#                          param_value = data_full$y,
#                          kr = data_full$kr,
#                          Kx = data_full$Kx,
#                          Kr = data_full$Kr,
#                          radius = data_full$radius,
#                          Barrier = data_full$Barrier,
#                          kAQP = data_full$kAQP)
# 
# 
# final_df <- data.frame()
# for(root_i in unique(data_full1$root)){
#   print(root_i)
# 
#   for(x_i in unique(data_full1$x)){
#     print(x_i)
# 
#     for(kaqp in unique(data_full1$kAQP)){
#       # print(kaqp)
#       for(MS in unique(data_full1$Barrier)){
#         # print(MS)
#         temp_df <- data_full1 %>% filter(root == root_i & x == x_i & kAQP == kaqp & Barrier == MS)
#         temp_df_e <- data.frame(root = unique(temp_df$root),
#                                 x = unique(temp_df$x),
#                                 kr = unique(temp_df$kr),
#                                 Kx = unique(temp_df$Kx),
#                                 Kr= unique(temp_df$Kr),
#                                 radius = unique(temp_df$radius),
#                                 Barrier = unique(temp_df$Barrier),
#                                 kAQP = unique(temp_df$kAQP))
# 
#         temp_df4 <- pivot_wider(temp_df[c(3,6)],
#                                 names_from = param_id,
#                                 values_from = param_value)
# 
#         temp_df_e2 <- cbind(temp_df_e, temp_df4)
#         # print(head(temp_df_e2))
# 
#         final_df <- rbind(final_df, temp_df_e2)
#       }
#     }
#   }
# }
# 
# # Export final database
# write.csv(final_df, "Data/DATA_FULL_FINAL.csv", row.names = F)
```

Load Data

```{r Load Data}
Conductivities_dico <- read.csv(paste0(simu_path, "Conductivities_dico_2024-02-12.csv"))
Conductivities_mono <- read.csv(paste0(simu_path, "COnductivities_mono_2024-02-12.csv"))

Conductivities <- rbind(Conductivities_dico, Conductivities_mono)

Anatomy_Full <- read.csv("Data/Anatomy/Anatomy_Full.csv")
Data_Full <- read.csv("Data/DATA_FULL_FINAL.csv")

# Remove day zero
Conductivities_dico <- Conductivities_dico %>% filter(x != 0)
Conductivities_mono <- Conductivities_mono %>% filter(x != 0)
Conductivities <- Conductivities %>% filter(x != 0)
Data_Full <- Data_Full %>% filter(x != 0)
```

# Visual analysis

## Plot pure data

```{r Plot Pure Data}
# kr vs kAQP
kAQP_plot1 <- ggplot(data = Conductivities_dico,
                     aes(x=(kAQP*10000), 
                         y = kr*1e08,
                         color = Barrier))+
  geom_point(aes(x = as.factor(kAQP*10000)),
             position = "jitter",
             alpha = 0.05) +
  # geom_boxplot(aes(x = as.factor(kAQP*10000), y = kr, color = Barrier))+
  # facet_wrap(~Barrier) +
  # scale_color_viridis() +
  geom_smooth(linewidth = 2) +
  ylab(expression(k[r] ~ 10^{8} ~ "[" * m ~ MPa^{-1} ~ s^{-1}*"]")) +
  # xlab("kAQP [10e-04 cm hPA-1 d-1]") +
  xlab(expression(kAQP ~ 10^{-4} ~ "[" * cm ~ hPa^{-1} ~ d^{-1} * "]")) +
  ylim(2, 12) +
  theme_test() 
  # theme(legend.position = "none")
kAQP_plot1
ggsave(filename = "plots/AQP_influence.svg", plot = kAQP_plot1, device = "svg", width = 4, height = 3, units = "in")
#============================================================================
# kr
kr_plot1 <- ggplot(data = Conductivities_dico,
       aes(x = x, 
           y = kr*10^8,
           color = kAQP*10000)) +
  geom_point(alpha = 0.5, position = "jitter") +
  facet_wrap(~Barrier) +
  scale_color_viridis() +
  # geom_smooth(aes(x = x, y = radius/5000000), color = "red") +
  # ylim(0, 3e-08) +
  ylab(expression(k[r] ~ 10^{-8} ~ "[" * m ~ MPa^{-1} ~ s^{-1}*"]")) +
  xlab("Age [d]") +
  ggtitle("kr DICOTS") +
  theme_test()
kr_plot1
#============================================================================
kr_plot0 <- ggplot(data = Conductivities_mono,
       aes(x = x, 
           y = kr,
           color = kAQP)) +
  geom_point(alpha = 0.2, position = "jitter") +
  facet_wrap(~Barrier) +
  scale_color_viridis() +
  # geom_smooth(aes(x = x, y = radius/5000000), color = "red") +
  # ylim(0, 2e-04) +
  ylab(expression(k[r] ~ 10^{8} ~ "[" * cm ~ MPa^{-1} ~ s^{-1}*"]")) +
  xlab("Age [d]") +
  # coord_fixed() +
  ggtitle("kr MONOCOTS") +
  theme_test()
kr_plot0
# Kr
#============================================================================
Kr_plot1 <- ggplot(data = Conductivities_dico,
       aes(x = x, 
           y = Kr,
           color = kAQP)) +
  geom_jitter(alpha = 0.2) +
  facet_wrap(~Barrier) +
  scale_color_viridis() +
  ylab("Radial Conductance [m^3 MPa-1 d-1]") +
  xlab("Age [d]") +
  # ylim(0, 3e-08) +
  theme_test()
Kr_plot1
#============================================================================
# Radius
Radius_plot1 <- ggplot(data = Conductivities_dico,
                       aes(x = x, y = radius)) +
  geom_point(alpha = 0.01) +
  # geom_smooth() +
  theme_test() +
  ylab("Radius [mm]") +
  xlab("Age [d]") 

Radius_plot1
#============================================================================
# Perimeter
Perimeter_plot1 <- ggplot(data = Conductivities_dico,
                       aes(x = x, y = perimeter)) +
  geom_point(alpha = 0.01) +
  # geom_smooth() +
  theme_test() +
  ylab("Perimeter [cm]") +
  xlab("Age [d]") 

Perimeter_plot1
#============================================================================
# Kx
kx_plot1 <- ggplot(data = Conductivities_dico%>%filter(Barrier == "T1"),
       aes(x = x, 
           y = Kx)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm") +
  scale_y_log10() +
  # geom_smooth(method = "lm", se = T) +
  # scale_color_viridis() +
  # ylim(0, 3e-08) +
  ylab("Axial Kr [cm^3 d-1 hPa-1]") +
  xlab("Age [d]") +
  theme_test()
kx_plot1
#============================================================================
#MS
MS_plot1 <- ggplot(data = Conductivities_dico) +
  geom_point(aes(x= Barrier, y = kr, color = kAQP), 
             position="jitter", 
             alpha = 0.1) +
  geom_boxplot(aes(x = Barrier, y = kr)) +
  theme_test() +
  scale_color_viridis() +
  xlab("Maturation Stage") +
  ylab("Radial conductivity [cm d-1 MPa-1]")
MS_plot1
```

Export plots

```{r Export graphs, eval = F, include=F}
svg("Plots/kAQP_1.svg", height = 4, width = 6)
kAQP_plot1
dev.off()

svg("Plots/kr_kAQP_1.svg", height = 3, width = 6)
kr_plot1 
dev.off()

svg("Plots/kx_kAQP_1.svg", height = 5, width = 8)
kx_plot1
dev.off()

svg("Plots/Kr_kAQP_1.svg", height = 5, width = 8)
Kr_plot1
dev.off()

svg("Plots/Radius_kAQP_1.svg", height = 5, width = 8)
Radius_plot1
dev.off()

svg("Plots/Perimeter_kAQP_1.svg", height = 3, width = 8)
Perimeter_plot1
dev.off()

svg("Plots/Maturation_Stage_1.svg", height = 5, width = 8)
MS_plot1
dev.off()

```

# Statistical Analysis per variable

## 0) Global Correlations

```{r Correlations}
library(corrplot)
corrplot(cor(subset(Data_Full %>% filter(Barrier == "T1", kAQP == 4e-04), select = -c(1, 7))))
```

## 1) Effect of Radius

### 1.1) Regression of radius from quantification data

```{r Radius plot}
radius_df <- Anatomy_Full[c("age", "radius")]

# PLot
r_plot2 <- ggplot(data = radius_df, aes(x = age, y = radius))+
  # ylim(0, 0.8) +
  geom_point() +
  # geom_smooth(formula = y~x) +
  theme_bw() +
  ggtitle("Radius of the data")

# svg(filename = paste0("Plots/Radius_data.svg"), width = 5, height = 5)
r_plot2
# dev.off()
```

To regress that, we split in two half : - If x is \< 25, we consider the radius as constant = 0.188 - If x is \>= 25, we consider exponential function

```{r Radius Regression}
# FIRST STAGE
radius_df1 <- radius_df %>% filter(age < 25)
radius_df2 <- radius_df %>% filter(age >= 25)
radius_df2$radius_ln <- ln(radius_df2$radius)
summary(radius_df1$radius)

rlm1 <- lm(data = radius_df1, formula = radius ~ 1)
summary(rlm1)

# SECOND STAGE
rlm2 <- lm(data = radius_df2, formula = radius_ln ~ age)
summary(rlm2)
plot(rlm2)
visreg(rlm2)
```

Okey, so this is nice. With these two regression function, we coded the "radius" function.

### 1.2) Effect of radius on kr

Here we start by looking at the relation between kr, root age and root radius, per Maturation Stage, at fixed kAQP (= 4e-04). We split in two : between 0 and 25 days their is \~linear increase in kr. After 25 days, kr drops linarly.

```{r Effect of radius on kr}
# =============================================================================
subset1 <- Conductivities_dico %>% filter(x < 25)
subset2 <- Conductivities_dico %>% filter(x >= 25)

subset1_1 <- subset1%>%filter(kAQP == "4e-04")
subset2_1 <- subset2%>%filter(kAQP == "4e-04")

cor(subset1$kr, subset1$radius)
cor(subset2$kr, subset2$radius)

#===============================================================================
# Individual MS

MS_indi <- ggplot(data = Conductivities_dico%>%filter(kAQP == "4e-04")) +
  geom_point(aes(x = x, y = kr), color = "blue", alpha = 0.3) + 
  # geom_smooth(aes(x = x, y = kr), color = "blue") +
  geom_smooth(data = subset1_1, aes(x = x, y = kr), color = "blue", method = "lm") +
  geom_smooth(data = subset2_1, aes(x = x, y = kr), color = "blue", method = "lm") +
  
  geom_point(aes(x = x, y = radius/(1e07)), color = "red",alpha = 0.3) +
  geom_smooth(aes(x= x , y =radius/(1e07)), color = "red") +
  facet_wrap(~Barrier) +
  ggtitle("Full Timeline") +
  theme_test()
  
MS_indi

#===============================================================================
MS_indi2 <- ggplot(data = subset1_1) +
  geom_point(aes(x = x, y = kr), color = "blue", alpha = 0.3) +
  geom_smooth(aes(x = x, y = kr), color = "blue", method = 'lm') +
  
  geom_point(aes(x = x, y = radius/(1e07)), color = "red", alpha = 0.3) +
  geom_smooth(aes(x= x , y =radius/(1e07)), color = "red", method = 'lm') +
  facet_wrap(~Barrier) +
  ggtitle("First Stage") +
  theme_test()
MS_indi2

#===============================================================================
MS_indi3 <- ggplot(data = subset2_1) +
  geom_point(aes(x = x, y = kr), color = "blue", alpha = 0.3) + 
  geom_smooth(aes(x = x, y = kr), color = "blue", method = 'lm') +
  
  geom_point(aes(x = x, y = radius/(1e07)), color = "red", alpha = 0.3) +
  geom_smooth(aes(x= x , y =radius/(1e07)), color = "red", method = 'lm') +
  facet_wrap(~Barrier) +
  ggtitle("Second Stage") +
  theme_test()
MS_indi3
```

Simple linear model ? Just to see in constant kAQP and MS Not efficient

```{r}
print("FIRST PHASE")
rad_lm <- lm(data = subset1_1, formula = kr ~ x + radius + Barrier)
summary(rad_lm)
anova(rad_lm)

print("SECOND PHASE")
rad_lm <- lm(data = subset2_1, formula = kr ~ x + radius + Barrier + radius:Barrier)
summary(rad_lm)
anova(rad_lm)
```

## 2) Influence of Aquaporins

```{r}
ggplot(data = Conductivities_dico) +
  geom_jitter(aes(x = kAQP*10000, y = kr, color = Barrier), alpha = 0.1) +
  geom_smooth(aes(x = kAQP*10000, y = kr, color = Barrier)) +
  # facet_wrap(~Barrier) +
  
  theme_test()

kAQP_lm <- lm(data = Conductivities_dico, formula = kr ~ kAQP*Barrier)
anova(kAQP_lm)
```

## 3) Influence of Deposition Levels

Globally, we clearly see that all maturation stages are different and significantly.

```{r}
# KR
kr_plot_dicot <- ggplot(data = Conductivities_dico, aes(x = as.factor(x), y = kr, color = Barrier, fill = Barrier)) +
  # geom_point() +
  # geom_line() +
  geom_boxplot(alpha = 0.5) +
  # facet_wrap(~Barrier, ncol = 2) +
  # facet_grid(~factor(Barrier, levels=c('b1', 'b5', 'b6', 'b4'))) +
  theme_bw() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  ylim(2e-08, 1.25e-07) +
  # theme(legend.position="none") +
  xlab("Root age [d]") +
  ylab("Radial conductivity [m s-1 MPa-1") +
  ggtitle("Dicot barriers- Kr")

kr_plot_dicot

#===============================================================================

# KR
kr_plot_monocot <- ggplot(data = Conductivities_mono, aes(x = as.factor(x), y = kr, color = Barrier, fill = Barrier)) +
  # geom_point() +
  # geom_line() +
  geom_boxplot(alpha = 0.5) +
  # facet_wrap(~Barrier, ncol = 2) +
  # facet_grid(~factor(Barrier, levels=c('b1', 'b3', 'b4'))) +
  theme_bw() +
  ylim(2e-08, 1.25e-07) +
  # theme(legend.position="none") +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  scale_color_brewer(palette ="Set2") +
  scale_fill_brewer(palette ="Set2") +
  xlab("Root age [d]") +
  ylab("Radial conductivity [m s-1 MPa-1") +
  ggtitle("Monocots barriers - kr")
  
# ggexport(kr_plot, filename=paste0("Kr.pdf"), plot = image)
# svg(filename = paste0("Plots/kr_plot_monocot_",date,".svg"), width = 10, height = 10)
kr_plot_monocot
# dev.off()

#===============================================================================
# MS_subset <- Conductivities %>% filter(kAQP == 5e-04)
MS_all <- ggplot(data = Conductivities %>% filter(kAQP == 5e-04), 
                 aes(x = Barrier, y = kr*10^08, fill = Barrier)) +
  geom_jitter(width = 0.1,
              alpha = 0.1) +
  geom_boxplot() + 
  xlab("Maturation Stage") +
  ylab(expression(k[r] ~ "[" ~ 10^{-08} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  scale_fill_manual(values=c("white","white","white", "grey", "grey", "grey")) +
  theme_bw() +
  # ggtitle(expression(k[r] ~ "[" ~ 10^{-08} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme(legend.position = "none") 


# svg("Plots/Maturation_Stages_All.svg", height = 4, width = 4)
MS_all
# dev.off()
```

Stats :

```{r}
MS_lm <- lm(data = Conductivities, formula = kr ~ Barrier)

summary(MS_lm)
anova(MS_lm)
emmeans(MS_lm, specs = pairwise ~ Barrier)

visreg(MS_lm)

DL_pred <- tibble(DL = c("M1", "M2", "M3", "T1", "T2", "T3"),
                  Estimate = MS_lm$coefficients)

DL_pred2 <- tibble(DL2 = c("M1", "M2", "M3", "T1", "T2", "T3"),
                  Estimate2 = MS_lm$coefficients)

EM <- emmeans(MS_lm, specs = pairwise ~ Barrier)
DL_mean <- as_tibble(EM$emmeans)
DL_contrast <- as_tibble(EM$contrasts)
```

Some interesting stats :

```{r}
mean_M1 <- DL_mean$emmean[DL_mean$Barrier == "M1"]
mean_M2 <- DL_mean$emmean[DL_mean$Barrier == "M2"]
mean_M3 <- DL_mean$emmean[DL_mean$Barrier == "M3"]
mean_T1 <- DL_mean$emmean[DL_mean$Barrier == "T1"]
mean_T2 <- DL_mean$emmean[DL_mean$Barrier == "T2"]
mean_T3 <- DL_mean$emmean[DL_mean$Barrier == "T3"]

print(paste0("Difference between T1 and M1 : ", (mean_M1-mean_T1)*100/mean_M1))
print(paste0("Difference between T2 and T1 : ", (mean_T1-mean_T2)*100/mean_T1))
print(paste0("Difference between T3 and T1 : ", (mean_T1-mean_T3)*100/mean_T1))
print(paste0("Difference between M2 and M3 : ", (mean_M2-mean_M3)*100/mean_M2))
```

# STATISTICAL ANALYSIS FULL

## 1) Radial conductivity

```{r}
lm_kr0 <- lm(data = Conductivities_dico, formula = kr ~ x + radius + Barrier + kAQP + kAQP:Barrier)
summary(lm_kr0)
anova(lm_kr0)
emmeans(lm_kr0, specs = pairwise ~ Barrier:kAQP)

coefficients_kr <- tibble(a = lm_kr0$coefficients[1], 
                                  x = lm_kr0$coefficients[2], 
                                  r = lm_kr0$coefficients[3], 
                                  T2 = lm_kr0$coefficients[4], 
                                  T3 = lm_kr0$coefficients[5],
                                  kAQP = lm_kr0$coefficients[6],
                                  T2kAQP = lm_kr0$coefficients[7],
                                  T3kAQP = lm_kr0$coefficients[8])

# write.csv(coefficients_kr, "Data/CRB-MARSHAL/kr_coef_full.csv", row.names = F)
```

This is very nice. So we see different informations : - The whole linear model is significant at R2 = 0.918 - On the ANOVA, all variables are significant - The less significant factor is T2 (p = 0.0178).

Really nice !

## 2) Axial Kr

```{r}
lm2 <- lm(data = Data_Full%>%filter(Barrier == "T1" & kAQP == 0.0004), formula = ln(Kx) ~ radius + x)
summary(lm2)
anova(lm2)

coefficients_Kx <- tibble(a = -25.97,
                          r = 6.52,
                          x = 0.139)

# write.csv(coefficients_Kx, "Data/CRB-MARSHAL/Kx_coef_full.csv", row.names = F)
```

# PREDICTION CURVES

## Scenario 1 : Tomato

```{r}
Reg2 <- tibble(x = seq(1:30))
Reg2$radius <- radius_reg(Reg2$x)
Reg2$radius[Reg2$x > 30] <- Reg2$radius[Reg2$x == 30]
Reg2$MS <- 0

timing <- c(7, 25)
Reg2$MS[Reg2$x <= timing[1]] <- "T1"
Reg2$MS[Reg2$x > timing[1] & Reg2$x < timing[2]] <- "T2"
Reg2$MS[Reg2$x >= timing[2]] <- "T3"

Reg2$kr <- 0
Reg2$Kx <- 0
Reg2$Kr <- 0


for(i in Reg2$x){
  Reg2$kr[Reg2$x == i] <- radial_reg(x = i,
                                     timing = timing,
                                     kAQP = 4e-04,
                                     coefficients = coefficients_kr)
  Reg2$Kx[Reg2$x == i] <- axial_reg(x = i, 
                                    timing = timing, 
                                    coefficients = coefficients_Kx)
}

Reg2$Kr <- Reg2$kr * 2 *3.1415 * Reg2$radius/1000

Reg2$Kx[Reg2$x > 30] <- Reg2$Kx[Reg2$x == 30]

Reg_plot <- ggplot(data = Reg2) +
  geom_line(aes(x = x, y = kr*1e8), color = "red", linewidth = 2) +
  geom_line(aes(x = x, y = Kx*1e09), color = "blue", linewidth = 2) +
  geom_line(aes(x = x, y = Kr*1e11), color = "green", linewidth = 2) +
  geom_line(aes(x = x, y = radius*1e1), color = "grey", linewidth = 2, linetype = 2) +
  xlim(0, 30) +
  theme_test()
Reg_plot

# svg("plots/Reg_Plot.svg", width = 5, height = 4)
# Reg_plot
# dev.off()
```

## Scenario 2 : No exodermis suberization

Here we simulate the same root (with secondary growth), but with no exodermal suberization

```{r}
lm_mono_kr <- lm(data = Conductivities_mono, formula = kr ~ x + radius + Barrier + kAQP + kAQP:Barrier)
summary(lm_mono_kr)

print(lm_mono_kr$coefficients)

coefficients_kr_mono <- tibble(a = lm_mono_kr$coefficients[1], 
                                  x = lm_mono_kr$coefficients[2], 
                                  r = lm_mono_kr$coefficients[3], 
                                  T2 = lm_mono_kr$coefficients[4], 
                                  T3 = lm_mono_kr$coefficients[5],
                                  kAQP = lm_mono_kr$coefficients[6],
                                  T2kAQP = lm_mono_kr$coefficients[7],
                                  T3kAQP = lm_mono_kr$coefficients[8])

# write.csv(coefficients_kr_mono, "Data/CRB-MARSHAL/kr_coef_full_mono.csv", row.names = F)
```

So we need to simulate no deposition level till 25 days (M1), and then only endodermal suberization (so M2)

```{r}
Reg_mono1 <- tibble(x = seq(1, 30),
               radius = 0,
               kr = 0,
               Kx = 0)
for(i in seq(1, length(Reg_mono1$x))){
  Reg_mono1$radius[i] <- radius_reg(Reg_mono1$x[i])
  Reg_mono1$kr[i] <- radial_reg(Reg_mono1$x[i], 
                                kAQP = 4.3e-4,
                                timing = c(25,30), 
                                coefficients = coefficients_kr_mono)
  Reg_mono1$Kx[i] <- axial_reg(Reg_mono1$x[i], 
                               timing = c(7, 25),
                               coefficients = coefficients_Kx)
}

Reg_mono1$Kr <- Reg_mono1$kr * 2 *3.1415 * Reg_mono1$radius/1000

Reg_plot_mono <- ggplot(data = Reg_mono1) +
  geom_line(aes(x = x, y = kr*1e8), color = "red", linewidth = 2) +
  geom_line(aes(x = x, y = Kx*1e9), color = "blue", linewidth = 2) +
  geom_line(aes(x = x, y = Kr*1e11), color = "green", linewidth = 2) +
  geom_line(aes(x = x, y = radius*1e1), color = "grey", linewidth = 2, linetype = 2) +
  xlim(0, 30) +
  theme_test()
Reg_plot_mono

# svg("plots/Reg_Plot_mono.svg", width = 5, height = 4)
# Reg_plot_mono
# dev.off()
```

## Scenario 3 : No secondary growth

Finally, here we simulate root with NO secondary growth and NO exodermal suberization

```{r}
Reg_mono2 <- tibble(x = seq(1, 30),
               radius = 0.18,
               kr = 0,
               Kx = 0)
for(i in seq(1, length(Reg_mono2$x))){
  # Reg_mono2$radius[i] <- radius_reg(Reg_mono2$x[i])
  Reg_mono2$kr[i] <- radial_reg(Reg_mono2$x[i],
                                radius = 0.18,
                                kAQP = 4.3e-4, 
                                coefficients = coefficients_kr_mono,
                                timing = c(25, 30))
  Reg_mono2$Kx[i] <- axial_reg(Reg_mono2$x[i], 
                               radius = 0.18,
                               coefficients = coefficients_Kx,
                               timing = c(25, 60))
}

Reg_mono2$Kr <- Reg_mono2$kr * 2 *3.1415 * Reg_mono2$radius/1000

Reg_plot_mono2 <- ggplot(data = Reg_mono2) +
  geom_line(aes(x = x, y = kr*1e8), color = "red", linewidth = 2) +
  geom_line(aes(x = x, y = Kx*1e09), color = "blue", linewidth = 2) +
  geom_line(aes(x = x, y = Kr*1e11), color = "green", linewidth = 2) +
  geom_line(aes(x = x, y = radius*1e1), color = "grey", linewidth = 2, linetype = 2) +
  xlim(0, 30) +
  theme_test()
Reg_plot_mono2

# svg("plots/Reg_Plot_mono2.svg", width = 5, height = 4)
# Reg_plot_mono2
# dev.off()
```

# Error bar plots

Define data : In this chunk we

1\) Create a dataframe where we store mean values and errors bars for constant kAQP == 4e-04

2\) Apply Maturation Stages Timings

```{r}
Data_EB <- data.frame()
for(i in unique(Conductivities_dico$x)){
  kAQP_value <- 4e-04
  temp_cdt <- Conductivities_dico %>% filter(x == i & kAQP==kAQP_value)
  # print(i)
  for(j in unique(temp_cdt$Barrier)){
    # print(j)
    temp_df <- data.frame(x = i, 
                          Barrier = j,
                          kr_mean = mean(temp_cdt$kr[temp_cdt$Barrier == j]),
                          kr_sd = sd(temp_cdt$kr[temp_cdt$Barrier == j]),
                          kr_median = median(temp_cdt$kr[temp_cdt$Barrier == j]),
                          kr_mad = mad(temp_cdt$kr[temp_cdt$Barrier == j]),
                          Kx_mean = mean(temp_cdt$Kx[temp_cdt$Barrier == j]),
                          Kx_sd = sd(temp_cdt$Kx[temp_cdt$Barrier == j]),
                          Kx_median = median(temp_cdt$Kx[temp_cdt$Barrier == j]),
                          Kx_mad = mad(temp_cdt$Kx[temp_cdt$Barrier == j]),
                          Kr_mean = mean(temp_cdt$Kr[temp_cdt$Barrier == j]),
                          Kr_sd = sd(temp_cdt$Kr[temp_cdt$Barrier == j]),
                          Kr_median = median(temp_cdt$Kr[temp_cdt$Barrier == j]),
                          Kr_mad = mad(temp_cdt$Kr[temp_cdt$Barrier == j]))
    Data_EB <- rbind(Data_EB, temp_df)
  }
}

# ================================================================================
Data_EB_timed = Data_EB %>% filter(Barrier == "T1" & x <= 7)
Data_EB_timed = rbind(Data_EB_timed, Data_EB%>% filter(Barrier == "T2" & x <= 20 & x > 7))
Data_EB_timed = rbind(Data_EB_timed, Data_EB%>% filter(Barrier == "T3" & x > 20))
# ================================================================================

# timings :
t0 <- c(0, 7)
t1 <- c(8, 24)
t2 <- c(25, 30)

m1 <- subset(Data_EB, 
             Barrier == "T1" & x >= t0[1] & x <= t0[2])
m2 <- subset(Data_EB, 
             Barrier == "T2" & x >= t1[1] & x <= t1[2])
m3 <- subset(Data_EB, 
             Barrier == "T3" & x >= t2[1] & x <= t2[2])




# MERGE
Data_EB_MS <- rbind(m1, m2, m3)
# write_csv(m_full, "Data/m_full.csv")
```

## Fixed kAQP

```{r}
EB_kr <- ggplot(data = Data_EB_MS) + 
  geom_point(aes(x = x, y = kr_median, color = Barrier)) +
  geom_errorbar(mapping=aes(x=x, ymin=kr_median-kr_mad, ymax=kr_median+kr_mad, color = Barrier), 
                width=0.5, 
                linewidth=1,
                alpha = 0.75) + 
  # geom_line(aes(x = x, y = kr_median, color = Barrier)) +
  # geom_smooth(aes(x = x, y = kr_median)) +
  # ylim(2.5e-08, 1.2e-07) +
  theme_test() +
  ggtitle(expression(k[r] ~ "[" ~ 10^{8} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme_test() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
# ==============================================================================
EB_Kx <- ggplot(data = Data_EB_MS) + 
  geom_point(aes(x = x, y = ln(Kx_median), color = Barrier)) +
  geom_errorbar(mapping=aes(x=x, 
                            ymin= ln(Kx_median - Kx_mad), 
                            ymax= ln(Kx_median + Kx_mad), 
                            color = Barrier),
                width=0.5,
                linewidth=1,
                alpha = 0.75) +
  ggtitle(expression(ln(K[x]) ~ "[" ~ cm^{4} ~ hPa^{-1} ~ d^{-1} ~ "]")) +
  theme_test() +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5))
# ==============================================================================
EB_Kr <- ggplot(data = Data_EB_MS) + 
  geom_point(aes(x = x, y = Kr_median, color = Barrier)) +
  geom_errorbar(mapping=aes(x=x, ymin=Kr_median-Kr_mad, ymax=Kr_median+Kr_mad, color = Barrier), 
                width=0.5, 
                linewidth=1,
                alpha = 0.75) + 
  xlab("Age [d]")+
  ggtitle(expression(K[r] ~ "[" ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme_test() +
  theme(axis.title.x=element_blank(), 
        legend.position = "bottom",
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5))

# ==============================================================================
legend <- get_legend(EB_kr + theme(legend.title = element_blank()))
# ==============================================================================

EB_kr
EB_Kx
EB_Kr

# ==============================================================================
pg1 <- plot_grid(EB_kr + theme(legend.position = "none"),
                 EB_Kx + theme(legend.position = "none"),
                 EB_Kr + theme(legend.position = "none"),
          align = 'v',
          labels = 'auto',
          ncol = 1)
pg2 <- plot_grid(pg1 + 
                   theme(plot.margin=unit(c(0,0,-4,0), "cm")), 
                 legend,
                 ncol = 1)
```

Export

```{r, eval=F}
svg("Plots/Error_Bar_Plots2.svg", height = 12, width = 3)
pg2 
dev.off()
```

## Full Plots

```{r}
treshold <- 25

p_kr <- ggplot(data = Data_Full, aes(x = x, y = kr*10^8, color = kAQP*1e4)) +
  geom_jitter(data = Data_Full%>%filter(Barrier == "T1" & x < 7), 
              alpha = 0.4, 
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier == "T2" & x >= 7 & x < treshold), 
              alpha = 0.4,
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier == "T3" & x >= treshold), 
              alpha = 0.4,
              size = 2) +
  scale_color_viridis() +
  xlab("Age [d]") +
  ylab("Radial Conductivity [cm d-1 MPa-1]") +
  theme_test() +
  ggtitle(expression(k[r] ~ "[" ~ 10^{-8} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme(panel.background = element_rect(fill = "gray")) +
    theme(axis.title.x=element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
p_kr
#===============================================================================
p_Kx <- ggplot(data = Data_Full%>%filter(Barrier == "T1" & kAQP == "1e-04"), aes(x = x, y = ln(Kx), color = xylem_max_size)) +
  geom_jitter() +
  scale_color_viridis() +
  xlab("Age [d]") +
  theme_test() +
  ggtitle(expression(ln(K[x]) ~ "[" ~ cm^{4} ~ hPa^{-1} ~ d^{-1} ~ "]")) +
  theme(panel.background = element_rect(fill = "gray")) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5))
p_Kx
#===============================================================================
p_Kr <- ggplot(data = Data_Full, aes(x = x, y = Kr*1e8, color = kAQP*1e4)) +
  geom_jitter(data = Data_Full%>%filter(Barrier == "T1" & x < 7), 
              alpha = 0.4, 
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier == "T2" & x >= 7 & x < treshold), 
              alpha = 0.4,
              size = 2) +
  geom_jitter(data = Data_Full%>%filter(Barrier == "T3" & x >= treshold), 
              alpha = 0.4,
              size = 2) +
  scale_color_viridis() +
  xlab("Age [d]") +
  theme_test() +
  ggtitle("Radial Kr with observed maturation timings") +
  theme(panel.background = element_rect(fill = "gray")) +
    ggtitle(expression(K[r] ~ "[" ~ 10^{-8} ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  theme(legend.position = "right",
        # axis.title.x=element_blank(), 
        axis.title.y=element_blank(),
        plot.title = element_text(hjust = 0.5)) 
p_Kr

```

Correlations

```{r}
Data_Full_sample <- Data_Full %>% filter(Barrier == "T1" & kAQP == 1e-04)

cor(Data_Full$Kx, Data_Full$xylem_n_cells)
cor(Data_Full$Kx, Data_Full$stele_layer_diameter)
cor(Data_Full$Kx, Data_Full$xylem_cell_diameter)
```

```{r, eval = F}
svg("Plots/Points_Plots_full.svg", height = 3, width = 12)
plot_grid(p_kr, p_Kx, p_Kr,
          align = 'h',
          labels = 'auto',
          ncol = 3)
dev.off()
```
