---
title: "MPIPE"
format: html
editor: source
---

# Load dependancies

```{r, include=F}
# knitr::opts_chunk$set(echo = FALSE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # Set working directory to the current file
rm(list = ls())

options(rstudio.help.showDataPreview = FALSE)

# Define paths
CRBM.path    <- "./src/CRB-MARSHAL/"
path.results <- "./Results/CRB-MARSHAL/"
path.plots   <- "./plots/CRB-MARSHAL/"

libs <- c("fmsb", 
          "SciViews", 
          "pander", 
          "visreg", 
          "readxl", 
          "EnvStats", 
          "FactoMineR", 
          "factoextra", 
          "knitr", 
          "data.table", 
          "reticulate", 
          "xml2", 
          "tidyverse", 
          "dplyr", 
          "viridis", 
          "Hmisc", 
          "ggplot2", 
          "gridExtra", 
          # "outliers",
          "Matrix", 
          "emmeans")

for(pk in libs) {
  library(pk, character.only = T)
}

# source(paste0(CRBM.path,"io_function.R")) # CROOTBOX
source(paste0(CRBM.path, "Get_SUF.R")) # MARSHAL
source(paste0(CRBM.path, "SUF.R"))
source(paste0(CRBM.path, "CRBM_functions.R"))

TRoot_path <- "./src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path, pattern = ".R")) {
  print(i)
  source(paste0(TRoot_path, i))
}

# LOAD DATA TABLES
Simulations_ID <- read_xlsx(paste0(CRBM.path, "inputs/Simulations_ID.xlsx"))
Scenarios_ID   <- read_xlsx(paste0(CRBM.path, "inputs/Scenarios_ID.xlsx"))
RSA.IDs        <- read.csv(paste0(CRBM.path, "inputs/RSA_ID.csv"))
# RSHA.IDs     <- read.csv(paste0(CRBM.path, "inputs/RSHA_ID.csv"))
```

# Load conductivities

Conductivities that we load from CSV are in SI ($m \times s^{-1} \times Pa^{-1}$).
But MARSHAL takes non-SI units ($cm \times d^{-1} \times HPa^{-1}$).
So we need a factor of conversion.

kr : $1 \times cm*10^{-2} \times (d*60*60*24)^{-1} \times (HPa * 10^{-4})^{-1} = 1 \times m \times s^{-1} \times MPa^{-1} $
Kx : $1 \times (cm*10^{-2})^{4} \times (d*60*60*24)^{-1} \times (HPa * 10^{-4})^{-1} = 1 \times m \times s^{-1} \times MPa^{-1}  $


```{r}
# Conversion factors of kr and kx
conv_kr       <- 1e-2 * (60*60*24)^-1 * (1e-4)^-1
conv_kx       <- (1e-2)^4 * (60*60*24)^-1 * (1e-4)^-1

# List hydraulic Scenarios to load
list_S <- c("1A", "1B", "2", "3")

Conds.tot <- tibble()
for(S_id in list_S){
  conds.temp             <- read.csv(paste0("./Data/conds_scenarios/", S_id, ".csv"))
  conds.temp$Scenario_ID <- S_id
  Conds.tot              <- rbind(Conds.tot, conds.temp)
}
```

# Plot RSA

```{r}

```


# LOOP MPIPE

## Dev

```{r}
# DEFINE SIMULATIONS MACRO PARAMETERS
tmin          <- 0
tmax          <- 30
it_length     <- 15 
S_list        <- c("3_30")
gif.delay     <- 50
radius.range  <- c(0.75, 2)

# LOAD RSA FILES AND CREATE A META FILE
RSA_list      <- unique(RSA.IDs$RSA_id) # Implement a way to select RSA_ids
RSA.all       <- tibble()

RSA_id        <- RSA_list[1]
RSAi          <- read.csv(paste0(CRBM.path, "inputs/RSA/", RSA_id, ".csv"))
RSAi$RSA_id   <- RSA_id
RSA.all       <- rbind(RSA.all, RSAi)

# RUN MPIPE FOR EVERY SCENARIO
for(Sim_ID in S_list){
  Scenario_ID_i  <- Simulations_ID$Scenario_ID[Simulations_ID$Simulation_ID == Sim_ID]
  SG_timing_1    <- Simulations_ID$SG_timing_1[Simulations_ID$Simulation_ID == Sim_ID]
  SG_timing_2    <- Simulations_ID$SG_timing_2[Simulations_ID$Simulation_ID == Sim_ID]
  path.out       <- paste0(path.results, "test/")
  source("./src/MPIPE.R")
}
```


## 30 days old RSA

```{r, include=F}
# DEFINE SIMULATIONS MACRO PARAMETERS
tmin      <- 0
tmax      <- 30
it_length <- 1 
S_list    <- c("1A_30", "1B_30", "2_30", "3_30")
gif.delay <- 20
radius.range  <- c(0.75, 2)

# LOAD RSA FILES AND CREATE A META FILE
RSA_list  <- RSA.IDs$RSA_id # Implement a way to select RSA_ids
RSA.all   <- tibble()
for(RSA_id in RSA_list){
  RSAi          <- read.csv(paste0(CRBM.path, "inputs/RSA/", RSA_id, ".csv"))
  RSAi$RSA_id   <- RSA_id
  RSA.all       <- rbind(RSA.all, RSAi)
}

# RUN MPIPE FOR EVERY SCENARIO
for(Sim_ID in S_list){
  Scenario_ID_i  <- Simulations_ID$Scenario_ID[Simulations_ID$Simulation_ID == Sim_ID]
  SG_timing_1    <- Simulations_ID$SG_timing_1[Simulations_ID$Simulation_ID == Sim_ID]
  SG_timing_2    <- Simulations_ID$SG_timing_2[Simulations_ID$Simulation_ID == Sim_ID]
  path.out       <- paste0(path.results, Sim_ID, "/")
  source("./src/MPIPE.R")
}
```

## 60 days old RSA

```{r, include = F}
RSA.all        <- read.csv(paste0(CRBM.path, "inputs/RSA/Tomato_60d_1.csv"))
RSA.all$RSA_id <- "Tomato_60d_1"

tmin      <- 0
tmax      <- 60
it_length <- 1
S_list    <- c("1A_60", "1B_60", "2_60", "3_60")
gif.delay <- 10

for(Sim_ID in S_list){
  Scenario_ID_i  <- Simulations_ID$Scenario_ID[Simulations_ID$Simulation_ID == Sim_ID]
  SG_timing_1    <- Simulations_ID$SG_timing_1[Simulations_ID$Simulation_ID == Sim_ID]
  SG_timing_2    <- Simulations_ID$SG_timing_2[Simulations_ID$Simulation_ID == Sim_ID]
  path.out       <- paste0(path.results, Sim_ID, "/")
  source("./src/MPIPE.R")
}
```

# Process results of each scenario

```{r}
Macro_full <- tibble()
RSHA_full  <- tibble()
S_list     <- c("1A_60", "1B_60", "2_60", "3_60")

for(si in S_list){
  print(si)
  
  temp_path              <- paste0(path.results, si, "/")
  
  temp_Macro             <- read.csv(paste0(temp_path, "Macro_all.csv"))
  temp_Macro$Scenario_ID <- si
  Macro_full <- rbind(Macro_full, temp_Macro)
  
  temp_RSHA              <- read.csv(paste0(temp_path, "RSHA_all.csv"))
  temp_RSHA$Scenario_ID  <- si
  RSHA_full <- rbind(RSHA_full, temp_RSHA)
}

Macro_full <- Macro_full %>% 
  mutate(Sim_ID = paste0(RSA_id, "_", Scenario_ID))
```

## Analyse Krs

```{r}
p <- ggplot(Macro_full) +
  geom_point(aes(x = as.factor(age), y = Krs, group = Sim_ID, color = Scenario_ID)) +
  geom_line(aes(x = as.factor(age), 
                y = Krs, 
                group = Sim_ID, 
                color = Scenario_ID), 
            alpha = 0.2) +
  geom_boxplot(aes(x = as.factor(age), y = Krs, fill = Scenario_ID)) +
  xlab("Age [d]") +
  ylab("Krs") +
  theme_classic()

# ggplotly(p)

ggsave(filename = "Krs_full_60.png", plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 20, height = 10)
```


Compare all root systems at day 30

```{r}
data2plot <- RSHA_full %>% 
  filter(age == 30) 

data2plot_main <- data2plot %>% filter(type == 1)
data2plot_lat <- data2plot %>% filter(type == 2)

p <- ggplot() +
  
  geom_segment(data = data2plot_main,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   size = radius),
               color = "blue") +  
  
  geom_segment(data = data2plot_lat,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = SUF, size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2plot$radius), 
                                   max(data2plot$radius))) +
  
  scale_color_viridis_c(option = "magma",
                          breaks = c(min(data2plot_lat$SUF), 
                                     max(data2plot_lat$SUF)),
                          # labels = c("low", "high"),
                          direction = 1
                          # , limits = c(0, max(RSHA.all$SUF[RSHA.all$RSA_id == RSA_id_i]))
                          ) +
  
  facet_grid(Scenario_ID ~ RSA_id) +
  coord_fixed() +
  theme_classic() 

ggsave(filename = "RSA_30.png", plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 30, height = 10)
```

```{r}
data2plot <- RSHA_full %>% 
  filter(age == 30) 

data2plot_main <- data2plot %>% filter(type == 1)
data2plot_lat <- data2plot %>% filter(type == 2)

p <- ggplot() +
  
  geom_segment(data = data2plot_main,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   size = radius),
               color = "blue") +  
  
  geom_segment(data = data2plot_lat,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = SUF, size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2plot$radius), 
                                   max(data2plot$radius))) +
  
  scale_color_viridis_c(option = "magma",
                          breaks = c(min(data2plot_lat$SUF), 
                                     max(data2plot_lat$SUF)),
                          # labels = c("low", "high"),
                          direction = 1
                          # , limits = c(0, max(RSHA.all$SUF[RSHA.all$RSA_id == RSA_id_i]))
                          ) +
  
  facet_grid(RSA_id ~Scenario_ID) +
  coord_fixed() +
  theme_classic() 

ggsave(filename = "RSA_60.png", plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 30, height = 10)
```

