---
title: "MPIPE"
format: html
editor: source
---

# Load dependancies

```{r, include=F}
# knitr::opts_chunk$set(echo = FALSE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # Set working directory to the current file
rm(list = ls())

options(rstudio.help.showDataPreview = FALSE)

# Define paths
CRBM.path    <- "./src/CRB-MARSHAL/"
path.results <- "./Results/CRB-MARSHAL/"
path.plots   <- "./plots/CRB-MARSHAL/"

libs <- c("pander", "readxl", "EnvStats", "FactoMineR", "factoextra", "data.table", "reticulate", "xml2", 
          "tidyverse", "dplyr", "viridis", "Hmisc", "ggplot2", "gridExtra", "Matrix", "emmeans", "ggthemes")

for(pk in libs) {
  library(pk, character.only = T)
}

# source(paste0(CRBM.path,"io_function.R")) # CROOTBOX
source(paste0(CRBM.path, "Get_SUF.R")) # MARSHAL
source(paste0(CRBM.path, "SUF.R"))
source(paste0(CRBM.path, "CRBM_functions.R"))

TRoot_path <- "./src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path, pattern = ".R")) {
  print(i)
  source(paste0(TRoot_path, i))
}

# LOAD DATA TABLES
Simulations_ID <- read_xlsx(paste0(CRBM.path, "inputs/Simulations_ID.xlsx"))
Scenarios_ID   <- read_xlsx(paste0(CRBM.path, "inputs/Scenarios_ID.xlsx"))
RSA.IDs        <- read.csv(paste0(CRBM.path, "inputs/RSA_id.csv"))
```

# Load Root System Architectures

We generated raw Root System Architectures (RSA) from CRootBox online interface and stored them in `./src/CRB-MARSHAL/inputs/RSA/raw/ folder`. \ 
We need to process them, and then we store them in `./src/CRB-MARSHAL/inputs/RSA/` folder. \
Each RSA is associated with a RSA_id and we create a table `RSA_id`. \

```{r}
# RSA.path     <- "./src/CRB-MARSHAL/inputs/RSA/"
# RSA.path.raw <- paste0(RSA.path, "raw/")
# 
# RSA_list <- list.files(RSA.path.raw, pattern = ".txt")
# 
# RSA.all <- tibble()
# RSA.IDs <- tibble()
# 
# for(RSA_i in RSA_list){
# 
#   # Load and process temp RSA
#   RSA_id_i        <- unlist(strsplit(RSA_i, split = ".txt"))[1]
#   RSA_temp        <- read.table(paste0(RSA.path.raw, RSA_i), header = T)
#   RSA_temp        <- reconnect.nodes(RSA_temp)
#   RSA_temp$RSA_id <- RSA_id_i
#   write.csv(x = RSA_temp, file = paste0(RSA.path, RSA_id_i, ".csv"), row.names = F)
# 
#   # Update RSA.IDs table
#   RSA_id_i_df     <- tibble(planttype = unlist(strsplit(RSA_id_i, split = "_"))[1],
#                             age       = unlist(strsplit(RSA_id_i, split = "_"))[2],
#                             rep       = unlist(strsplit(RSA_id_i, split = "_"))[3],
#                             RSA_id    = RSA_id_i)
#   RSA.IDs <- rbind(RSA.IDs, RSA_id_i_df)
# 
#   # Add RSA to global RSA.all table
#   RSA.all <- rbind(RSA.all, RSA_temp)
# }
# 
# write.csv(x = RSA.all,
#           file = paste0(CRBM.path, "inputs/RSA_all.csv"),
#           row.names = F)
# 
# write.csv(x = RSA.IDs,
#           file = paste0(CRBM.path, "inputs/RSA_id.csv"),
#           row.names = F)
```

```{r}
RSA.all <- read.csv(paste0(CRBM.path, "inputs/RSA_all.csv"))

RSA_plot <- ggplot(RSA.all) +
  geom_segment(aes(x = x1, xend = x2, 
                   y = z1, yend = z2, 
                   color = branchID)
               ) +
  facet_wrap(~RSA_id, nrow = 2) +
  scale_color_viridis(option = "plasma") +
  coord_fixed() +
  theme_few()

RSA_plot

ggsave(filename = paste0(path.plots, "RSA_raw.png"), 
       plot = RSA_plot, device = "png", 
       width = 10, height = 5, dpi = 300)
```

# Define conductivities

Here we build and plot conductivities curves that we will apply in MARSHAL. \
First, load coefficients of kr and Kx regressions computed in TROOT_ANALYSIS \
* kr is converted from $m s^{-1} MPa^{-1}$ to $cm d^{-1} HPa^{-1}$ \
* Kx is converted from $m^3 s^{-1} MPa^{-1}$ to $cm^4 d^{-1} HPa^{-1}$ \

```{r}
coefficients_kr <- read.csv("./Data/kr_coefficients.csv")
coefficients_Kx <- read.csv("./Data/Kx_coefficients.csv")

conv_kr   <-  0.001157407
conv_kx   <-  1.157407e-09
```

Let's define 3 scenarios :

-   1A : \
    -   SG   = T \
    -   LC   = T \
    -   SE   = T \
    -   kAQP = constant \
-   1B : \
    -   SG   = T \
    -   LC   = T \
    -   SE   = T \
    -   kAQP = decreasing \
-   2 : \
    -   SG   = T \
    -   LC   = T \
    -   SE   = F \
    -   kAQP = constant \
-   3 : \
    -   SG   = F \
    -   LC   = T \
    -   SE   = F \
    -   kAQP = constant \

## General parameters

```{r}
source("./src/CRB-MARSHAL/CRBM_functions.R")

# DEFAULTS PARAMETERS
nmin         <- 0
nmax         <- 60         # Maximum number of iterations

# SG TIMING (default 7 - 20)
SG_timing1A  <- c(7, 25)
SG_timing1B  <- c(7, 25)
SG_timing2   <- c(7, 25)
SG_timing3   <- c(100, 101)

# MS TIMING (default 7 - 20)
MS_timing1A  <- c(7,   100)
MS_timing1B  <- c(7,   100)
MS_timing2   <- c(100, 101)
MS_timing3   <- c(100, 101)

rmin         <- 0.1887     # minimum radius (default = 0.1887 from data)
rmax         <- 2          # maximum radius
kAQP_start   <- 6.35e-7    # kAQP (default = 6.35e-7)
kAQP_end     <- 6.35e-7    # 
Kx.max       <- 1e-8

# ============================================================================ #
# SCENARIO 1A
Conds_S1A <- create.conds(S_ID = "1A"
                          ,nmin       = nmin
                          ,nmax       = nmax
                          ,SG_timing  = SG_timing1A
                          ,MS_timing  = MS_timing1A
                          ,kr.coeff   = coefficients_kr
                          ,Kx.coeff   = coefficients_Kx
                          ,kAQP_start = 6.35e-7
                          ,kAQP_end   = 6.35e-7
                          ,rmin       = 0.1887
                          ,rmax       = 2
                          ,Kx.max     = Kx.max
                          )
mparam_1A <- tibble(SG_timing = SG_timing1A,
                    MS_timing = MS_timing1A,
                    rmin      = rmin,
                    rmw       = rmax,
                    S_ID      = "1A")
# ============================================================================ #
# SCENARIO 1B
Conds_S1B <- create.conds(S_ID = "1B"
                          ,nmin        = nmin
                          ,nmax        = nmax
                          ,SG_timing  = SG_timing1B
                          ,MS_timing  = MS_timing1B
                          ,kr.coeff   = coefficients_kr
                          ,Kx.coeff   = coefficients_Kx
                          ,kAQP_start = 6.35e-7
                          ,kAQP_end   = 1e-16
                          ,rmin       = 0.1887
                          ,rmax       = 2
                          ,Kx.max     = Kx.max
                          )
mparam_1B <- tibble(SG_timing = SG_timing1B,
                    MS_timing = MS_timing1B,
                    rmin      = rmin,
                    rmw       = rmax,
                    S_ID      = "1B")
# ============================================================================ #
# SCENARIO 2
Conds_S2 <- create.conds(S_ID = "2"
                         ,nmin       = nmin
                         ,nmax       = nmax
                         ,SG_timing  = SG_timing2
                         ,MS_timing  = MS_timing2
                         ,kr.coeff   = coefficients_kr
                         ,Kx.coeff   = coefficients_Kx
                         ,kAQP_start = 6.35e-7
                         ,kAQP_end   = 6.35e-7
                         ,rmin       = 0.1887
                         ,rmax       = 2
                         ,Kx.max     = Kx.max
                         )
mparam_2 <- tibble(SG_timing = SG_timing2,
                    MS_timing = MS_timing2,
                    rmin      = rmin,
                    rmw       = rmax,
                   S_ID       = "2")
# ============================================================================ #
# SCENARIO 3
Conds_S3 <- create.conds(S_ID = "3"
                         ,nmin        = nmin
                         ,nmax        = nmax
                         ,SG_timing  = SG_timing3
                         ,MS_timing  = MS_timing3
                         ,kr.coeff   = coefficients_kr
                         ,Kx.coeff   = coefficients_Kx
                         ,kAQP_start = 6.35e-7
                         ,kAQP_end   = 6.35e-7
                         ,rmin       = 0.1887
                         ,rmax       = 1
                         ,kr.min     = 6.5e-8
                         ,kr.max     = 6.5e-8   
                         ,Kx.min     = 1e-10
                         ,Kx.max     = 2e-10  # Manually limited !
                         )
mparam_3 <- tibble(SG_timing = SG_timing3,
                   MS_timing = MS_timing3,
                   rmin      = rmin,
                   rmw       = rmax,
                   S_ID = "3")
# ============================================================================ #
# Rbind all scenarios together
Conds.tot <- rbind(Conds_S1A, Conds_S1B) %>% 
  rbind(Conds_S2) %>% rbind(Conds_S3)

mparams   <- rbind(mparam_1A, mparam_1B) %>% 
  rbind(mparam_2) %>% rbind(mparam_3)


# Convert kr and Kx to cm d HPa
Conds.tot$y[Conds.tot$type == "kr"]   <- Conds.tot$y[Conds.tot$type == "kr"]/conv_kr
Conds.tot$y[Conds.tot$type == "kAQP"] <- Conds.tot$y[Conds.tot$type == "kAQP"]/conv_kr
Conds.tot$y[Conds.tot$type == "kx"]   <- Conds.tot$y[Conds.tot$type == "kx"]/conv_kx

ggplot(Conds.tot) +
  geom_line(aes(x = x, y = y, color = S_ID),
            size = 1,
            alpha = 0.5) +
  facet_grid(type~S_ID, scales = "free") +
  theme_bw()

# ============================================================================ #
# Add root types
roottypes <- tibble(order_id = c(1, 2),
                    order    = c("Taproot", "Lateral"))

Conds.tot <- merge(Conds.tot, roottypes)
```

Plot all together with a rectangle for MS

```{r}
rect_data <- expand.grid(start = 0, end = 0, 
                         MS = c("T1", "T2"), 
                         S_ID = unique(Conds.tot$S_ID))

rect_data$start[rect_data$S_ID == "1A" & rect_data$MS == "T1"] <- 1
rect_data$end[rect_data$S_ID   == "1A" & rect_data$MS == "T1"] <- 7
rect_data$start[rect_data$S_ID == "1A" & rect_data$MS == "T2"] <- 8
rect_data$end[rect_data$S_ID   == "1A" & rect_data$MS == "T2"] <- 60

rect_data$start[rect_data$S_ID == "1B" & rect_data$MS == "T1"] <- 1
rect_data$end[rect_data$S_ID   == "1B" & rect_data$MS == "T1"] <- 7
rect_data$start[rect_data$S_ID == "1B" & rect_data$MS == "T2"] <- 8
rect_data$end[rect_data$S_ID   == "1B" & rect_data$MS == "T2"] <- 60

rect_data$start[rect_data$S_ID == "2" & rect_data$MS == "T1"]  <- 1
rect_data$end[rect_data$S_ID   == "2" & rect_data$MS == "T1"]  <- 60
rect_data$start[rect_data$S_ID == "2" & rect_data$MS == "T2"]  <- 0
rect_data$end[rect_data$S_ID   == "2" & rect_data$MS == "T2"]  <- 0

rect_data$start[rect_data$S_ID == "3" & rect_data$MS == "T1"]  <- 1
rect_data$end[rect_data$S_ID   == "3" & rect_data$MS == "T1"]  <- 60
rect_data$start[rect_data$S_ID == "3" & rect_data$MS == "T2"]  <- 0
rect_data$end[rect_data$S_ID   == "3" & rect_data$MS == "T2"]  <- 0

S_full_plot <- ggplot(data = Conds.tot) +
  
  geom_rect(data = rect_data, 
            aes(xmin = start, xmax = end, 
                ymin = -Inf, ymax = Inf, 
                fill = MS
                ),
    alpha = 0.2
  ) +
  
  # Display curves
  geom_line(aes(x = x, y = y, 
                color = type),
            linewidth = 1) +
  
  # scale_color_manual(values = colors) +
  
  facet_grid(type~S_ID, scales = "free_y") +
  ylab("Value [normalised]") +
  xlab("Root age [d]") +
  theme_few() 

S_full_plot
ggsave(plot = S_full_plot, filename = "./plots/CRB-MARSHAL/Scenarios_full.svg", device = "svg", width = 8, height = 5)
```

# LOOP MPIPE

So we want to loop MARSHAL for each S_ID of Conds.tot

```{r, include = F}
source("./src/CRB-MARSHAL/CRBM_functions.R")

# DEFINE SIMULATIONS MACRO PARAMETERS
tmin          <- 0
tmax          <- 60
it_length     <- 10
S_list        <- unique(Conds.tot$S_ID)
gif.delay     <- 50
radius.range  <- c(0.75, 2)

# SG_timing     <- c(7, 25)

# LOAD RSA FILES AND CREATE A META FILE
RSA_list      <- unique(RSA.IDs$RSA_id) 
RSA.all       <- read.csv("./src/CRB-MARSHAL/inputs/RSA_all.csv") %>% 
  filter(RSA_id %in% RSA_list & time <= tmax)

RSA_plot <- ggplot(RSA.all) +
  geom_segment(aes(x = x1, xend = x2, 
                   y = z1, yend = z2, 
                   color = branchID)
               ) +
  facet_wrap(~RSA_id, nrow = 2) +
  scale_color_viridis(option = "plasma") +
  coord_fixed() +
  theme_few()

RSA_plot

# RUN MPIPE FOR EVERY SCENARIO
for(S_ID_i in S_list){

  Scenario_ID_i  <- S_ID_i
  
  Conds          <- Conds.tot %>% filter(S_ID == S_ID_i)
  
  SG_timing      <- mparams$SG_timing[mparams$S_ID == S_ID_i]
  MS_timing      <- mparams$MS_timing[mparams$S_ID == S_ID_i]
  rmin           <- min(Conds$y[Conds$type == "radius"])
  rmax           <- max(Conds$y[Conds$type == "radius"])
  
  path.out       <- paste0(path.results, S_ID_i, "/")
  
  S_ID           <- S_ID_i
  source("./src/MPIPE.R")
}
```

# Process results of each scenario

```{r}
# ============================================================================ #
# PROCESS RESULTS
# ============================================================================ #
Macro_full <- tibble()
RSHA_full  <- tibble()
S_list     <- c("1A", "1B", "2", "3")

for(si in S_list){
  print(si)
  
  temp_path              <- paste0(path.results, si, "/")
  
  temp_Macro             <- read.csv(paste0(temp_path, "Macro_all.csv"))
  temp_Macro$Scenario_ID <- si
  Macro_full             <- rbind(Macro_full, temp_Macro)
  
  temp_RSHA              <- read.csv(paste0(temp_path, "RSHA_all.csv"))
  temp_RSHA$Scenario_ID  <- si
  RSHA_full              <- rbind(RSHA_full, temp_RSHA)
}

Macro_full <- Macro_full %>% 
  mutate(Sim_ID = paste0(RSA_id, "_", Scenario_ID))


# ============================================================================ #
# ANALYSE KRS
# ============================================================================ #
p <- ggplot(Macro_full) +
  
  geom_line(aes(x = as.factor(age), 
                y = Krs, 
                group = Sim_ID, 
                color = Scenario_ID), 
            alpha = 0.2) +
  
  geom_boxplot(aes(x = as.factor(age),
                   y = Krs,
                   fill = Scenario_ID)
               ,width = 0.5
               ,outlier.shape = NA)+
  
  xlab("Age [d]") +
  ylab(expr(K[rs] ~ "[" ~ m^{4} ~ MPa^{-1} ~ s^{-1} ~ "]"))     +
  theme_classic()


p

ggsave(filename = paste0(path.plots, "Krs_full.svg"), 
       plot = p
       ,device = "svg"
       ,width = 5, height = 3)

# ============================================================================ #
# ANALYSE SUF
# ============================================================================ #

SUF_df2 <- RSHA_full %>% filter(age %in% c(30, 60)) %>% 
  select(c("SUF", "RSHA_id", "age", "Scenario_ID", "z1", "type")) %>% 
  mutate(zr = round(z1/2, digits = 0)*2) %>% 
  group_by(RSHA_id, zr, Scenario_ID, age) %>% 
  summarise(SUF_sum = sum(SUF)) %>% 
  ungroup() %>% 
  group_by(zr, Scenario_ID, age) %>% 
  summarise(SUF_sum_mean = mean(SUF_sum),
            SUF_sum_sd   = sd(SUF_sum)
            )

SUF_plot <- ggplot(data = SUF_df2) +
    
    # geom_bar(aes(x = zr, y = SUF_sum_mean, fill = Scenario_ID),
    #          stat = "identity", 
    #          position = "dodge", 
    #          alpha = 0.75) +
  
    geom_point(aes(x = zr, 
                   y = SUF_sum_mean, 
                   color = Scenario_ID)
               # ,position = position_dodge(2)
               ) +
    
    geom_errorbar(aes(x = zr, 
                      ymin = SUF_sum_mean-SUF_sum_sd, 
                      ymax = SUF_sum_mean+SUF_sum_sd,
                      color = Scenario_ID),
                  width = 0.5
                  # ,position = position_dodge(2)
                  ) +
  
    ylab("Standart Uptake Fractions [-]") +
    xlab("depth [cm]") +
    
    facet_wrap(~age, ncol = 1, scales = "free_y") +
    # coord_flip() +
    # ggtitle(paste0("Sum of SUF per scenario")) +
    theme_few() +
    theme(axis.text.x  = element_text(size = 8, angle = 90, hjust = 1, vjust = 0.5))
  
SUF_plot
ggsave(filename = paste0(path.plots, "SUF_sum_full.svg"), 
       plot = SUF_plot, 
       device = "svg", width = 5, height = 4)
```

## Compare all root systems

```{r}
data2plot <- RSHA_full %>% filter(age == 40)

data2plot_main <- data2plot %>% filter(type == 1)
data2plot_lat <- data2plot %>% filter(type == 2)

p <- ggplot() +
  
  geom_segment(data = data2plot_main,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   size = radius),
               color = "blue") +  
  
  geom_segment(data = data2plot_lat,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = SUF, size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2plot$radius), 
                                   max(data2plot$radius))) +
  
  scale_color_viridis_c(option = "magma",
                          breaks = c(min(data2plot_lat$SUF), 
                                     max(data2plot_lat$SUF)),
                          labels = c("low", "high"),
                          direction = 1
                          # , limits = c(0, max(RSHA.all$SUF[RSHA.all$RSA_id == RSA_id_i]))
                          ) +
  
  facet_grid(Scenario_ID ~ RSA_id) +
  coord_fixed() +
  theme_classic() 

p

ggsave(filename = "RSHA_full.png", plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 17, height = 10)
```

# Select only one for figure

```{r}
data2plot <- RSHA_full %>% filter(age == 60 & RSA_id == unique(RSA.IDs$RSA_id[1]))

data2plot_main <- data2plot %>% filter(type == 1)
data2plot_lat <- data2plot %>% filter(type == 2)

p <- ggplot() +
  
  geom_segment(data = data2plot_main,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   size = radius),
               color = "blue") +  
  
  geom_segment(data = data2plot_lat,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = SUF, size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2plot$radius), 
                                   max(data2plot$radius))) +
  
  scale_color_viridis_c(option = "magma",
                          breaks = c(min(data2plot_lat$SUF), 
                                     max(data2plot_lat$SUF)),
                          labels = c("low", "high"),
                          direction = 1
                          # , limits = c(0, max(RSHA.all$SUF[RSHA.all$RSA_id == RSA_id_i]))
                          ) +
  
  facet_wrap(~ Scenario_ID, nrow = 1) +
  coord_fixed() +
  theme_few() 

p

ggsave(filename = "RSHA_suf_example.png", plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 6, height = 4)
```


# Statistical analysis

## Krs

```{r}
for(age_i in unique(Macro_full$age)){
  cat("================= \n")
  cat("Age = ", age_i, "\n")
  cat("================= \n")
  temp_df <- Macro_full %>% filter(age == age_i)
  temp_lm <- lm(temp_df, formula = Krs ~ Scenario_ID)
  # plot(temp_lm)
  print(summary(temp_lm))
  print(emmeans(temp_lm, ~Scenario_ID))
}
```

## SUF

```{r}
for(age_i in unique(SUF_df2$age)){
  
  cat("================= \n")
  cat("Age = ", age_i, "\n")
  cat("================= \n")
  
  temp_SUF   <- SUF_df2 %>% filter(age == age_i)
  p <- ggplot(temp_SUF) +
    geom_point(aes(x = zr, y = SUF_sum_mean, color = Scenario_ID)) +
    geom_line(aes(x = zr, y = SUF_sum_mean, color = Scenario_ID))
  
  plot(p)
  
  distrib_1A <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "1A"]
  distrib_1B <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "1B"]
  distrib_2  <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "2"]
  distrib_3  <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "3"]
  
  # plot(distrib_1A)
  # plot(distrib_3)
  
  ks_test    <- ks.test(distrib_1A, distrib_3)
  print(ks_test)
}
```

Investigate peaks and plateau in 60 days old

```{r}
SUF_60 <- SUF_df2 %>% filter(age == 60)

subset_peak    <- SUF_60 %>% filter(zr == -24)
subset_plateau <- SUF_60 %>% filter(zr >= -10) 

SUF_lm1        <- lm(subset_peak, formula = SUF_sum_mean~Scenario_ID)
summary(SUF_lm1)
```

