---
title: "MAIN"
author: "Marco D'Agostino"
format: html
editor: source
editor_options: 
  chunk_output_type: inline
---

# INTRODUCTION

This notebook contains the main codes of the project T-ROOT

First we load the packages. NB : you may need to install some of them manually.

-   *GRANAR* libraries : I advise to get them directly from GITHUB

-   Specific functions for this notebook : load all functions in *src/FUNCTIONS/T-Root/*.

Other folders :

-   *Data* : contains all data used in these scripts

-   *src/MECHA/* : contains all codes to run MECHA

-   *src/Params/* : contains all quantified experimental cross sections in the form of GRANAR input parameters

-   *src/CRB-MARSHAL/* : contains all codes and data to run CRootBox and MARSHAL

Here we load an convert quantification data (in the form of *xlsx* files in *Data/Quantifications* folder) into GRANAR parameters (params). The params will be stored both into single *xml* files (in the folder *Params*) directly usible into GRANAR, and into the big table Anatomy2. The file *Data_Preparation.R* automatically load and treat data from *Data/Quantifications*.

-   *Plants* contains IDs, ages and lengths of each roots
-   *Segments* contains informations about segments of each root
-   *CrossSections* contains IDs and informations about each cross section
-   *anatomy1* contains all quantifiation data
-   *anatomy2* contains all values of all GRANAR params for each cross section
-   *Parameters* contains information about the measured and GRANAR params

```{r, include=F}
options(rstudio.help.showDataPreview = FALSE)
rm(list = ls())

# SET LOCATION
path_MECHA <- "./src/MECHA/"

# LOAD FUNCTIONS
TRoot_path <- "src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path, pattern = ".R")) {
  print(i)
  source(paste0(TRoot_path, i))
}

#LOAD PACKAGES
pkg_list <- c("fmsb", 
              "packcircles", 
              "pander", 
              "readxl", 
              "visreg", 
              "EnvStats", 
              "factoextra", 
              "data.table",
              "reticulate", 
              "xml2", 
              "tidyverse", 
              "deldir", 
              "viridis", 
              "Hmisc", 
              "devtools", 
              "ggplot2",
              "gridExtra", 
              "dplyr", 
              "cowplot", 
              "stats", 
              "emmeans", 
              "corrplot", 
              "sf", 
              "SciViews")

for(pk in pkg_list) {
  try(library(pk, character.only = T))
}

library(ggthemes)

# LOAD GRANAR FUNCTIONS
GRANAR_path <- "C:/Users/mdagostino/Desktop/GITHUB/granar/R/" # change with your directory
GRANAR_path <- "../granar/R/" # change with your directory
for (i in list.files(GRANAR_path, pattern = ".R")) {
  print(i)
  source(paste0(GRANAR_path, i))
}

# source("Data_preparation.R")

Plants         <- read.csv("Data/Anatomy/Plants.csv")
Segments       <- read.csv("Data/Anatomy/Segments.csv")
CrossSections  <- read.csv("Data/Anatomy/CrossSections.csv")
anatomy1       <- read.csv("Data/Anatomy/anatomy1.csv")
anatomy2       <- read.csv("Data/Anatomy/anatomy2.csv")
Parameters     <- read.csv("Data/Anatomy/Parameters.csv")
Anatomy_Full   <- read.csv("Data/Anatomy/Anatomy_Full.csv")
Barriers_Types <- read_xlsx("Data/Barriers_Types.xlsx")

date           <- Sys.Date()

# Correct units in Parameters
Parameters$units[Parameters$param_id == "xylem_max_size" | Parameters$param_id == "xylem_cell_diameter"] <- "mm"
```

```{r}
## All anatomical data in standard table ; Create Anatomy_Full.csv

# Anatomy_Full <- anatomy2 %>% 
#   spread(key = param_id, value = value) %>% 
#   left_join(CrossSections, by = "CS_id") %>% 
#   mutate(radius = 
#            cortex_cell_diameter * cortex_n_layers +
#            endodermis_cell_diameter * endodermis_n_layers +
#            epidermis_cell_diameter * epidermis_n_layers +
#            exodermis_cell_diameter * exodermis_n_layers +
#            stele_layer_diameter/2
#            )

# write.csv(Anatomy_Full, "Data/Anatomy/Anatomy_Full.csv", row.names = F)
```

# 0) Analysis of quantifications

This part load and analyse the cross section quantifications.

First let's have a look at metadata. 

So we had 

## Root lengths

```{r}
head(Plants)

Plants$days2 <- as.factor(Plants$days)

# LENGTHS
ggplot(data = Plants, aes(color = days2)) +
  geom_point(aes(x = days2, y = length)) +
  geom_boxplot(aes(x = days2, y = length)) + 
  # facet_wrap(~days) +
  theme_bw() +
  ggtitle("Root length (cm")

#GROWTH RATE
ggplot(data = Plants, aes(color = days2)) +
  geom_point(aes(x = days2, y = growth_rate)) +
  geom_boxplot(aes(x = days2, y = growth_rate)) +
  theme_bw() +
  ggtitle("Growth rate (cm/d)")
```

## Visualization of data per param

*anatomy2* contains quantified anatomical traits for 43 cross-sections

```{r}
summary(anatomy2)

data2plot <- anatomy2 %>% 
  left_join(Parameters[c("name", "type", "param_id", "units")], by = "param_id") %>% 
  left_join(CrossSections[c("CS_id", "age", "plant_id")], by = "CS_id") %>% 
  mutate(Title = paste0(name, " ", type," [", units, "]"))

cols <- c(
  "cortex_cell_diameter",
  "cortex_n_layers", 
  "endodermis_cell_diameter", 
  "epidermis_cell_diameter",
  "exodermis_cell_diameter",
  "pericycle_cell_diameter",
  "phloem_cell_diameter",
  "phloem_n_layers",
  "phloem_proportion",
  # "secondarygrowth_param",
  "stele_cell_diameter",
  "stele_layer_diameter",
  "stele_n_layers",
  "stele_SD",
  "xylem_cell_diameter",
  "xylem_max_size",
  "xylem_n_cells"
  )

p <- ggplot(data = data2plot %>% filter(param_id %in% cols)) +
  geom_point(aes(x = age, y = value, color = plant_id)) +
  facet_wrap(~Title, 
             scales = "free",
             ncol = 4) +
  theme_few() +
  theme(
    legend.position = "right"
  ) +
  theme(strip.text = element_text(size = 8))

p
ggsave(filename = "plots/Anatomy/Anatomy_Quantifications.svg", 
       plot = p, width = 10, height = 7, units = "in",
       device = "svg")
```

Plot all individual quantified traits in *plots/anatomical_measurements/* 

```{r}
# param_id_i <- cols[5]

for(i in seq(1, length(cols))){
  
  param_id_i <- cols[i]
  title_i <- unique(data2plot$Title[data2plot$param_id == param_id_i])
  2
  p_temp <- ggplot(data = data2plot %>% filter(param_id == param_id_i)) +
    geom_point(aes(x = age, y = value)) +
    # facet_wrap(~Title, scales = "free", ncol = 4) +
    ggtitle(title_i) +
      
    theme_few() +
    theme(
      legend.position = "right"
    ) +
    theme(plot.title = element_text(size=9))

  ggsave(filename = paste0("plots/Anatomy/measurements/", param_id_i, ".svg"), 
         plot = p_temp, width = 2.5, height = 2.5, units = "in",
         device = "svg")
}
```

## Secondary Growth

Secondary Growth was monitored as binary (0 = primary growth, 1 = secondary growth).
Note that the *intermediate* phase is classified as secondary growth.

```{r}
SG_data <- anatomy2 %>% 
  filter(param_id == "secondarygrowth_param") %>% 
  left_join(CrossSections[c("CS_id", "age", "plant_id")], by = "CS_id")

# SG_data$value <- as.factor(SG_data$value)

p <- ggplot(data = SG_data) +
  geom_jitter(aes(x = age, y = value),
              color = "grey1",
              height = 0.01,
              width = 0,
              alpha = 0.75) +
  stat_smooth(aes(x = age, y = value), 
              color = "red", linetype = 2,
              method = "glm",
              method.args=list(family="binomial")) +
  ylab("SG presence") +
  theme_few()

p
ggsave(filename = "plots/Anatomy/SG_probability.svg", 
       plot = p, width = 3, height = 2, units = "in",
       device = "svg")
```

## Radius 

Here we see that radius can be approximated as constant till 25 days, at 0.199 mm. Then, after 25 days, it can be approximated using : $r = exp(-7.59 + 0.23x)$

```{r}
radius_data <- Anatomy_Full[c("radius", "age")]

# Set secondary growth treshold
treshold    <- 25

# Linear model 1
radius_lm1  <- lm(data = radius_data %>%
                    filter(age < treshold), 
                  formula = radius ~ 1)

summary(radius_lm1)
mrad        <- radius_lm1$coefficients[1]

# Linear model 2
radius_lm2  <- lm(data = radius_data %>%
                    filter(age >= treshold), 
                  formula = ln(radius) ~ age)
summary(radius_lm2)

# Extract parameters from lm2
alpha       <- radius_lm2$coefficients[1]
beta        <- radius_lm2$coefficients[2]

# Create an dataframe to store the regression
pred1 <- predict(object  = radius_lm1, 
                 newdata = data.frame(age = seq(1, treshold),
                                      radius = 1), 
                 interval = "confidence")

pred1_df <- data.frame(age      = seq(1, treshold),
                       radius   = pred1[,"fit"],
                       lower_ci = pred1[, "lwr"],
                       upper_ci = pred1[, "upr"])

pred2 <- exp(predict(object  = radius_lm2, 
                 newdata = data.frame(age = seq(treshold, 30),
                                      radius = 1), 
                 interval = "confidence")
             )

pred2_df <- data.frame(age      = seq(treshold, 30),
                       radius   = pred2[, "fit"],
                       lower_ci = pred2[, "lwr"],
                       upper_ci = pred2[, "upr"])

radius_pred <- rbind(pred1_df, pred2_df)
```


```{r}
radius_plot <- ggplot() +
  
  geom_ribbon(data = radius_pred,
              aes(x = age, ymin = lower_ci, ymax = upper_ci),
              fill = "orange", 
              alpha = 0.5,
              ) +
  
  geom_point(data = radius_data, 
             aes(x = age, y = radius), 
             size = 1) + 
  
  geom_line(data = radius_pred, 
            aes(x = age, y = radius), 
            linetype = 2, 
            color = "red", linewidth = 1.2) +
  
  xlab("Age [d]") +
  ylab("Radius [mm]") +
  theme_bw()

radius_plot
svg("Plots/Anatomy/Radius_Plot.svg", width = 3, height = 2)
radius_plot
dev.off()
```

## Correlations

```{r}
prm <- c("cortex_n_layers", 
         "endodermis_cell_diameter", 
         "exodermis_cell_diameter",
         "pericycle_cell_diameter",
         "phloem_cell_diameter",
         "phloem_n_layers",
         "phloem_proportion",
         "stele_cell_diameter",
         "stele_layer_diameter",
         "stele_n_layers",
         "stele_SD",
         "xylem_cell_diameter",
         "xylem_max_size",
         "xylem_n_cells",
         "radius",
         "age")

svg(filename = "plots/Anatomy/Anatomy_Correlations.svg", width = 6, height = 6)
pcor <- corrplot(cor(Anatomy_Full[prm]), 
                 method = "color",
                 # type = "upper"
                 diag = F,
                 )
dev.off()
```

## Apoplastic Barriers

```{r}
Barriers_Timing <- read_xlsx("./Data/Barriers_Timings.xlsx") %>%
  separate(CS_id, into = c("plant_id", "segment", "coloration", "cut", "zoom", "repetition"), sep = "_") %>% 
  gather(Endo, Exo, key = "tissue", value = "barrier")
  

ggplot(Barriers_Timing) +
  geom_point(aes(x = age, y = barrier, color = tissue)) +
  theme_few()
```


## Parameter regressions

Generate individual regressions

```{r}
source("src/FUNCTIONS/T-Root/Functions_Misc.R")
source("src/Regressions_Auto.R")
```

```{r}
data2plot <- reg_data %>% 
  filter(param_id != "stele_SD") %>% 
  left_join(Parameters, by = "param_id") %>% 
  mutate(plot_title = paste(name, "|", type, " [", units, "]"))

p <- ggplot(data2plot) +
  geom_ribbon(aes(x = age, ymax = reg+sd, ymin = reg-sd),
              fill = "orange", alpha = 0.5) +
  geom_point(aes(x = age, y = value)) +
  geom_line(aes(x = age, y = reg), 
            color ="red", linetype = 2
             ) +
  
  xlab("Age [d]") +
  facet_wrap(~plot_title, scales = "free") +
  theme_few() +
  theme(strip.text = element_text(size = 9))

ggsave(filename = "./plots/Regressions.svg", plot = p, 
       device = "svg", width = 10, height = 9)

ggsave(filename = "./plots/Regressions.png", plot = p, 
       device = "png", width = 10, height = 9)

p
```

# 1) GRANAR

GRANAR is the generator of root anatomy in R (Heymans 2020).

Run the following chunks to checks if all is good with GRANAR.\
Examples of parameter files are in \*/Params/.

## Load params

```{r}
# xml <- "Params/examples/B73_taproot_2021.xml"
xml <- "src/Params/B04_B_To_C01_Z20_01.xml"

param1 <- read_param_xml(xml)

# Modify some parameters
# param1$value[param1$name == "secondarygrowth" & param1$type == "param"] <- 1
# param1$value[param1$name == "phloem" & param1$type == "n_layers"]       <- 0
param1$value[param1$name == "param" & param1$type == "randomness"]        <- 0
# param1$value[param1$name == "cortex" & param1$type == "n_layers"]         <- 1
# param1$value[param1$name == "cortex" & param1$type == "cell_diameter"]    <- 0.005
# param1$value[param1$name == "epidermis" & param1$type == "cell_diameter"] <- 0.005
# param1$value[param1$name == "exodermis" & param1$type == "cell_diameter"] <- 0.005
```



## Play with GRANAR

```{r, warning=F}
# PRIMARY GROWTH
sim1 <- create_anatomy(parameters = param1, verbatim = F)

# svg("test.svg")
plot_anatomy(sim1)
# dev.off()
```

### Run GRANAR for all data

And store anatomies in Anatomies/data/

```{r, include=F, eval=F}
path <- "Data/Virtual Anatomies/"
param_list <- list.files("src/Params/", pattern = ".xml")

for(param_i in param_list){
  print(param_i)
  param_temp <- read_param_xml(paste0("src/Params/",param_i))
  try(expr = {
      sim_temp <- create_anatomy(parameters = param_temp, verbatim = F)
      write_anatomy_xml(sim = sim_temp, path = paste0(path, param_i))
      
      p <- plot_anatomy(sim_temp)
      ggsave(filename = paste0(path, strsplit(param_i, ".xml")[[1]], ".svg")
             ,plot = p
             ,device = "svg"
             ,width = 5, height = 5
             ) 
    }
  )
}
```

# 2) MECHA

## Presentation and Installation

MECHA is the solver of local conductivities (Couvreur 2018)

Set up steps to run it in local :

1.  Open **ANACONDA NAVIGATOR**

2.  Create a new environment with **python 3.7** (in this work it is called "**MECHA2**")\
    `conda create -n MECHA2 python=3.7`

3.  Open the console of this environment and enter the following :\
    `conda install numpy`\
    `conda install scipy`\
    `conda install matplotlib`\
    `conda install lxml`\
    `conda install pip`\
    `pip install networkx==1.9.1`

4.  Open *MECHAv4_septa_temp_V2.py* and change directories to the current path (in the form "*C:/.../MECHA/"*)

To run MECHA, we first load the root of interest by changing *current_root*. Next we run the MECHA file.

By default, MECHA can simulate different scenarios : \*

-   **B0 : No apoplastic barriers**

-   **B1 : Endodermal Casparian strip (radial walls)**

-   **B2 : Endodermal suberization except at passage cells**

-   **B3 : Endodermis full suberization**

-   **B4 : Endodermis full suberization and exodermal Casparian strip (radial walls)**

-   **B5 : Endo- and exodermal Casparian strips (radial walls)**

-   **B6 : Exodermis full suberization and endodermal Casparian strip (radial walls)**

-   **B7 : Exodermal Casparian strip (radial walls)**

-   **B8 : Endo and exodermal suberization**

-   **B9: Lignin Cap and endodermal CS**

Here we choose to compute scenarios 0, 1, 5 and 6. You can change the simulated scenarios in *MECHA/Projects/granar/in/Maize_Geometry.xml* in line 19.

```{r}
# Load a GRANAR anatomy file
anatomy_path <- "Data/Virtual Anatomies/"
anatomy_file <- "B04_B_To_C01_Z20_01.xml"

# Quick look at current_root
test <- get_root_section(paste0(anatomy_path, anatomy_file))
ggplot(test) +
    # geom_polygon(aes_string("x", "y", group="id_cell", fill=col), colour="white") +
    geom_polygon(aes(x = x, y = y, fill = type, group = id_cell),
                 color = "white") +
    theme_classic() +
    coord_fixed() +
    theme(axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank())

# Load MECHA functions
source("./src/MECHA/MECHA_functions.R")

# Upload current anatomy to MECHA folder
MECHA.upload_anatomy(filename = "B04_B_To_C01_Z20_01.xml",
                     filepath = "./Data/Virtual Anatomies/",
                     path_MECHA = "./src/MECHA/")

```

## Test MECHA for one anatomy

```{r}
# LOAD XML AS A BIG LIST
read_path <- "./src/MECHA/Projects/in/"

# Read XML input files as templates
MECHA_inputs_list <- read_MECHA_inputs(read_path,
                                       file_General = "Tomato_General.xml",
                                       file_Hydraulics = "Tomato_Hydraulics.xml",
                                       file_Hormones = "Tomato_Hormones_Carriers.xml",
                                       file_BC = "Tomato_BC.xml",
                                       file_Geometry = "Tomato_Geometry.xml"
                                       ) 

# MODIFY MECHA INPUTS BY HAND
MECHA_inputs_list$General$properties$Output$path        <- "out/"
MECHA_inputs_list$Hydraulics$param$kAQPrange$kAQP$value <- 1.5e-4

# WRITE XML's
write_MECHA_inputs(input_list = MECHA_inputs_list, 
                   path = paste0(path_MECHA, "Projects/in/"), 
                   file_General    = "Tomato_General.xml",
                   file_Hydraulics = "Tomato_Hydraulics.xml", 
                   file_Hormones   = "Tomato_Hormones_Carriers.xml",
                   file_BC         = "Tomato_BC.xml",
                   file_Geometry   = "Tomato_Geometry.xml")
```

Launch MECHA

```{r}
library(reticulate)
use_condaenv("GRANAR-MECHA") # choose python environment 
sys <- import("sys", convert=T)

# ============================================================================ #
py_run_file("src/MECHA/MECHAv4_TRoot.py")
Conds <- MECHA_get_results(output_path = "./src/MECHA/Projects/out/")

```

Visualization (in devlopment)

```{r, eval=FALSE}
rp <- "./src/MECHA/Projects/out/"

Flux1 <- ApoSymp(paste0(rp,"Macro_prop_1,1.txt")) # En.CS
Flux9 <- ApoSymp(paste0(rp,"Macro_prop_9,9.txt")) # En.CS-Ex.LC
Flux6 <- ApoSymp(paste0(rp,"Macro_prop_6,6.txt")) # En.CS-Ex.Sub

plot_water_flux(Flux1, apobar = 3)
plot_water_flux(Flux9, apobar = 3)
plot_water_flux(Flux6, apobar = 3)
```

## Run MECHA for all quantified anatomies

We need to run MECHA for :

* Each GRANAR anatomy

* 10 values of kAQP (ranging from 1 to 10 e-4 cm HPa-1 d-1)

* 10 values of PDM?

Define parametric space

```{r, eval= F}
# List files of GRANAR anatomies
Anatomy_list <- list.files(path = "./Data/Virtual Anatomies/", pattern = ".xml")

# Set hydraulic parameters
kAQP_list    <- seq(1:10)*1e-4  # Elhert et al. (2009) : 4.3e-4 [cm/HPa/d]
kpl_list     <- 5.3e-12         # Bret-Harte 1994      : 5.3e-12 [cm^3/hPa/d/plasmodesmata]

hydro_params  <- expand.grid(kAQP = kAQP_list, kpl  = kpl_list)

hydro_params <- hydro_params %>% 
  mutate(Simu_ID = paste0(kAQP, "_", kpl))
```

```{r, include = F}
library(reticulate)
source("./src/MECHA/MECHA_functions.R")

# Set up
path_MECHA         <- "./src/MECHA/"                       # Path to MECHA folder
read_path          <- paste0(path_MECHA, "Projects/in/")   # Path to MECHA inputs
MECHA_file         <- "MECHAv4_TRoot.py"                   # MECHA file
output_path        <- paste0(path_MECHA, "Projects/out/")  # Path to MECHA outputs
write_results_path <- "./Results/MECHA_results/"           # Path to results

Results_list <- list.files(write_results_path)

# use_condaenv("GRANAR-MECHA") # choose python environment
# sys <- import("sys", convert=T)

# ============================================================================ #
# INITIALIZATION
Conds_full <- tibble()
sim_count  <- 0
sim_tot    <- length(Anatomy_list) * nrow(hydro_params)

# LOOP FOR ANATOMY
for(anatomy in Anatomy_list){
  
  CS_id <- unlist(strsplit(anatomy, split = ".xml"))[1]
  
  # Move anatomy to MECHA folder
  MECHA.upload_anatomy(filename = anatomy,
                       filepath = "./Data/Virtual Anatomies/",
                       path_MECHA = "./src/MECHA/")
  
  # ============================= #
  # LOOP FOR HYDRAULIC PARAMETERS
  for(i in seq(1, nrow(hydro_params))){
    
    sim_count <- sim_count + 1
    cat("Simulating ", sim_count, "/", sim_tot, "\n")
    
    Simu_ID <- hydro_params$Simu_ID[i]
    kAQP    <- hydro_params$kAQP[i]
    kpl     <- hydro_params$kpl[i]
    
    # Check if the Result_ID has already been simulated
    Result_ID <- paste0(CS_id, "_", Simu_ID)
    if(paste0(Result_ID, ".csv") %in% Results_list){
      cat("Already simulated, skip to next ... \n")
      next
    }
    
    # ======================== #
    # UPDATE MECHA PARAMS
    # ======================== #
    
    # Load MECHA parameters
    MECHA_inputs_list <- read_MECHA_inputs(read_path,
                                           file_General    = "Tomato_General.xml",
                                           file_Hydraulics = "Tomato_Hydraulics.xml",
                                           file_Hormones   = "Tomato_Hormones_Carriers.xml",
                                           file_BC         = "Tomato_BC.xml",
                                           file_Geometry   = "Tomato_Geometry.xml"
                                           ) 
    
    # Modify Inputs
    MECHA_inputs_list$General$properties$Output$path        <- "out/"
    MECHA_inputs_list$Hydraulics$param$kAQPrange$kAQP$value <- kAQP
    MECHA_inputs_list$Hydraulics$param$Kplrange$Kpl$value   <- kpl
    
    # WRITE XML's
    write_MECHA_inputs(input_list = MECHA_inputs_list, 
                       path = paste0(path_MECHA, "Projects/in/"), 
                       file_General    = "Tomato_General.xml",
                       file_Hydraulics = "Tomato_Hydraulics.xml", 
                       file_Hormones   = "Tomato_Hormones_Carriers.xml",
                       file_BC         = "Tomato_BC.xml",
                       file_Geometry   = "Tomato_Geometry.xml")
    
    # ======================== #
    # LAUNCH MECHA
    # ======================== #
    
    # Clean output path
    unlink(output_path, recursive = T)
    dir.create(output_path)
    
    # Unleash MECHA
    try(expr = {
      py_run_file(paste0(path_MECHA, MECHA_file))
    
      # ======================== #
      # COLLECT RESULTS
      # ======================== #
      Conds_temp <- MECHA_get_results(output_path = output_path)
      Conds_temp$CS_id   <- CS_id
      Conds_temp$kAQP    <- kAQP
      Conds_temp$kpl     <- kpl
      Conds_temp$Simu_ID <- Simu_ID
      
      # write temp
      write.csv(x = Conds_temp, 
                file = paste0(write_results_path, Result_ID, ".csv"), 
                row.names = F)
      
      Conds_full <- rbind(Conds_full, Conds_temp)
    }
    )
  }
}
```

Collect all results

```{r}
list_results  <- list.files("./Results/MECHA_results/")
MECHA_results <- tibble()

for(i in list_results){
  results_temp <- read.csv(file = paste0("./Results/MECHA_results/", i))
  MECHA_results <- rbind(MECHA_results, results_temp)
}

write.csv(x = MECHA_results, file = "./Results/MECHA_results.csv", row.names = F)
```

Simple preview

```{r}
MECHA_results <- read.csv("./Results/MECHA_results.csv")

data2plot <- MECHA_results %>% 
  left_join(Anatomy_Full, by = "CS_id") %>% 
  # filter(kAQP == 4e-4) %>% 
  filter(Barrier %in% c("b1", "b9", "b6"))

ggplot(data2plot, 
       aes(x = age, 
           y = kr, 
           color = Barrier)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~kAQP) +
  theme_few()
```


