---
title: "TROOT_GRANAR-MECHA"
author: "Marco D'Agostino"
format: html
editor: source
editor_options: 
  chunk_output_type: inline
---

# INTRODUCTION

This notebook contains the code workflow to load quantified anatomy data, run GRANAR and run MECHA.\

```{r, include=F}
options(rstudio.help.showDataPreview = FALSE)
rm(list = ls())

# SET LOCATION
path_MECHA <- "./src/MECHA/"

# LOAD FUNCTIONS
TRoot_path <- "src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path, pattern = ".R")) {
  print(i)
  source(paste0(TRoot_path, i))
}

#LOAD PACKAGES
pkg_list <- c("fmsb", 
              "packcircles", 
              "pander", 
              "readxl", 
              "visreg", 
              "EnvStats", 
              "factoextra", 
              "data.table",
              "reticulate", 
              "xml2", 
              "tidyverse", 
              "deldir", 
              "viridis", 
              "Hmisc", 
              "devtools", 
              "ggplot2",
              "gridExtra", 
              "dplyr", 
              "cowplot", 
              "stats", 
              "emmeans", 
              "corrplot", 
              "sf", 
              "SciViews")

for(pk in pkg_list) {
  try(library(pk, character.only = T))
}

library(ggthemes)

# LOAD GRANAR FUNCTIONS
GRANAR_path <- "C:/Users/mdagostino/Desktop/GITHUB/granar/R/" # change with your directory
GRANAR_path <- "../granar/R/" # change with your directory
for (i in list.files(GRANAR_path, pattern = ".R")) {
  print(i)
  source(paste0(GRANAR_path, i))
}

# source("Data_preparation.R")

Plants         <- read.csv("Data/Anatomy/Plants.csv")
Segments       <- read.csv("Data/Anatomy/Segments.csv")
CrossSections  <- read.csv("Data/Anatomy/CrossSections.csv")
anatomy1       <- read.csv("Data/Anatomy/anatomy1.csv")
anatomy2       <- read.csv("Data/Anatomy/anatomy2.csv")
Parameters     <- read.csv("Data/Anatomy/Parameters.csv")
Anatomy_Full   <- read.csv("Data/Anatomy/Anatomy_Full.csv")
Barriers_Types <- read_xlsx("Data/Barriers_Types.xlsx")

date           <- Sys.Date()

# Correct units in Parameters
Parameters$units[Parameters$param_id == "xylem_max_size" | Parameters$param_id == "xylem_cell_diameter"] <- "mm"

# Set conversion factors from cm HPa-1 d-1 to m MPa-1 s-1
kr.conv <- 1.1574e-3
kx.conv <- 1.1574e-9
```

# \[don't run\] Process Anatomical Data

We quantified 40+ root cross sections of tomato from microscope pictures.\
These quantifications are in *Data/Quantifications/* folder, in the form of .XSLX files.\
We run the script *Data_preparation.R* in *./src¨* to convert these XLSX file into single tables.\
NB : Metadata files are required :\
- *Plants* contains IDs, ages and lengths of each roots\
- *Segments* contains informations about segments of each root\
- *CrossSections* contains IDs and informations about each cross section\
The script in *Data_preparation.R* creates

Here we load an convert quantification data (in the form of *xlsx* files in *Data/Quantifications* folder) into GRANAR parameters (params). The params will be stored both into single *xml* files (in the folder *Params*) directly usible into GRANAR, and into the big table Anatomy2. The file *Data_Preparation.R* automatically load and treat data from *Data/Quantifications*.

- *anatomy1* contains all quantifiation data
- *anatomy2* contains all values of all GRANAR params for each cross section
- *Parameters* contains information about the measured and GRANAR params

```{r}
# source("./src/Data_preparation.R")
```

```{r}
# All anatomical data in standard table ; Create Anatomy_Full.csv

Anatomy_Full <- anatomy2 %>%
  spread(key = param_id, value = value) %>%
  left_join(CrossSections, by = "CS_id") %>%
  mutate(radius =
           cortex_cell_diameter * cortex_n_layers +
           endodermis_cell_diameter * endodermis_n_layers +
           epidermis_cell_diameter * epidermis_n_layers +
           exodermis_cell_diameter * exodermis_n_layers +
           stele_layer_diameter/2
           )

write.csv(Anatomy_Full, "Data/Anatomy/Anatomy_Full.csv", row.names = F)
```

# 0) Analysis of quantifications

This part load and analyse the cross section quantifications.

First let's have a look at metadata.

So we had

## Root lengths

```{r}
head(Plants)

Plants$days2 <- as.factor(Plants$days)

# LENGTHS
ggplot(data = Plants, aes(color = days2)) +
  geom_point(aes(x = days2, y = length)) +
  geom_boxplot(aes(x = days2, y = length)) + 
  # facet_wrap(~days) +
  theme_bw() +
  ggtitle("Root length (cm")

#GROWTH RATE
ggplot(data = Plants, aes(color = days2)) +
  geom_point(aes(x = days2, y = growth_rate)) +
  geom_boxplot(aes(x = days2, y = growth_rate)) +
  theme_bw() +
  ggtitle("Growth rate (cm/d)")
```

## Visualization of data per param

*anatomy2* contains quantified anatomical traits for 43 cross-sections

```{r}
summary(anatomy2)

data2plot <- anatomy2 %>% 
  left_join(Parameters[c("name", "type", "param_id", "units")], by = "param_id") %>% 
  left_join(CrossSections[c("CS_id", "age", "plant_id")], by = "CS_id") %>% 
  mutate(Title = paste0(name, " ", type, " [", units, "]"))

cols <- c(
  "cortex_cell_diameter",
  "cortex_n_layers", 
  "endodermis_cell_diameter", 
  "epidermis_cell_diameter",
  "exodermis_cell_diameter",
  "pericycle_cell_diameter",
  "phloem_cell_diameter",
  "phloem_n_layers",
  "phloem_proportion",
  # "secondarygrowth_param",
  "stele_cell_diameter",
  "stele_layer_diameter",
  "stele_n_layers",
  "stele_SD",
  "xylem_cell_diameter",
  "xylem_max_size",
  "xylem_n_cells"
  )

p <- ggplot(data = data2plot %>% filter(param_id %in% cols)) +
  geom_point(aes(x = age, y = value, color = plant_id)) +
  facet_wrap(~Title, 
             scales = "free",
             ncol = 4) +
  theme_few() +
  theme(
    legend.position = "right"
  ) +
  theme(strip.text = element_text(size = 8))

p
ggsave(filename = "plots/Anatomy/Anatomy_Quantifications.svg", 
       plot = p, width = 10, height = 7, units = "in",
       device = "svg")
```

Plot all individual quantified traits in *plots/anatomical_measurements/*

```{r}
# param_id_i <- cols[5]

for(i in seq(1, length(cols))){
  
  param_id_i <- cols[i]
  title_i <- unique(data2plot$Title[data2plot$param_id == param_id_i])
  2
  p_temp <- ggplot(data = data2plot %>% filter(param_id == param_id_i)) +
    geom_point(aes(x = age, y = value)) +
    # facet_wrap(~Title, scales = "free", ncol = 4) +
    ggtitle(title_i) +
      
    theme_few() +
    theme(
      legend.position = "right"
    ) +
    theme(plot.title = element_text(size=9))

  ggsave(filename = paste0("plots/Anatomy/measurements/", param_id_i, ".svg"), 
         plot = p_temp, width = 2.5, height = 2.5, units = "in",
         device = "svg")
}
```

## Secondary Growth

Secondary Growth was monitored as binary (0 = primary growth, 1 = secondary growth). Note that the *intermediate* phase is classified as secondary growth.

```{r}
SG_data <- anatomy2 %>% 
  filter(param_id == "secondarygrowth_param") %>% 
  left_join(CrossSections[c("CS_id", "age", "plant_id")], by = "CS_id")

# SG_data$value <- as.factor(SG_data$value)

p <- ggplot(data = SG_data) +
  geom_jitter(aes(x = age, y = value),
              color = "grey1",
              height = 0.01,
              width = 0,
              alpha = 0.75) +
  stat_smooth(aes(x = age, y = value), 
              color = "red", linetype = 2,
              method = "glm",
              method.args=list(family="binomial")) +
  ylab("SG presence") +
  theme_few()

p
ggsave(filename = "plots/Anatomy/SG_probability.svg", 
       plot = p, width = 3, height = 2, units = "in",
       device = "svg")
```

## Radius

Here we see that radius can be approximated as constant till 25 days, at 0.199 mm. Then, after 25 days, it can be approximated using : $r = exp(-7.59 + 0.23x)$

```{r}
radius_data <- Anatomy_Full[c("radius", "age")]

# Set secondary growth treshold
treshold    <- 25

# Linear model 1
radius_lm1  <- lm(data = radius_data %>%
                    filter(age < treshold), 
                  formula = radius ~ 1)

summary(radius_lm1)
mrad        <- radius_lm1$coefficients[1]

# Linear model 2
radius_lm2  <- lm(data = radius_data %>%
                    filter(age >= treshold), 
                  formula = ln(radius) ~ age)
summary(radius_lm2)

# Extract parameters from lm2
alpha       <- radius_lm2$coefficients[1]
beta        <- radius_lm2$coefficients[2]

# Create an dataframe to store the regression
pred1 <- predict(object  = radius_lm1, 
                 newdata = data.frame(age = seq(1, treshold),
                                      radius = 1), 
                 interval = "confidence")

pred1_df <- data.frame(age      = seq(1, treshold),
                       radius   = pred1[,"fit"],
                       lower_ci = pred1[, "lwr"],
                       upper_ci = pred1[, "upr"])

pred2 <- exp(predict(object  = radius_lm2, 
                 newdata = data.frame(age = seq(treshold, 30),
                                      radius = 1), 
                 interval = "confidence")
             )

pred2_df <- data.frame(age      = seq(treshold, 30),
                       radius   = pred2[, "fit"],
                       lower_ci = pred2[, "lwr"],
                       upper_ci = pred2[, "upr"])

radius_pred <- rbind(pred1_df, pred2_df)
```

```{r}
radius_plot <- ggplot() +
  
  geom_ribbon(data = radius_pred,
              aes(x = age, ymin = lower_ci, ymax = upper_ci),
              fill = "orange", 
              alpha = 0.5,
              ) +
  
  geom_point(data = radius_data, 
             aes(x = age, y = radius), 
             size = 1) + 
  
  geom_line(data = radius_pred, 
            aes(x = age, y = radius), 
            linetype = 2, 
            color = "red", linewidth = 1.2) +
  
  xlab("Age [d]") +
  ylab("Radius [mm]") +
  theme_bw()

radius_plot
svg("Plots/Anatomy/Radius_Plot.svg", width = 3, height = 2)
radius_plot
dev.off()
```

## Hydrophobic barriers

```{r}
HB_data <- read_xlsx("./Data/Barriers_Timings.xlsx") %>% 
  mutate(Exo = factor(Exo, levels = c("none", "Suberin (patchy)", "Suberin (complete)", "Lignin Cap")))

p <- ggplot(HB_data) +
  geom_point(aes(x = Staining, y = age, color = Exo, shape = Exo), size = 3) +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "right")
p

svg(filename = paste0("./plots/BarriersTiming.svg"), width = 4, height = 2)
p
dev.off()
```

In Canto-Pastor 2024, suberin appears at :
  * patchy : 35+-5    % of root length -> 2.45+-0.35 d
  * full   : 63+-11.5 % of root length -> 4.41+-0.80 d
  
In Manzano 2025 :
  * lignin start at 0.4 cm from the root tip
  * fully recover epidermal frontier at 2 cm
  * full recover of epi frontier + CS at 8 cm

## Correlations

```{r}
prm <- c("cortex_n_layers", 
         "endodermis_cell_diameter", 
         "exodermis_cell_diameter",
         "pericycle_cell_diameter",
         "phloem_cell_diameter",
         "phloem_n_layers",
         "phloem_proportion",
         "stele_cell_diameter",
         "stele_layer_diameter",
         "stele_n_layers",
         "stele_SD",
         "xylem_cell_diameter",
         "xylem_max_size",
         "xylem_n_cells",
         "radius",
         "age")

svg(filename = "plots/Anatomy/Anatomy_Correlations.svg", width = 6, height = 6)
pcor <- corrplot(cor(Anatomy_Full[prm]), 
                 method = "color",
                 # type = "upper"
                 diag = F,
                 )
dev.off()
```

## Apoplastic Barriers

```{r}
Barriers_Timing <- read_xlsx("./Data/Barriers_Timings.xlsx") %>%
  separate(CS_id, into = c("plant_id", "segment", "coloration", "cut", "zoom", "repetition"), sep = "_") %>% 
  gather(Endo, Exo, key = "tissue", value = "barrier")
  

ggplot(Barriers_Timing) +
  geom_point(aes(x = age, y = barrier, color = tissue)) +
  theme_few()
```

## Parameter regressions

Generate individual regressions

```{r}
source("src/FUNCTIONS/T-Root/Functions_Misc.R")
source("src/Regressions_Auto.R")
```

```{r}
data2plot <- reg_data %>% 
  filter(param_id != "stele_SD") %>% 
  left_join(Parameters, by = "param_id") %>% 
  mutate(plot_title = paste(name, "|", type, " [", units, "]"))

p <- ggplot(data2plot) +
  geom_ribbon(aes(x = age, ymax = reg+sd, ymin = reg-sd),
              fill = "orange", alpha = 0.5) +
  geom_point(aes(x = age, y = value)) +
  geom_line(aes(x = age, y = reg), 
            color ="red", linetype = 2
             ) +
  
  xlab("Age [d]") +
  facet_wrap(~plot_title, scales = "free") +
  theme_few() +
  theme(strip.text = element_text(size = 9))

ggsave(filename = "./plots/Regressions.svg", plot = p, 
       device = "svg", width = 10, height = 9)

ggsave(filename = "./plots/Regressions.png", plot = p, 
       device = "png", width = 10, height = 9)

p
```

# 1) GRANAR

GRANAR is the generator of root anatomy in R (Heymans 2020).

Run the following chunks to checks if all is good with GRANAR.\
Examples of parameter files are in \*/Params/.

## Load params

```{r}
# xml <- "Params/examples/B73_taproot_2021.xml"
xml <- "src/Params/B04_B_To_C01_Z20_01.xml"

param1 <- read_param_xml(xml)

# Modify some parameters
# param1$value[param1$name == "secondarygrowth" & param1$type == "param"]   <- 1
# param1$value[param1$name == "phloem" & param1$type == "n_layers"]         <- 0
param1$value[param1$name == "param" & param1$type == "randomness"]          <- 0
# param1$value[param1$name == "cortex" & param1$type == "n_layers"]         <- 1
# param1$value[param1$name == "cortex" & param1$type == "cell_diameter"]    <- 0.005
# param1$value[param1$name == "epidermis" & param1$type == "cell_diameter"] <- 0.005
# param1$value[param1$name == "exodermis" & param1$type == "cell_diameter"] <- 0.005
```

## Play with GRANAR

```{r, warning=F}
# PRIMARY GROWTH
sim1 <- create_anatomy(parameters = param1, verbatim = F)

# svg("test.svg")
plot_anatomy(sim1)
# dev.off()
```

### Run GRANAR for all data

And store anatomies in Anatomies/data/

```{r, include=F, eval=F}
path <- "Data/Virtual Anatomies/"
param_list <- list.files("src/Params/", pattern = ".xml")

for(param_i in param_list){
  print(param_i)
  param_temp <- read_param_xml(paste0("src/Params/",param_i))
  try(expr = {
      sim_temp <- create_anatomy(parameters = param_temp, verbatim = F)
      write_anatomy_xml(sim = sim_temp, path = paste0(path, param_i))
      
      p <- plot_anatomy(sim_temp)
      ggsave(filename = paste0(path, strsplit(param_i, ".xml")[[1]], ".svg")
             ,plot = p
             ,device = "svg"
             ,width = 5, height = 5
             ) 
    }
  )
}
```

# 2) MECHA

## Presentation and Installation

MECHA is the solver of local conductivities (Couvreur 2018)

Set up steps to run it in local :

1.  Open **ANACONDA NAVIGATOR**

2.  Create a new environment with **python 3.7** (in this work it is called "**MECHA2**")\
    `conda create -n MECHA2 python=3.7`

3.  Open the console of this environment and enter the following :\
    `conda install numpy`\
    `conda install scipy`\
    `conda install matplotlib`\
    `conda install lxml`\
    `conda install pip`\
    `pip install networkx==1.9.1`

4.  Open *MECHAv4_septa_temp_V2.py* and change directories to the current path (in the form "*C:/.../MECHA/"*)

To run MECHA, we first load the root of interest by changing *current_root*. Next we run the MECHA file.

By default, MECHA can simulate different scenarios : \*

- **B0 : No apoplastic barriers**

- **B1 : Endodermal Casparian strip (radial walls)**

- **B2 : Endodermal suberization except at passage cells**

- **B3 : Endodermis full suberization**

- **B4 : Endodermis full suberization and exodermal Casparian strip (radial walls)**

- **B5 : Endo- and exodermal Casparian strips (radial walls)**

- **B6 : Exodermis full suberization and endodermal Casparian strip (radial walls)**

- **B7 : Exodermal Casparian strip (radial walls)**

- **B8 : Endo and exodermal suberization**

- **B9: Lignin Cap and endodermal CS**

Here we choose to compute scenarios 0, 1, 5 and 6. You can change the simulated scenarios in *MECHA/Projects/granar/in/Maize_Geometry.xml* in line 19.

```{r}
# Load a GRANAR anatomy file
anatomy_path <- "Data/Virtual Anatomies/"
anatomy_file <- "P11_D_To_C01_Z20_01.xml"

# Quick look at current_root
test <- get_root_section(paste0(anatomy_path, anatomy_file))
ggplot(test) +
    # geom_polygon(aes_string("x", "y", group="id_cell", fill=col), colour="white") +
    geom_polygon(aes(x = x, y = y, fill = type, group = id_cell),
                 color = "white") +
    theme_classic() +
    coord_fixed() +
    theme(axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank())

# Load MECHA functions
source("./src/MECHA/MECHA_functions.R")

# Upload current anatomy to MECHA folder
MECHA.upload_anatomy(filename = "P11_D_To_C01_Z20_01.xml",
                     filepath = "./Data/Virtual Anatomies/",
                     path_MECHA = "./src/MECHA/")

```

## Test MECHA for one anatomy

```{r}
# LOAD XML AS A BIG LIST
read_path <- "./src/MECHA/Projects/in/"

# Read XML input files as templates
MECHA_inputs_list <- read_MECHA_inputs(read_path,
                                       file_General = "Tomato_General.xml",
                                       file_Hydraulics = "Tomato_Hydraulics.xml",
                                       file_Hormones = "Tomato_Hormones_Carriers.xml",
                                       file_BC = "Tomato_BC.xml",
                                       file_Geometry = "Tomato_Geometry.xml"
                                       ) 

# MODIFY MECHA INPUTS BY HAND
MECHA_inputs_list$General$properties$Output$path        <- "out/"
MECHA_inputs_list$Hydraulics$param$kAQPrange$kAQP$value <- 1.5e-4

MECHA_inputs_list$Hydraulics$param$kw_barrier_range$kw_barrier$Casp <- 1e-10

# WRITE XML's
write_MECHA_inputs(input_list = MECHA_inputs_list, 
                   path = paste0(path_MECHA, "Projects/in/"), 
                   file_General    = "Tomato_General.xml",
                   file_Hydraulics = "Tomato_Hydraulics.xml", 
                   file_Hormones   = "Tomato_Hormones_Carriers.xml",
                   file_BC         = "Tomato_BC.xml",
                   file_Geometry   = "Tomato_Geometry.xml")
```

Launch MECHA

```{r}
library(reticulate)
use_condaenv("GRANAR-MECHA") # choose python environment
sys <- import("sys", convert=T)

# ============================================================================ #
# Clean output file
files <- list.files("./src/MECHA/Projects/out/")
for(f in files){
  unlink(paste0("./src/MECHA/Projects/out/", f))
}

# Run MECHA
py_run_file("src/MECHA/MECHAv4_TRoot.py")
Conds <- MECHA_get_results(output_path = "./src/MECHA/Projects/out/")

ggplot(Conds %>% 
         filter(Barrier %in% c("b1", "b9", "b6")) %>% 
         mutate(Barrier = factor(Barrier, levels = c("b1", "b9", "b6")))) +
  geom_bar(aes(x = Barrier, y = kr), stat = "identity") +
  theme_bw()

```

Visualization (in devlopment)

```{r, eval=FALSE}
rp <- "./src/MECHA/Projects/out/"

# Flux1 <- ApoSymp(paste0(rp,"Macro_prop_1,1.txt")) # En.CS
Flux9 <- ApoSymp(paste0(rp,"Macro_prop_9,9.txt")) # En.CS-Ex.LC
Flux6 <- ApoSymp(paste0(rp,"Macro_prop_6,6.txt")) # En.CS-Ex.Sub

# plot_water_flux(Flux1, apobar = 3)
plot_water_flux(Flux9, apobar = 3)
# plot_water_flux(Flux6, apobar = 3)
```

## Run MECHA for all quantified anatomies

NB : For the main analysis, MECHA was run for 10 values of kAQP (ranging from 1 to 10 x E-4 cm HPa-1 d-1) and for all apoplastic barriers types.

The results of this main analysis are stored in */Results/MECHA_results_1.csv*.

Here we re-run an analysis only for b1, b6 and b9, with varying kAQP and lignin permeability.

The results of this second analysis will be stored in */Results/MECHA_results_2.csv*.

/!\ The definition of apoplastic barriers simulation is done manually in *MECHA/Projects/in/Tomato_Geometry.xml*

We need to run MECHA for :

  - Each GRANAR anatomy
  
  - 3 types of apoplastic barriers deposition (b1, b6 and b9 -> to change manually in Tomato_Geometry.xml!!)

  - 10 values of kAQP (ranging from 1 to 10 e-4 cm HPa-1 d-1)

  - 2 values of kw_lignin : 1e-16 (impermeable) and 4.3e-7 (1 nanometer pores) cm2 HPa-1 d-1

### Define parametric space

```{r, eval= F}
# List files of GRANAR anatomies
Anatomy_list <- list.files(path = "./Data/Virtual Anatomies/", pattern = ".xml")

# Set hydraulic parameters
kAQP_list    <- c(1e-4, 4e-4, 8e-4)  # Elhert et al. (2009) : 4.3e-4 [cm/HPa/d]
kpl_list     <- c(5.3e-12)           # Bret-Harte 1994      : 5.3e-12 [cm^3/hPa/d/plasmodesmata]
kw_lignin    <- c(1e-16, 4.3e-7)

hydro_params  <- expand.grid(kAQP = kAQP_list, kpl  = kpl_list, kw_lignin = kw_lignin)

hydro_params <- hydro_params %>% 
  mutate(Simu_ID = paste0(kAQP, "_", kpl, "_", kw_lignin))
```

### Loop MECHA

```{r, include = F}
library(reticulate)
# use_condaenv("GRANAR-MECHA") # choose python environment
# sys <- import("sys", convert=T)
source("./src/MECHA/MECHA_functions.R")

# Set up
path_MECHA         <- "./src/MECHA/"                       # Path to MECHA folder
read_path          <- paste0(path_MECHA, "Projects/in/")   # Path to MECHA inputs
MECHA_file         <- "MECHAv4_TRoot.py"                   # MECHA file
output_path        <- paste0(path_MECHA, "Projects/out/")  # Path to MECHA outputs
write_results_path <- "./Results/MECHA_results/"           # Path to results

Results_list <- list.files(write_results_path)

# use_condaenv("GRANAR-MECHA") # choose python environment
# sys <- import("sys", convert=T)

# ============================================================================ #
# INITIALIZATION
Conds_full <- tibble()
sim_count  <- 0
sim_tot    <- length(Anatomy_list) * nrow(hydro_params)

# LOOP FOR ANATOMY
for(anatomy in Anatomy_list){
  
  CS_id <- unlist(strsplit(anatomy, split = ".xml"))[1]
  
  # Move anatomy to MECHA folder
  MECHA.upload_anatomy(filename = anatomy,
                       filepath = "./Data/Virtual Anatomies/",
                       path_MECHA = "./src/MECHA/")
  
  # LOOP FOR HYDRAULIC PARAMETERS
  for(i in seq(1, nrow(hydro_params))){
    
    sim_count <- sim_count + 1
    cat("Simulating ", sim_count, "/", sim_tot, "\n")
    
    Simu_ID <- hydro_params$Simu_ID[i]
    kAQP    <- hydro_params$kAQP[i]
    kpl     <- hydro_params$kpl[i]
    kw_lignin <- hydro_params$kw_lignin[i]
    
    # Check if the Result_ID has already been simulated
    Result_ID <- paste0(CS_id, "_", Simu_ID)
    if(paste0(Result_ID, ".csv") %in% Results_list){
      cat("Already simulated, skip to next ... \n")
      next
    }
    
    # ======================== #
    # UPDATE MECHA PARAMS
    # ======================== #
    
    # Load MECHA parameters
    MECHA_inputs_list <- read_MECHA_inputs(
      read_path,
      file_General    = "Tomato_General.xml",
      file_Hydraulics = "Tomato_Hydraulics.xml",
      file_Hormones   = "Tomato_Hormones_Carriers.xml",
      file_BC         = "Tomato_BC.xml",
      file_Geometry   = "Tomato_Geometry.xml"
      ) 
    
    # Modify Inputs
    MECHA_inputs_list$General$properties$Output$path        <- "out/"
    MECHA_inputs_list$Hydraulics$param$kAQPrange$kAQP$value <- kAQP
    MECHA_inputs_list$Hydraulics$param$Kplrange$Kpl$value   <- kpl
    MECHA_inputs_list$Hydraulics$param$kw_barrier_range$kw_barrier$Casp <- kw_lignin
    
    # WRITE XML's
    write_MECHA_inputs(
      input_list = MECHA_inputs_list, 
      path = paste0(path_MECHA, "Projects/in/"), 
      file_General    = "Tomato_General.xml",
      file_Hydraulics = "Tomato_Hydraulics.xml", 
      file_Hormones   = "Tomato_Hormones_Carriers.xml",
      file_BC         = "Tomato_BC.xml",
      file_Geometry   = "Tomato_Geometry.xml"
      )
    
    # ======================== #
    # LAUNCH MECHA
    # ======================== #
    
    # Clean output path
    unlink(output_path, recursive = T)
    dir.create(output_path)
    
    # Unleash MECHA
    try(expr = {
      
      ##################################################
      py_run_file(paste0(path_MECHA, MECHA_file))
      ##################################################
    
      # COLLECT RESULTS
      Conds_temp <- MECHA_get_results(output_path = output_path)
      Conds_temp$CS_id   <- CS_id
      Conds_temp$kAQP    <- kAQP
      Conds_temp$kpl     <- kpl
      Conds_temp$Simu_ID <- Simu_ID
      
      # write temp result file
      write.csv(x = Conds_temp, 
                file = paste0(write_results_path, Result_ID, ".csv"), 
                row.names = F)
      
      # Bind to all results
      Conds_full <- rbind(Conds_full, Conds_temp)
    }
    )
  }
}
```

### Collect and process all results

```{r}
list_results  <- list.files("./Results/MECHA_results/")
MECHA_results <- tibble()

for(i in list_results){
  results_temp <- read.csv(file = paste0("./Results/MECHA_results/", i))
  MECHA_results <- rbind(MECHA_results, results_temp)
}


MECHA_results <- left_join(MECHA_results, hydro_params) %>% 
  
  # Here we remove scenarios that are not in hydro_params
  # na.omit() %>% 
  
  rename(kx = Kx) %>% 
  
  # Convert kr to m s-1 MPa-1 and kx to m4 s-1 MPa-1
  mutate(perimeter = perimeter*10, # from cm to mm
         kr = kr*kr.conv,
         kx = kx*kx.conv,
         Kr = kr*perimeter,
         kpl = kpl*(1e-6 * 1e4 * (60*60*24)^-1)
         # kAQP = kAQP*kr.conv
         ) %>% 

  # Change barrier names  
  mutate(Barrier_Name = case_when(
    Barrier == "b1" ~ "En.CS",
    Barrier == "b2" ~ "En.Sub*",
    Barrier == "b3" ~ "En.Sub",
    Barrier == "b4" ~ "En.Sub-Ex.CS",
    Barrier == "b5" ~ "En.CS-Ex.CS",
    Barrier == "b6" ~ "En.CS-Ex.Sub",
    Barrier == "b7" ~ "Ex.CS",
    Barrier == "b8" ~ "En.Sub-Ex.Sub",
    Barrier == "b9" ~ "En.CS-Ex.LC"
  )) 
  

write.csv(x = MECHA_results, file = "./Results/MECHA_results_2.csv", row.names = F)
```

## Analyse Results

Simple preview

```{r}
color_scale <- c("En.CS" = "black", 
                 "En.CS-Ex.LC" = "#C71AB7", 
                 "En.CS-Ex.Sub" = "#4E3CA5")

MECHA_results <- read.csv("./Results/MECHA_results_2.csv") %>% 
  mutate(Barrier_Name = factor(Barrier_Name, levels = c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub"))) %>% 
  mutate(kw_lignin = as.factor(kw_lignin))  

data2plot <- MECHA_results %>% 
  left_join(Anatomy_Full, by = "CS_id")

p1 <- ggplot(data2plot, 
       aes(x = age, 
           y = kr*1e7, 
           color = kw_lignin)) +
  geom_point() +
  geom_smooth() +
  facet_grid(kAQP~Barrier_Name) +
  theme_bw()

p1
ggsave(filename = "./plots/MECHA/MECHA_lignin_comparison_1.png",plot = p1
       ,device = "png", width = 5, height = 4)

```

```{r}
data2stat <- MECHA_results %>% 
  select(c("CS_id", "kr", "kw_lignin", "kAQP", "Barrier_Name")) %>% 
  mutate(ln_p = case_when(kw_lignin == 1e-16 ~ "imper.",
                          kw_lignin == 4.3e-7 ~ "per.")
         ) %>% 
  select(-c(kw_lignin)) %>% 
  mutate(kAQP = as.factor(kAQP*1e4))

p <- ggplot(data2stat) +
  geom_violin(aes(x = ln_p, y = kr, fill = Barrier_Name, color = Barrier_Name), 
              alpha = 0.2, width = 0.7) +
  geom_boxplot(aes(x = ln_p, y = kr, fill = Barrier_Name), 
               alpha = 0.2, width = 0.7) +
  # geom_jitter(aes(x = ln_p, y = kr, color = Barrier_Name, shape = ln_p), width = 0.1) +
  facet_wrap(~kAQP, nrow = 1) +
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  theme_clean()  +
  theme(axis.text.x = element_text(angle = 90))
p

ggsave(filename = "./plots/MECHA/MECHA_lignin_comparison_2.png",plot = p
       ,device = "png", width = 7, height = 3)
```

Stats 

```{r}
data2stat2 <- data2stat %>% filter(kAQP == 4) 
kw_lignin_lm <- lm(data2stat2
                  ,formula = kr ~ Barrier_Name * ln_p)

par(mfrow = c(2, 2))
plot(kw_lignin_lm)
```


```{r}
summary(kw_lignin_lm)
cat("###################################### \n")
anova(kw_lignin_lm)
cat("###################################### \n")
EM <- emmeans(kw_lignin_lm, ~ Barrier_Name | ln_p)
print(EM)

Means <- as_tibble(EM)
mean1 <- Means$emmean[Means$Barrier_Name == "En.CS" & Means$ln_p == "per."]
mean2 <- Means$emmean[Means$Barrier_Name == "En.CS-Ex.LC" & Means$ln_p == "per."]
mean3 <- Means$emmean[Means$Barrier_Name == "En.CS-Ex.Sub" & Means$ln_p == "per."]

cat("Difference between En.CS and En.CS-Ex.LC :", round((mean2-mean1)*100/mean1, digits = 2), "% \n")
cat("Difference between En.CS-Ex.LC and En.CS-Ex.Sub :", round((mean3-mean2)*100/mean2, digits = 2), "% \n")
cat("Difference between En.CS and En.CS-Ex.Sub :", round((mean3-mean1)*100/mean1, digits = 2), "% \n")

contrast(EM, method = "pairwise")
```

Violin Plot

```{r}
data2plot <- MECHA_results %>% 
  filter(kAQP == 4e-4 & kw_lignin == 4.3e-7) %>% 
  
  mutate(Endodermis = recode(Barrier_Name,
                             "En.CS"         = "Endodermal CS",
                             "En.CS-Ex.LC"   = "Endodermal CS",
                             "En.CS-Ex.Sub"  = "Endodermal CS",
                             "En.Sub"        = "Endodermal Sub",
                             "En.Sub-Ex.CS"  = "Endodermal Sub",
                             "En.Sub-Ex.Sub" = "Endodermal Sub")
         ) %>% 
  mutate(Exodermis = recode(Barrier_Name,
                             "En.CS"         = "none",
                             "En.CS-Ex.LC"   = "LC",
                             "En.CS-Ex.Sub"  = "Sub",
                             "En.Sub"        = "none",
                             "En.Sub-Ex.CS"  = "LC",
                             "En.Sub-Ex.Sub" = "Sub")
         ) %>% 
  mutate(kr = kr*1e8)
  

p_Barriers <- ggplot(data = data2plot, 
                     aes(x = Exodermis, 
                         y = kr)
                     ) +
  
  # # ADD VIOLINS
  geom_violin(aes(fill  = Barrier_Name, color = Barrier_Name),
              # fill  = "lightgrey",
              # color = "white",
              alpha = 0.2) +
  
  # ADD POINTS
  geom_jitter(aes(x = Exodermis, 
                  y = kr,
                  color = Barrier_Name)
              ,width = 0.1
              ,size = 1
              ) +
  
  facet_wrap(~Endodermis, scales = "free") +
  
  # CUSTOM LABELS
  xlab("Exodermis") +
  ylab(expression(k[r] ~ "[" ~ 10^{-08} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  ylim(1, 20) +
  
  # OTHER PARAMS
  # scale_fill_manual(values=c("white","white","white", "grey", "grey", "grey")) +
  # scale_color_viridis() +
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  
  theme_few() +
  theme(legend.position = "none"
        ,axis.line = element_line()
        ,panel.border = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90))

p_Barriers

svg(filename = "plots/MECHA/MECHA_Barriers_comparison.svg", width = 2, height = 4)
p_Barriers
dev.off()
```

