---
title: "RESULTS ANALYSIS"
format: html
editor: source
editor_options: 
  chunk_output_type: inline
---

```{r Load Packages, include=F}
DIR_path <- getwd()
options(rstudio.help.showDataPreview = FALSE)
rm(list = ls())

TRoot_path <- "src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path)) {
  print(i)
  source(paste0(TRoot_path, i))
}

libs <- c("pander", "readxl", "EnvStats", 
          "FactoMineR", "factoextra", 
          "data.table", "reticulate", 
          "dplyr", "tidyverse", 
          "xml2", 
          "viridis", "Hmisc", "ggplot2", 
          "gridExtra", "Matrix", "emmeans", 
          "ggthemes", "SciViews")

for(pk in libs) {
  library(pk, character.only = T)   
}

simu_path <- "Results/12-01-2023/"
```

# Load Results from MECHA

* kr and kAQP are converted from $cm d^{-1} HPa^{-1}$ to $m s^{-1} MPa^{-1}$

* kpl is converted from $cm^3/hPa/d/plasmodesmata$ to $m^{3} s^{-1} MPa^{-1} pd^{-1}$

* kx  is converted from $cm^{4} d^{-1} HPa^{-1}$   to $m^{3} s^{-1} MPa^{-1}$

```{r}
kr.conv <- 1.1574e-3
kx.conv <- 1.1574e-9

MECHA_results  <- read.csv("./Results/MECHA_results.csv")
Anatomy_Full   <- read.csv("Data/Anatomy/Anatomy_Full.csv")
anatomy2       <- read.csv("Data/Anatomy/anatomy2.csv")
Parameters     <- read_xlsx("Data/Parameters.xlsx")

# Convert kr to m s-1 MPa-1 and kx to m4 s-1 MPa-1
MECHA_results <- MECHA_results %>% 
  rename(kx = Kx) %>% 
  mutate(perimeter = perimeter*10, # from cm to mm
         kr = kr*kr.conv,
         kx = kx*kx.conv,
         Kr = kr*perimeter,
         kpl = kpl*(1e-6 * 1e4 * (60*60*24)^-1)
         # kAQP = kAQP*kr.conv
         )

# Change barrier names
MECHA_results$Barrier_Name <- NaN
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b1"] <- "En.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b2"] <- "En.Sub*"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b3"] <- "En.Sub"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b4"] <- "En.Sub-Ex.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b5"] <- "En.CS-Ex.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b6"] <- "En.CS-Ex.Sub"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b7"] <- "Ex.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b8"] <- "En.Sub-Ex.Sub"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b9"] <- "En.CS-Ex.LC"
```

# DESCRIPTIVE AND PLOTS OF QUANTIFIED DATA

Here we analyse the results of conductivities computed on quantified cross-sections.

## - Plot kr vs each anatomical trait

```{r}
# data2plot <- MECHA_results %>% 
#   filter(Barrier_Name %in% c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub")) 
# 
cols <- c(
  "cortex_cell_diameter",
  "cortex_n_layers",
  "endodermis_cell_diameter",
  "epidermis_cell_diameter",
  "exodermis_cell_diameter",
  "pericycle_cell_diameter",
  "phloem_cell_diameter",
  "phloem_n_layers",
  "phloem_proportion",
  "secondarygrowth_param",
  "stele_cell_diameter",
  "stele_layer_diameter",
  "stele_n_layers",
  "stele_SD",
  "xylem_cell_diameter",
  "xylem_max_size",
  "xylem_n_cells"
  )

plist <- Parameters %>% 
  filter(param_id %in% cols)
plist <- plist$param_id

data2plot <- MECHA_results[c("CS_id", "kr", "kAQP", "Barrier_Name")] %>% 
  filter(kAQP == 4e-4) %>% 
  select(-kAQP) %>% 
  filter(Barrier_Name %in% c("En.CS")) %>% 
  left_join(Anatomy_Full[c("CS_id", plist, "radius", "age")], by = "CS_id") %>% 
  select(-c("CS_id")) %>% 
  gather(c(all_of(plist), "radius", "age"), key = "Variable", value = "Value")

color_scale <- c("En.CS" = "black", 
                 "En.CS-Ex.LC" = "#C71AB7", 
                 "En.CS-Ex.Sub" = "#4E3CA5")

p <- ggplot(data2plot,
       aes(x = Value, y = kr, color = Barrier_Name)) +
  
  # geom_line(aes(x = age, y = Kr, group = plant_id)) +
  
  geom_point(alpha = 1, size = 0.5) +
  # geom_smooth(method = "loess", span = 1) +
  scale_color_manual(values = color_scale) +
  facet_wrap(~Variable, scales = "free", nrow = 3) +
  theme_few() +
  theme(axis.text.x = 
          element_text(angle = 90, hjust = 1, vjust = 0.5))

p
ggsave(filename = "plots/kr_vs_anatomy.png", plot = p,
       device = "png", width = 15, height = 8, dpi = 200)
```


## - Radial conductivity & conductance at fixed kAQP

```{r}
color_scale <- c("En.CS"        = "black", 
                 "En.CS-Ex.LC"  = "#C71AB7", 
                 "En.CS-Ex.Sub" = "#4E3CA5")

data2plot <- MECHA_results %>% 
  filter(kAQP == 4e-4) %>%
  filter(Barrier_Name %in% c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub")) %>% 
  # mutate(kr = kr*1e8,
  #        Kr = Kr*1e9) %>% 
  left_join(Anatomy_Full, by = "CS_id") %>% 
  select(c("Barrier_Name", "age", "kr", "Kr", "kAQP")) %>% 
  gather(kr, Kr, key = "Variable", value = "Value") 
  
# ============================================================================ #

p_RadialConds <- ggplot(data2plot) +
  geom_point(aes(x = age, 
                 y = Value,
                 color = Barrier_Name)) +
  
  geom_smooth(aes(x = age, 
                  y = Value,
                  color = Barrier_Name,
                  fill = Barrier_Name
                  ), 
              # color = "black",
              alpha = 0.1,
              span = 1) +
  
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  
  xlab("Age [d]") +
  # ylab(expression(K[r] ~ "[" ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  facet_wrap(~Variable, scales = "free") +
  # facet_grid(Variable~kAQP) +
  
  theme_few() +
  theme(legend.position = "bottom") 

# ============================================================================ #
p_RadialConds
# svg(filename = "plots/MECHA_results_kr-Kr_all-kAQP.svg", width = 12, height = 6)
# p_RadialConds
# dev.off()

svg(filename = "plots/MECHA_results_kr-Kr.svg", width = 6, height = 4)
p_RadialConds
dev.off()
```

## - Axial conductance

```{r}
# Select data for only one Barrier (they all have the same values anyway)
data2plot <- MECHA_results %>% 
  filter(Barrier == "b1" & kAQP == 1e-4) %>% 
  select(c("CS_id", "kx")) %>% 
  left_join(Anatomy_Full[c("CS_id", "age")], by = "CS_id") %>% 
  mutate(kx_ln = ln(kx))

kx_plot <- ggplot(data2plot) +

  geom_point(aes(x = age,
                 y = kx)) +
  
  geom_smooth(aes(x = age, y = kx),
              # span = 1,
              method = "lm",
              se = F) +
  
  xlab("Age [d]") +
  ylab(expression(k[x] ~ "[" ~ m^{4} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  scale_y_continuous(trans = 'log10') +
  
  theme_few()

# =========================================================================== #
kx_plot

svg(filename = "plots/MECHA_results_kx.svg", width = 3, height = 3)
kx_plot
dev.off()

# ggsave(filename = "plots/data_kx_plot.svg", plot = kx_plot, device = "svg", width = 3, height = 3)
```


## - Important anatomical parameters

```{r}
variables <- c("xylem_cell_diameter", 
               "xylem_n_cells", 
               "stele_layer_diameter", 
               "cortex_n_layers", 
               "phloem_n_layers", 
               "radius")

data2plot <- unique(MECHA_results[c("CS_id", "kx")]) %>% 
  left_join(Anatomy_Full, by = "CS_id") %>% 
  select(c("age", variables)) %>% 
  gather(variables,
         key = "Variable", value = "Value")

Anatomy_plot <- ggplot(data2plot) +
  
  geom_point(aes(x = age, y = Value)) +
  geom_smooth(aes(x = age, y = Value),
              span = 1, se = T) +
  
  facet_wrap(~Variable, scales = "free") +
  theme_few()
Anatomy_plot

svg(filename = "plots/Anatomy_important_traits.svg", width = 5, height = 4)
Anatomy_plot
dev.off()

ggsave(filename = "plots/Anatomy_important_traits.png", plot = Anatomy_plot, 
       device = "png", width = 6, height = 4, dpi = 300)
```

## - Secondary growth

```{r}
data2plot <- Anatomy_Full %>% 
  select("age", "secondarygrowth_param")

ggplot(data2plot, aes(x = age, y = secondarygrowth_param)) +
  geom_point() +
  geom_smooth_logistic
```

## - Analyse corelations between kr and anatomical measurements

```{r}
plist <- Parameters %>%
  filter(param_id %in% colnames(Anatomy_Full))
plist <- plist$param_id
print(plist)
plist <- c(
           # "aerenchyma_proportion", 
           # "aerenchyma_n_files",    
           "xylem_max_size",
           "xylem_cell_diameter",
           # "xylem_n_files",
           "xylem_n_cells",
           "stele_cell_diameter",
           "stele_SD",
           "stele_layer_diameter", 
           "phloem_n_layers", 
           "phloem_cell_diameter",  
           "phloem_proportion",    
           "pericycle_cell_diameter",
           # "pericycle_n_layers",    
           "endodermis_cell_diameter", 
           # "endodermis_n_layers",   
           "cortex_cell_diameter",  
           "cortex_n_layers",
           "exodermis_cell_diameter",
           # "exodermis_n_layers",    
           "epidermis_cell_diameter"
           # "epidermis_n_layers"
           )

data2stat <- MECHA_results %>%
  select(c("CS_id", "kr", "kx", "Barrier_Name", "kAQP")) %>% 
  filter(Barrier_Name == "En.CS" & kAQP == 4e-4) %>% 
  left_join(Anatomy_Full[c("CS_id", plist, "radius", "age")], by = "CS_id") %>% 
  select(-c("CS_id"))

```


```{r}
library(corrplot)

# Print correlations
kr_corr <- data2stat %>%
  select(-kr, -kAQP, -Barrier_Name) %>%
  sapply(function(x) cor(x, data2stat$kr, use = "complete.obs", method = "pearson")) %>% 
  as.data.frame()

# Add cortex layer length
data2stat <- data2stat %>% 
  mutate(cortex_layer_diameter = cortex_n_layers*cortex_cell_diameter) %>% 
  select(-kAQP, -Barrier_Name)

svg(filename = "./plots/Correlations.svg", width = 10, height = 10)
p <- corrplot(cor(data2stat, method = "pearson"), method = "number")
dev.off()
```

# STATISTICAL ANALYSIS

## - Radius

```{r}
radius_mean <- mean(Anatomy_Full$radius[Anatomy_Full$age < 25])
radius_sd   <- sd(Anatomy_Full$radius[Anatomy_Full$age < 25])

data2stat <- Anatomy_Full[c("age", "radius")] %>% 
  filter(age >= 25)

ggplot(data2stat) +
  geom_point(aes(x = age, y = radius)) +
  theme_few()

# CHECK NORMALITY
par(mfrow = c(1, 2))
qqnorm(data2stat$radius)
qqline(data2stat$radius)
hist(data2stat$radius)  
shapiro.test(data2stat$radius)

# NORMALIZE WITH BOX-COX
# par(mfrow = c(1))
bc        <- MASS::boxcox(lm(data2stat$radius ~ 1))
lambda_r  <- bc$x[which(bc$y == max(bc$y))]

data2stat$radius_tf <- BoxCox(data2stat$radius, lambda_r)
# data2stat$kr_tf <- log(sqrt(data2stat$kr))

# CHECK NORMALITY
par(mfrow = c(1, 2))
qqnorm(data2stat$radius_tf)
qqline(data2stat$radius_tf)
hist(data2stat$radius_tf)  
shapiro.test(data2stat$radius_tf)

# LINEAR REGRESSION
par(mfrow = c(2,2))
radius_lm <- lm(data = data2stat, formula = radius_tf ~ age)
plot(radius_lm)
summary(radius_lm)

# write radius_lm
saveRDS(object = radius_lm, file = "./Results/radius_model.rds")
```


```{r}
# To have condfidence interval we will do it mannually 

radius_lm <- readRDS("./Results/radius_model.rds")

data2plot <- Anatomy_Full[c("age", "radius")] 

newdata_1 <- data2plot %>% 
  filter(age < 25) %>% 
  mutate(fit = mean(radius),
         lwr = mean(radius) - sd(radius),
         upr = mean(radius) + sd(radius)
         )

newdata_2 <- data2plot %>% 
  filter(age >= 25)

df <- BoxCox_reverse(predict(radius_lm, newdata = newdata_2, interval = 'confidence'),
                            lambda = lambda_r)

newdata_2 <- cbind(newdata_2, df)

data2plot <- rbind(newdata_1, newdata_2)

p <- ggplot(data2plot) +
  
  geom_line(aes(x = age, 
                y = fit),
            linewidth = 2,
            color = "orange") +
  
  geom_ribbon(aes(x = age,
                  ymin = lwr,
                  ymax = upr),
              fill = "orange",
              alpha = 0.2) +
  
  geom_point(aes(x = age, 
                 y = radius)
             # ,color = "blue"
             ) +
  
  ylim(0.1,1.25) +
  
  ylab("Radius [mm]") +
  xlab("Root age [d]") +
  theme_few()

svg(filename = "./plots/Anatomy_Radius.svg", width = 3, height = 3)
p
dev.off()
p

```

## - Radial conductivity

### Prepare data

```{r}
barriers <- c("En.CS", 
              "En.CS-Ex.LC", 
              "En.CS-Ex.Sub", 
              "En.Sub", 
              "En.Sub-Ex.CS", 
              "En.Sub-Ex.Sub")

th <- 3 # Outlier treshold (x)

# Define data
data2stat <- MECHA_results %>% 
  select(c("Barrier_Name", "kr", "kAQP", "CS_id")) %>% 
  left_join(Anatomy_Full[c("CS_id", "age", "radius")], by = "CS_id") %>% 
  mutate(Barrier_Name = as.factor(Barrier_Name)) %>% 
  filter(Barrier_Name %in% barriers) %>% 
  mutate(kr = kr)

# # Remove outliers
# data2stat <- data2stat %>% 
#   group_by(Barrier_Name) %>%
#   mutate(
#     median = median(kr, na.rm = TRUE),
#     mad = mad(kr, na.rm = TRUE),
#     lower_bound = median - th * mad,
#     upper_bound = median + th * mad
#   ) %>%
#   filter(kr >= lower_bound & kr <= upper_bound) %>%
#   select(-median, -mad, -lower_bound, -upper_bound) 

# CHECK NORMALITY
par(mfrow = c(1, 2))
qqnorm(data2stat$kr)
qqline(data2stat$kr)
hist(data2stat$kr)  
shapiro.test(data2stat$kr)

# NORMALIZE WITH BOX-COX
# par(mfrow = c(1))
bc        <- MASS::boxcox(lm(data2stat$kr ~ 1))
lambda_kr <- bc$x[which(bc$y == max(bc$y))]

data2stat$kr_tf <- BoxCox(data2stat$kr, lambda_kr)
# data2stat$kr_tf <- log(sqrt(data2stat$kr))

# CHECK NORMALITY
par(mfrow = c(1, 2))
qqnorm(data2stat$kr_tf)
qqline(data2stat$kr_tf)
hist(data2stat$kr_tf)  
shapiro.test(data2stat$kr_tf)
```

### Advanced plots

```{r}
p <- ggplot(data2stat) +
  
  geom_jitter(aes(x = Barrier_Name, 
                  y = kr*1e8,
                  color = kAQP,
                  size = radius^2), 
              width = 0.25,
              alpha = 0.75
              ) +
  
  # geom_boxplot(aes(x = Barrier_Name,
  #                 y = ))
  
  scale_color_viridis() +
  scale_size_area(
                  max_size = 5) +
  
  ylab(expression(k[r] ~ "[" ~ 10^{-08} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  theme_few() +
  theme(axis.line = element_line()
        ,panel.border = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90))
  
p

ggsave("./plots/MECHA_results_MixedPlot.svg", plot = p,
       device = "svg", width = 5, height = 5)
```

```{r}
data2plot <- data2stat %>% 
  mutate(
    # kr_tf2 = kr_tf,
    # kr_tf2 = 25^-(kr_tf)
  )

p <- ggplot(data2plot,
       aes(x = radius, y = kr_tf
           )
       ) +
  geom_point(aes(shape = Barrier_Name, color = kAQP)) +
  scale_color_viridis() +
  facet_grid(Barrier_Name ~ kAQP) +
  geom_smooth(method = "lm") +
  theme_few()
p
ggsave(filename = "./plots/MECHA_results_FULL_TABLE.svg", plot = p,
       device = "svg", width = 5, height = 5)
```

### Linear Regression

```{r}
lm_kr <- lm(data = data2stat, 
             formula = kr_tf ~ 
               age +
               radius +
               Barrier_Name +
               kAQP +
               kAQP:Barrier_Name
               )

par(mfrow = c(2, 2))
plot(lm_kr)

cat("================= \n  LINEAR MODEL \n=================\n")
summary(lm_kr)
pander(summary(lm_kr))

# cat("================= \n  ANOVA \n=================\n")
# anova(lm_kr)

# Export model 
saveRDS(object = lm_kr, file = "./Results/kr_model.rds")
```

$k_r^* = \beta_0 + \beta_1* $

```{r}
Coef <- lm_kr$coefficients

alpha1 = Coef["(Intercept)"]
beta1  = Coef["age"]
beta2  = Coef["radius"]
beta3  = Coef["kAQP"]

cat("En.CS         : ", alpha1, 
    " + ", beta1, "*age + ", 
    beta2, "*radius + ", 
    beta3, "*kAQP",
    "\n")

cat("En.CS-Ex.LC   : ", alpha1+Coef["Barrier_NameEn.CS-Ex.LC"], " + ", 
    beta1, "*age + ", 
    beta2, "*radius + ", 
    beta3+Coef["Barrier_NameEn.CS-Ex.LC:kAQP"], "*kAQP",
    "\n")

cat("En.CS-Ex.Sub  : ", alpha1+Coef["Barrier_NameEn.CS-Ex.Sub"], " + ", 
    beta1, "*age + ", 
    beta2, "*radius + ", 
    beta3+Coef["Barrier_NameEn.CS-Ex.Sub:kAQP"], "*kAQP",
    "\n")

cat("En.Sub        : ", alpha1+Coef["Barrier_NameEn.Sub"], " + ", 
    beta1, "*age + ", 
    beta2, "*radius + ", 
    beta3+Coef["Barrier_NameEn.Sub"], "*kAQP",
    "\n")

cat("En.Sub-Ex.CS  : ", alpha1+Coef["Barrier_NameEn.Sub-Ex.CS"], " + ", 
    beta1, "*age + ", 
    beta2, "*radius + ", 
    beta3+Coef["Barrier_NameEn.Sub-Ex.CS:kAQP"], "*kAQP",
    "\n")

cat("En.Sub-Ex.Sub : ", alpha1+Coef["Barrier_NameEn.Sub-Ex.Sub"], " + ", 
    beta1, "*age + ", 
    beta2, "*radius + ", 
    beta3+Coef["Barrier_NameEn.Sub-Ex.Sub:kAQP"], "*kAQP",
    "\n")
```

I created a function (in Function_Misc.R) to automatically predict kr.
Prediction analysis

```{r}
lm_kr <- readRDS(file = "./Results/kr_model.rds")

# data2plot <- MECHA_results[c("CS_id", "kr", "Barrier_Name", "kAQP")] %>% 
#   filter(Barrier_Name %in% c("En.CS", "En.")) 
#   left_join(Anatomy_Full[c("CS_id", "age", "radius")], by = "CS_id") %>% 
#   select(-CS_id)
  
# data2stat$kr_pred <- kr_pred(newdata = data2stat, 
#                              lm_kr = lm_kr, 
#                              lambda = lambda_kr)
# 
# # ============================================================================ #
# cat("RMSE : ", sqrt(mean((data2stat$kr - data2stat$kr_pred)^2)))
# # ============================================================================ #
# ggplot(data2stat) +
#   geom_point(aes(x = kr, 
#                  y = kr_pred,
#                  color = kAQP,
#                  size = radius
#                  ),
#              alpha = 0.5) +
#   
#   # geom_smooth(aes(x = kr, 
#   #                 y = kr_pred), 
#   #             method = "loess", 
#   #             color = "red") +
# 
#   coord_fixed(ratio = 1:1) +
#   
#   # xlim(0, 20) +
#   # ylim(0, 20) +
#   
#   geom_abline(linewidth = 1, color = "red") +
#   scale_color_viridis() +
#   
#   # facet_wrap(~kAQP) +
#   
#   xlab("Computed kr") + ylab("Predicted kr") +
#   theme_classic()
```

### Predict and plot

## - Radial conductivity & conductance at fixed kAQP

```{r}
color_scale <- c("En.CS"        = "black", 
                 "En.CS-Ex.LC"  = "#C71AB7", 
                 "En.CS-Ex.Sub" = "#4E3CA5")

data2plot <- MECHA_results %>% 
  filter(kAQP == 4e-4) %>%
  filter(Barrier_Name %in% c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub")) %>% 
  # mutate(kr = kr*1e8,
  #        Kr = Kr*1e9) %>% 
  left_join(Anatomy_Full[c("CS_id", "radius", "age")], by = "CS_id") %>% 
  select(c("Barrier_Name", "age", "kr", "Kr", "kAQP", "radius", "perimeter")) %>% 
  rename("r_data" = "radius") 

# Order by age
data2plot <- data2plot[order(data2plot$age),]

data2plot$radius  <- radius_pred(newdata = data2plot
                                 ,radius_lm = radius_lm
                                 ,radius.mean = radius_mean
                                 ,radius.sd   = radius_sd
                                 ,age.th = 25)

# For this plot we will do mannually to plot CI
kr_pred_df <- BoxCox_reverse(predict(newdata = data2plot, 
                                     lm_kr,
                                     interval = 'prediction'),
                             lambda = lambda_kr)

data2plot <- data2plot %>% 
  cbind(kr_pred_df) %>% 
  rename("kr_pred" = "fit",
         "kr_pred_upr" = "upr",
         "kr_pred_lwr" = "lwr")

data2plot$Kr_pred     <- data2plot$kr_pred*2*3.1415*data2plot$radius
data2plot$Kr_pred_lwr <- data2plot$kr_pred_lwr*2*3.1415*data2plot$radius
data2plot$Kr_pred_upr <- data2plot$kr_pred_upr*2*3.1415*data2plot$radius

# ============================================================================ #
p_kr <- ggplot(data2plot) +
  
  geom_line(aes(x = age
                ,y = kr_pred
                ,color = Barrier_Name
                )
            ,linewidth = 1
            ,linetype = 1
            ,alpha = 1
            ,span = 1
            ) +
  
  geom_ribbon(aes(x = age,
                  ymin = kr_pred_lwr,
                  ymax = kr_pred_upr,
                  fill = Barrier_Name),
              alpha = 0.1) +
  
  geom_point(aes(x = age, 
                 y = kr,
                 color = Barrier_Name)) +
  
  
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  
  xlab("Age [d]") +
  ylab(expression(k[r] ~ "[" ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  # facet_wrap(~Variable, scales = "free") +
  # facet_grid(Variable~kAQP) +
  
  theme_few() +
  theme(legend.position = "none") 
# ============================================================================ #
p_Kr <- ggplot(data2plot) +
  
  geom_line(aes(x = age, 
                y = Kr_pred,
                color = Barrier_Name)
            ,linewidth = 1
            ,linetype = 1
            ,alpha = 1
            ,span = 1
            ) +
  
  geom_ribbon(aes(x = age,
                  ymin = Kr_pred_lwr,
                  ymax = Kr_pred_upr,
                  fill = Barrier_Name),
              alpha = 0.1) +
  
  geom_point(aes(x = age, 
                 y = Kr,
                 color = Barrier_Name)) +
  
  
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  
  xlab("Age [d]") +
  ylab(expression(K[r] ~ "[" ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  # facet_wrap(~Variable, scales = "free") +
  # facet_grid(Variable~kAQP) +
  
  theme_few() +
  theme(legend.position = "none") 
# ============================================================================ #
grid.arrange(p_kr, p_Kr, nrow = 1)
# svg(filename = "plots/MECHA_results_kr-Kr_all-kAQP.svg", width = 12, height = 6)
# p_RadialConds
# dev.off()
# 
svg(filename = "plots/MECHA_results_kr-Kr.svg", width = 6, height = 3)
grid.arrange(p_kr, p_Kr, nrow = 1)
dev.off()
```

## - Axial conductance

At first i tested a ln transformation, but generalised Box-Cox transformation is better, so let's keep it.

```{r}
data2stat <- MECHA_results %>%
  filter(kAQP == 1e-4 & Barrier_Name == "En.CS-Ex.Sub") %>% 
  left_join(Anatomy_Full[c("CS_id", "age", "radius")], by = "CS_id") %>% 
  select("kx", "age", "radius") %>% 
  mutate("kx_ln" = ln(kx))

ggplot(data2stat) +
  geom_point(aes(x = age, y = kx)) +
  theme_few()

# CHECK NORMALITY ON ln TRANSFORMED DATA
par(mfrow = c(1, 2))
qqnorm(data2stat$kx_ln)
qqline(data2stat$kx_ln)
hist(data2stat$kx_ln)  
shapiro.test(data2stat$kx_ln)

# NORMALIZE WITH BOX-COX
bc              <- MASS::boxcox(lm(data2stat$kx ~ 1))
lambda_kx          <- bc$x[which(bc$y == max(bc$y))]
cat("kx lambda : ", lambda_kx, "\n")
data2stat$kx_tf <- BoxCox(data2stat$kx,  lambda_kx)

# RE-CHECK NORMALITY ON BOX-COX TRANSFORMED DATA
par(mfrow = c(1, 2))
qqnorm(data2stat$kx_tf)
qqline(data2stat$kx_tf)
hist(data2stat$kx_tf)  
shapiro.test(data2stat$kx_tf)

# LINEAR REGRESSION
lm_kx <- lm(data    = data2stat, 
             formula = kx_tf ~ radius+age)

par(mfrow = c(2,2))
plot(lm_kx)
pander(summary(lm_kx))
# anova(kx_lm)

saveRDS(object = lm_kx, file = "./Results/kx_model.rds")
```

$$
ln(K_x^*) = \alpha + \beta \cdot radius + \gamma \cdot age
$$

with :

```{r}
cat("alpha = ", lm_kx$coefficients["(Intercept)"], "\n")
cat("beta  = ", lm_kx$coefficients["radius"], "\n")
cat("gamma = ", lm_kx$coefficients["age"], "\n")
```

Test prediction

```{r}
lm_kx <- readRDS("./Results/kx_model.rds")

data2stat$r_data  <- data2stat$radius
data2stat$radius  <- kx_pred(data2stat, lm_kx = lm_kx)
data2stat$kx_pred <- kx_pred(data2stat, lm_kx)

ggplot(data2stat) +
  
  geom_point(aes(x = ln(kx), 
                 y = ln(kx_pred), 
                 color = age
                 )
             ) +
  
  geom_smooth(aes(x = ln(kx),
                  y = ln(kx_pred)
                  ), 
              method = "lm", color = "red") +
  
  coord_fixed() +
  
  # xlim(-26.5, -18) +
  # ylim(-26.5, -18) +
  
  xlab("ln(kx)") + ylab("ln(kx*)") +
  
  # geom_abline() +
  scale_color_viridis() +
  theme_classic()
# ==============================================================================


p_kx <- ggplot(data2stat) +
  
  geom_line(aes(x = age, y = ln(kx_pred)), 
            color = "orange",
            linewidth =2)+
  
  geom_point(aes(x = age, y = ln(kx))) +
  
  ylab(expression(ln(k)[x] ~ "[" ~ m^{4} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  theme_few()

p_kx
svg(filename = "./plots/MECHA_results_Kx.svg", width =3, height = 3)
p_kx
dev.off()
```


# PAIRWISE ANALYSIS OF HYDROPHOBIC BARRIERS

We take here the effect of barriers when kAQP is at mean value

### - Prepare data

```{r}
barriers <- c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub", 
              "En.Sub", "En.Sub-Ex.CS", "En.Sub-Ex.Sub")
th <- 3 # Outlier treshold (x)

# Define data
data2stat <- MECHA_results %>% 
  filter(kAQP == 4e-4) %>% 
  select(c("Barrier_Name", "kr")) %>% 
  mutate(Barrier_Name = as.factor(Barrier_Name)) %>% 
  filter(Barrier_Name %in% barriers)

# Remove outliers
data2stat <- data2stat %>% 
  group_by(Barrier_Name) %>%
  mutate(
    median = median(kr, na.rm = TRUE),
    mad = mad(kr, na.rm = TRUE),
    lower_bound = median - th * mad,
    upper_bound = median + th * mad
  ) %>%
  filter(kr >= lower_bound & kr <= upper_bound) %>%
  select(-median, -mad, -lower_bound, -upper_bound) 
```

### - Check normality

We use Shapiro-Wilk test (Shapiro & Wilk 1963).

```{r}
# FIRST NORMALITY TEST
shapiro.test(data2stat$kr)
ks.test(data2stat$kr, 'pnorm', mean(data2stat$kr), sd(data2stat$kr))
hist(data2stat$kr, breaks = 20)
qqnorm(data2stat$kr)
qqline(data2stat$kr)
```

We see that data is not normal so we apply a Cox-Box transfomation (Box & Cox 1964).

```{r}
#APPLY COX-BOX TRANSFORMATION
bc     <- MASS::boxcox(lm(data2stat$kr ~ 1))
lambda <- bc$x[which(bc$y == max(bc$y))]

data2stat <- data2stat %>% 
  mutate(kr_tf = BoxCox(kr, lambda)) %>% 
  mutate(kr_test = BoxCox_reverse(kr_tf, lambda))

# SECOND NORMALITY CHECK
shapiro.test(data2stat$kr_tf)
ks.test(data2stat$kr_tf, 'pnorm', mean(data2stat$kr_tf), sd(data2stat$kr_tf))
hist(data2stat$kr_tf, breaks = 15)
qqnorm(data2stat$kr_tf)
qqline(data2stat$kr_tf)

# ============================================================================ #
ggplot(data2stat) +
  geom_point(aes(x = Barrier_Name, y = kr_tf)) +
  theme_few()
```

### - ANOVA

Let's try a linear model on transform (normalized) data.

```{r}
Barrier_lm <- lm(data = data2stat, 
                 formula = kr_tf ~ Barrier_Name)

par(mfrow = c(2,2))
plot(Barrier_lm)
# summary(Barrier_lm)
anova(Barrier_lm)
```

### - Post-Hoc Mean Comparison

```{r}
EM <- emmeans(Barrier_lm, specs = pairwise ~ Barrier_Name)

Means <- as_tibble(EM$emmeans)
Contrasts <- as_tibble(EM$contrasts)

Means$emmean_TF <- BoxCox_reverse(Means$emmean, lambda)

```

To develop because we transformed the data !

```{r}
mean_b1 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.CS"], lambda)
mean_b2 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.CS-Ex.LC"], lambda)
mean_b3 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.CS-Ex.Sub"], lambda)
mean_b4 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.Sub"], lambda)
mean_b5 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.Sub-Ex.CS"], lambda)
mean_b6 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.Sub-Ex.Sub"], lambda)

print(paste0("Difference between En.CS and En.CS-Ex.LC [%]         : ", round((mean_b1-mean_b2)*100/mean_b1, digits = 2)))
print(paste0("Difference between En.CS and En.Sub [%]              : ", round((mean_b1-mean_b4)*100/mean_b1, digits = 2)))
```


### - Plot

```{r}
color_scale2 <- c("En.CS"        = "black", 
                  "En.CS-Ex.LC"  = "#C71AB7", 
                  "En.CS-Ex.Sub" = "#4E3CA5",
                  "En.Sub"       = "lightblue4",
                  "En.Sub-Ex.CS" = "lightblue4",
                  "En.Sub-Ex.Sub"= "lightblue4"
                  )

# ============================================================================ #
data2plot <- data2stat %>% 
  mutate(Endodermis = recode(Barrier_Name,
                             "En.CS"         = "Endodermal CS",
                             "En.CS-Ex.LC"   = "Endodermal CS",
                             "En.CS-Ex.Sub"  = "Endodermal CS",
                             "En.Sub"        = "Endodermal Sub",
                             "En.Sub-Ex.CS"  = "Endodermal Sub",
                             "En.Sub-Ex.Sub" = "Endodermal Sub")
         ) %>% 
  mutate(Exodermis = recode(Barrier_Name,
                             "En.CS"         = "none",
                             "En.CS-Ex.LC"   = "LC",
                             "En.CS-Ex.Sub"  = "Sub",
                             "En.Sub"        = "none",
                             "En.Sub-Ex.CS"  = "LC",
                             "En.Sub-Ex.Sub" = "Sub")
         ) %>% 
  mutate(kr = kr*1e8)

# Custom order
data2plot$Barrier_Name <- factor(data2plot$Barrier_Name, 
                                 levels = c("En.CS", 
                                            "En.CS-Ex.LC", 
                                            "En.CS-Ex.Sub", 
                                            "En.Sub", 
                                            "En.Sub-Ex.CS", 
                                            "En.Sub-Ex.Sub")
                                 )

data2plot$Exodermis <- factor(data2plot$Exodermis, 
                                 levels = c("none", 
                                            "LC", 
                                            "Sub")
                                 )

data2plot <- data2plot[order(data2plot$Barrier_Name),]

# ============================================================================ #
library(ggsignif)
p_Barriers <- ggplot(data = data2plot, 
                     aes(x = Exodermis, 
                         y = kr)
                     ) +
  
  # # ADD VIOLINS
  geom_violin(aes(fill  = Barrier_Name),
              # fill  = "lightgrey",
              color = "white",
              alpha = 0.2) +

  # ADD BOXPLOTS
  geom_boxplot(width = 0.5,
               alpha = 1) +
  
  # ADD POINTS
  geom_jitter(aes(x = Exodermis, 
                  y = kr,
                  color = Barrier_Name)
              ,width = 0.1
              ,size = 1
              ) +
  
  facet_wrap(~Endodermis, scales = "free") +
  
  # ADD SIGNIFICANTS
  geom_signif(comparisons = list(c("none", "LC"),
                                 c("none", "Sub"),
                                 c("LC", "Sub")
                                 ),
              map_signif_level = F,
              test = "wilcox.test",
              # test.args = list(formula = "kr ~ Barrier_Name"),
              y_position = c(15, 17, 19)
              ) +
  
  # CUSTOM LABELS
  xlab("Exodermis") +
  ylab(expression(k[r] ~ "[" ~ 10^{-08} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  ylim(1, 20) +
  
  # OTHER PARAMS
  # scale_fill_manual(values=c("white","white","white", "grey", "grey", "grey")) +
  # scale_color_viridis() +
  scale_color_manual(values = color_scale2) +
  scale_fill_manual(values = color_scale2) +
  
  theme_few() +
  theme(legend.position = "none"
        ,axis.line = element_line()
        ,panel.border = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90))

# =========================================================================== #
p_Barriers

ggsave(filename = "plots/MECHA_results_barriers.svg", 
       plot = p_Barriers, 
       device = "svg", width = 5, height = 5)

svg(filename = "plots/MECHA_results_barriers.svg", width = 4, height = 4)
p_Barriers
dev.off()
```





