---
title: "RESULTS ANALYSIS"
format: html
editor: source
editor_options: 
  chunk_output_type: inline
---

```{r Load Packages, include=F}
DIR_path <- getwd()
options(rstudio.help.showDataPreview = FALSE)
rm(list = ls())

TRoot_path <- "src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path)) {
  print(i)
  source(paste0(TRoot_path, i))
}

libs <- c("pander", "readxl", "EnvStats", 
          "FactoMineR", "factoextra", 
          "data.table", "reticulate", 
          "dplyr", "tidyverse", 
          "xml2", 
          "viridis", "Hmisc", "ggplot2", 
          "gridExtra", "Matrix", "emmeans", 
          "ggthemes", "SciViews")

for(pk in libs) {
  library(pk, character.only = T)
}

simu_path <- "Results/12-01-2023/"
```

# Load Results from MECHA

* kr and kAQP are converted from $cm d^{-1} HPa^{-1}$ to $m s^{-1} MPa^{-1}$

* kpl is converted from $cm^3/hPa/d/plasmodesmata$ to $m^{3} s^{-1} MPa^{-1} pd^{-1}$

* Kx is converted to $cm^{4} d^{-1} HPa^{-1}$ to $m^3 s^{-1} MPa^{-1}$

```{r}
MECHA_results  <- read.csv("./Results/MECHA_results.csv")
Anatomy_Full   <- read.csv("Data/Anatomy/Anatomy_Full.csv")
anatomy2       <- read.csv("Data/Anatomy/anatomy2.csv")
Parameters     <- read_xlsx("Data/Parameters.xlsx")

# Convert kr and kx to m3 s-1 MPa-1
MECHA_results <- MECHA_results %>% 
  mutate(kr = kr*0.001157407,
         Kx = Kx*1.157407e-09,
         Kr = kr*perimeter,
         kpl = kpl*(1e-6 * 1e4 * (60*60*24)^-1)
         # kAQP = kAQP*0.001157407
         )

# Change barrier names
MECHA_results$Barrier_Name <- NaN
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b1"] <- "En.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b2"] <- "En.Sub*"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b3"] <- "En.Sub"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b4"] <- "En.Sub-Ex.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b5"] <- "En.CS-Ex.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b6"] <- "En.CS-Ex.Sub"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b7"] <- "Ex.CS"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b8"] <- "En.Sub-Ex.Sub"
MECHA_results$Barrier_Name[MECHA_results$Barrier == "b9"] <- "En.CS-Ex.LC"
```

# ANALYSE QUANTIFIED DATA

Here we analyse the results of conductivities computed on quantified cross-sections.

## Plot kr vs each anatomical trait

```{r}
# data2plot <- MECHA_results %>% 
#   filter(Barrier_Name %in% c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub")) 
# 
cols <- c(
  "cortex_cell_diameter",
  "cortex_n_layers",
  "endodermis_cell_diameter",
  "epidermis_cell_diameter",
  "exodermis_cell_diameter",
  "pericycle_cell_diameter",
  "phloem_cell_diameter",
  "phloem_n_layers",
  "phloem_proportion",
  "secondarygrowth_param",
  "stele_cell_diameter",
  "stele_layer_diameter",
  "stele_n_layers",
  "stele_SD",
  "xylem_cell_diameter",
  "xylem_max_size",
  "xylem_n_cells"
  )

plist <- Parameters %>% 
  filter(param_id %in% cols)
plist <- plist$param_id

data2plot <- MECHA_results[c("CS_id", "kr", "kAQP", "Barrier_Name")] %>% 
  filter(kAQP == 4e-4) %>% 
  select(-kAQP) %>% 
  filter(Barrier_Name %in% c("En.CS")) %>% 
  left_join(Anatomy_Full[c("CS_id", plist, "radius", "age")], by = "CS_id") %>% 
  select(-c("CS_id")) %>% 
  gather(c(all_of(plist), "radius", "age"), key = "Variable", value = "Value")

color_scale <- c("En.CS" = "black", 
                 "En.CS-Ex.LC" = "#C71AB7", 
                 "En.CS-Ex.Sub" = "#4E3CA5")

p <- ggplot(data2plot,
       aes(x = Value, y = kr, color = Barrier_Name)) +
  
  # geom_line(aes(x = age, y = Kr, group = plant_id)) +
  
  geom_point(alpha = 1, size = 0.5) +
  # geom_smooth(method = "loess", span = 1) +
  scale_color_manual(values = color_scale) +
  facet_wrap(~Variable, scales = "free", nrow = 3) +
  theme_few() +
  theme(axis.text.x = 
          element_text(angle = 90, hjust = 1, vjust = 0.5))

p
ggsave(filename = "plots/kr_vs_anatomy.png", plot = p,
       device = "png", width = 15, height = 8, dpi = 200)
```


## Radial conductivity & conductance at fixed kAQP

```{r}
color_scale <- c("En.CS"        = "black", 
                 "En.CS-Ex.LC"  = "#C71AB7", 
                 "En.CS-Ex.Sub" = "#4E3CA5")

data2plot <- MECHA_results %>% 
  filter(kAQP == 4e-4) %>%
  filter(Barrier_Name %in% c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub")) %>% 
  # mutate(kr = kr*1e8,
  #        Kr = Kr*1e9) %>% 
  left_join(Anatomy_Full, by = "CS_id") %>% 
  select(c("Barrier_Name", "age", "kr", "Kr", "kAQP")) %>% 
  gather(kr, Kr, key = "Variable", value = "Value") 
  
# ============================================================================ #

p_RadialConds <- ggplot(data2plot) +
  geom_point(aes(x = age, 
                 y = Value,
                 color = Barrier_Name)) +
  
  geom_smooth(aes(x = age, 
                  y = Value,
                  color = Barrier_Name,
                  fill = Barrier_Name
                  ), 
              # color = "black",
              alpha = 0.1,
              span = 1) +
  
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  
  xlab("Age [d]") +
  # ylab(expression(K[r] ~ "[" ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  facet_wrap(~Variable, scales = "free") +
  # facet_grid(Variable~kAQP) +
  
  theme_few() +
  theme(legend.position = "bottom") 

# ============================================================================ #
p_RadialConds
# svg(filename = "plots/MECHA_results_kr-Kr_all-kAQP.svg", width = 12, height = 6)
# p_RadialConds
# dev.off()

svg(filename = "plots/MECHA_results_kr-Kr.svg", width = 6, height = 4)
p_RadialConds
dev.off()
```

## Axial conductance

```{r}
# Select data for only one Barrier (they all have the same values anyway)
data2plot <- MECHA_results %>% 
  filter(Barrier == "b1" & kAQP == 1e-4) %>% 
  select(c("CS_id", "Kx")) %>% 
  left_join(Anatomy_Full[c("CS_id", "age")], by = "CS_id") %>% 
  mutate(Kx_ln = ln(Kx))

Kx_plot <- ggplot(data2plot) +

  geom_point(aes(x = age,
                 y = Kx)) +
  
  geom_smooth(aes(x = age, y = Kx),
              # span = 1,
              method = "lm",
              se = F) +
  
  xlab("Age [d]") +
  ylab(expression(k[x] ~ "[" ~ m^{4} ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  
  scale_y_continuous(trans = 'log10') +
  
  theme_few()

# =========================================================================== #
Kx_plot

svg(filename = "plots/MECHA_results_Kx.svg", width = 3, height = 3)
Kx_plot
dev.off()

# ggsave(filename = "plots/data_kx_plot.svg", plot = Kx_plot, device = "svg", width = 3, height = 3)
```


## Important anatomical parameters

```{r}
variables <- c("xylem_cell_diameter", 
               "xylem_n_cells", 
               "stele_layer_diameter", 
               "cortex_n_layers", 
               "phloem_n_layers", 
               "radius")

data2plot <- unique(MECHA_results[c("CS_id", "Kx")]) %>% 
  left_join(Anatomy_Full, by = "CS_id") %>% 
  select(c("age", variables)) %>% 
  gather(variables,
         key = "Variable", value = "Value")

Anatomy_plot <- ggplot(data2plot) +
  
  geom_point(aes(x = age, y = Value)) +
  geom_smooth(aes(x = age, y = Value),
              span = 1, se = T) +
  
  facet_wrap(~Variable, scales = "free") +
  theme_few()
Anatomy_plot

svg(filename = "plots/Anatomy_important_traits.svg", width = 5, height = 4)
Anatomy_plot
dev.off()

ggsave(filename = "plots/Anatomy_important_traits.png", plot = Anatomy_plot, 
       device = "png", width = 6, height = 4, dpi = 300)
```

### Secondary growth

```{r}
data2plot <- Anatomy_Full %>% 
  select("age", "secondarygrowth_param")

ggplot(data2plot, aes(x = age, y = secondarygrowth_param)) +
  geom_point() +
  geom_smooth_logistic
```



## Analyse corelations between kr and anatomical measurements

```{r}
plist <- Parameters %>% 
  filter(param_id %in% colnames(Anatomy_Full))
plist <- plist$param_id

data2stat <- MECHA_results[c("CS_id", "kr", "kAQP")] %>%
  filter(kAQP == 4e-4) %>% 
  select(-kAQP) %>% 
  left_join(Anatomy_Full[c("CS_id", plist, "radius", "age")], by = "CS_id") %>% 
  select(-c("CS_id"))

kr_corr <- data2stat %>% 
  select(-kr) %>% 
  sapply(function(x) cor(x, data2stat$kr, use = "complete.obs"))

pander(kr_corr)
```





# COMPLETE STATISTICAL ANALYSIS

## 1) Radial conductivity

### Linear model

```{r}
barriers <- c("En.CS", 
              "En.CS-Ex.LC", 
              "En.CS-Ex.Sub", 
              "En.Sub", 
              "En.Sub-Ex.CS", 
              "En.Sub-Ex.Sub")

th <- 3 # Outlier treshold (x)

# Define data
data2stat <- MECHA_results %>% 
  select(c("Barrier_Name", "kr", "kAQP", "CS_id")) %>% 
  left_join(Anatomy_Full[c("CS_id", "age", "radius")], by = "CS_id") %>% 
  mutate(Barrier_Name = as.factor(Barrier_Name)) %>% 
  filter(Barrier_Name %in% barriers) %>% 
  mutate(kr = 1e8*kr)

# # Remove outliers
# data2stat <- data2stat %>% 
#   group_by(Barrier_Name) %>%
#   mutate(
#     median = median(kr, na.rm = TRUE),
#     mad = mad(kr, na.rm = TRUE),
#     lower_bound = median - th * mad,
#     upper_bound = median + th * mad
#   ) %>%
#   filter(kr >= lower_bound & kr <= upper_bound) %>%
#   select(-median, -mad, -lower_bound, -upper_bound) 

# CHECK NORMALITY
par(mfrow = c(1, 2))
qqnorm(data2stat$kr)
qqline(data2stat$kr)
hist(data2stat$kr)  
shapiro.test(data2stat$kr)

# NORMALIZE WITH BOX-COX
# par(mfrow = c(1))
bc     <- MASS::boxcox(lm(data2stat$kr ~ 1))
lambda <- bc$x[which(bc$y == max(bc$y))]

data2stat$kr_tf <- BoxCox(data2stat$kr, lambda)
# data2stat$kr_tf <- log(sqrt(data2stat$kr))

# CHECK NORMALITY
par(mfrow = c(1, 2))
qqnorm(data2stat$kr_tf)
qqline(data2stat$kr_tf)
hist(data2stat$kr_tf)  
shapiro.test(data2stat$kr_tf)
```

```{r}
p <- ggplot(data2stat) +
  
  geom_jitter(aes(x = Barrier_Name, 
                  y = kr,
                  color = kAQP,
                  size = radius^2), 
              width = 0.25,
              alpha = 0.75
              ) +
  
  # geom_boxplot(aes(x = Barrier_Name,
  #                 y = ))
  
  scale_color_viridis() +
  scale_size_area(
                  max_size = 5) +
  
  theme_few() +
  theme(axis.line = element_line()
        ,panel.border = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90))
  
p

ggsave("./plots/MECHA_results_MixedPlot.svg", plot = p,
       device = "svg", width = 5, height = 5)
```


```{r}
data2plot <- data2stat %>% 
  mutate(
    # kr_tf2 = kr_tf,
    # kr_tf2 = 25^-(kr_tf)
  )

p <- ggplot(data2plot,
       aes(x = radius, y = kr_tf
           )
       ) +
  geom_point(aes(shape = Barrier_Name, color = kAQP)) +
  scale_color_viridis() +
  facet_grid(Barrier_Name ~ kAQP) +
  geom_smooth(method = "lm") +
  theme_few()
p
ggsave(filename = "./plots/MECHA_results_FULL_TABLE.svg", plot = p,
       device = "svg", width = 5, height = 5)
```


```{r}
lm_kr1 <- lm(data = data2stat, 
             formula = kr_tf ~ 
               age +
               radius +
               Barrier_Name +
               kAQP +
               kAQP:Barrier_Name
               )

par(mfrow = c(2, 2))
plot(lm_kr1)

cat("================= \n  LINEAR MODEL \n=================\n")
summary(lm_kr1)

# cat("================= \n  ANOVA \n=================\n")
# anova(lm_kr1)

# Export model 
saveRDS(object = lm_kr1, file = "./Results/kr_model.rds")
```

Let's try to predict some stuff :

```{r}
# ============================================================================ #
data2stat$kr_pred <- BoxCox_reverse(predict(lm_kr0, data2stat), lambda)
cat("RMSE : ", sqrt(mean((data2stat$kr - data2stat$kr_pred)^2)))
# ============================================================================ #
ggplot(data2stat) +
  geom_point(aes(x = kr, 
                 y = kr_pred,
                 color = kAQP,
                 size = radius
                 ),
             alpha = 0.5) +
  
  # geom_smooth(aes(x = kr, 
  #                 y = kr_pred), 
  #             method = "loess", 
  #             color = "red") +

  coord_fixed(ratio = 1:1) +
  
  xlim(0, 20) +
  ylim(0, 20) +
  
  geom_abline(linewidth = 1, color = "red") +
  scale_color_viridis() +
  
  # facet_wrap(~kAQP) +
  
  xlab("Computed kr") + ylab("Predicted kr") +
  theme_classic()
```

## 2) Axial Kx

At first i tested a ln transformation, but generalised Box-Cox transformation is better, so let's keep it.

```{r}
data2stat <- MECHA_results %>%
  filter(kAQP == 1e-4 & Barrier_Name == "En.CS-Ex.Sub") %>% 
  left_join(Anatomy_Full[c("CS_id", "age", "radius")], by = "CS_id") %>% 
  select("Kx", "age", "radius") %>% 
  mutate("Kx_ln" = ln(Kx))

# CHECK NORMALITY ON ln TRANSFORMED DATA
par(mfrow = c(1, 2))
qqnorm(data2stat$Kx_ln)
qqline(data2stat$Kx_ln)
hist(data2stat$Kx_ln)  
shapiro.test(data2stat$Kx_ln)

# NORMALIZE WITH BOX-COX
bc              <- MASS::boxcox(lm(data2stat$Kx ~ 1))
lambda          <- bc$x[which(bc$y == max(bc$y))]
cat("Kx lambda : ", lambda, "\n")
data2stat$Kx_tf <- BoxCox(data2stat$Kx,  lambda)

# RE-CHECK NORMALITY ON BOX-COX TRANSFORMED DATA
par(mfrow = c(1, 2))
qqnorm(data2stat$Kx_tf)
qqline(data2stat$Kx_tf)
hist(data2stat$Kx_tf)  
shapiro.test(data2stat$Kx_tf)

# LINEAR REGRESSION
lm_Kx1 <- lm(data    = data2stat, 
             formula = ln(Kx) ~ radius+age)

plot(lm_Kx1)
summary(lm_Kx1)
# anova(Kx_lm)

```

$$
ln(K_x^*) = \alpha + \beta \cdot t + \gamma \cdot r
$$

```{r}
cat("alpha = ", lm_Kx1$coefficients[1], "\n")
cat("beta  = ", lm_Kx1$coefficients[2], "\n")
cat("gamma = ", lm_Kx1$coefficients[3], "\n")
```

```{r}
data2stat$Kx_pred <- BoxCox_reverse(exp(1)^(predict(lm_Kx1, data2stat)), lambda)

ggplot(data2stat) +
  geom_point(aes(x = ln(Kx), y = ln(Kx_reg), color = x)) +
  geom_smooth(aes(x = ln(Kx), y = ln(Kx_reg)), method = "lm", color = "red") +
  coord_fixed() +
  xlim(-26.5, -18) +
  ylim(-26.5, -18) +
  xlab("ln(Kx)") + ylab("ln(Kx*)") +
  geom_abline() +
  scale_color_viridis() +
  theme_classic()
  
# ==============================================================================
```




# Pairwise analysis of hydrophobic barriers

We take here the effect of barriers when kAQP is at mean value

### 0) Prepare data

```{r}
barriers <- c("En.CS", "En.CS-Ex.LC", "En.CS-Ex.Sub", 
              "En.Sub", "En.Sub-Ex.CS", "En.Sub-Ex.Sub")
th <- 3 # Outlier treshold (x)

# Define data
data2stat <- MECHA_results %>% 
  filter(kAQP == 4e-4) %>% 
  select(c("Barrier_Name", "kr")) %>% 
  mutate(Barrier_Name = as.factor(Barrier_Name)) %>% 
  filter(Barrier_Name %in% barriers)

# Remove outliers
data2stat <- data2stat %>% 
  group_by(Barrier_Name) %>%
  mutate(
    median = median(kr, na.rm = TRUE),
    mad = mad(kr, na.rm = TRUE),
    lower_bound = median - th * mad,
    upper_bound = median + th * mad
  ) %>%
  filter(kr >= lower_bound & kr <= upper_bound) %>%
  select(-median, -mad, -lower_bound, -upper_bound) 
```

### 1) Check normality

We use Shapiro-Wilk test (Shapiro & Wilk 1963).

```{r}
# FIRST NORMALITY TEST
shapiro.test(data2stat$kr)
ks.test(data2stat$kr, 'pnorm', mean(data2stat$kr), sd(data2stat$kr))
hist(data2stat$kr, breaks = 20)
qqnorm(data2stat$kr)
qqline(data2stat$kr)
```

We see that data is not normal so we apply a Cox-Box transfomation (Box & Cox 1964).

```{r}
#APPLY COX-BOX TRANSFORMATION
bc     <- MASS::boxcox(lm(data2stat$kr ~ 1))
lambda <- bc$x[which(bc$y == max(bc$y))]

data2stat <- data2stat %>% 
  mutate(kr_tf = BoxCox(kr, lambda)) %>% 
  mutate(kr_test = BoxCox_reverse(kr_tf, lambda))

# SECOND NORMALITY CHECK
shapiro.test(data2stat$kr_tf)
ks.test(data2stat$kr_tf, 'pnorm', mean(data2stat$kr_tf), sd(data2stat$kr_tf))
hist(data2stat$kr_tf, breaks = 15)
qqnorm(data2stat$kr_tf)
qqline(data2stat$kr_tf)

# ============================================================================ #
ggplot(data2stat) +
  geom_point(aes(x = Barrier_Name, y = kr_tf)) +
  theme_few()
```

### 2) ANOVA

Let's try a linear model on transform (normalized) data.

```{r}
Barrier_lm <- lm(data = data2stat, 
                 formula = kr_tf ~ Barrier_Name)

plot(Barrier_lm)
# summary(Barrier_lm)
anova(Barrier_lm)
```

### 3) Post-Hoc Mean Comparison

```{r}
EM <- emmeans(Barrier_lm, specs = pairwise ~ Barrier_Name)

Means <- as_tibble(EM$emmeans)
Contrasts <- as_tibble(EM$contrasts)

Means$emmean_TF <- BoxCox_reverse(Means$emmean, lambda)

```

To develop because we transformed the data !

```{r}
mean_b1 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.CS"], lambda)
mean_b2 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.CS-Ex.LC"], lambda)
mean_b3 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.CS-Ex.Sub"], lambda)
mean_b4 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.Sub"], lambda)
mean_b5 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.Sub-Ex.CS"], lambda)
mean_b6 <- BoxCox_reverse(Means$emmean[Means$Barrier_Name == "En.Sub-Ex.Sub"], lambda)

print(paste0("Difference between En.CS and En.CS-Ex.LC [%]         : ", round((mean_b1-mean_b2)*100/mean_b1, digits = 2)))
print(paste0("Difference between En.CS and En.Sub [%]              : ", round((mean_b1-mean_b4)*100/mean_b1, digits = 2)))
```


### 5) Plot

```{r}
color_scale2 <- c("En.CS"        = "black", 
                  "En.CS-Ex.LC"  = "#C71AB7", 
                  "En.CS-Ex.Sub" = "#4E3CA5",
                  "En.Sub"       = "lightblue4",
                  "En.Sub-Ex.CS" = "lightblue4",
                  "En.Sub-Ex.Sub"= "lightblue4"
                  )

# ============================================================================ #
data2plot <- data2stat %>% 
  mutate(Endodermis = recode(Barrier_Name,
                             "En.CS"         = "Endodermal CS",
                             "En.CS-Ex.LC"   = "Endodermal CS",
                             "En.CS-Ex.Sub"  = "Endodermal CS",
                             "En.Sub"        = "Endodermal Sub",
                             "En.Sub-Ex.CS"  = "Endodermal Sub",
                             "En.Sub-Ex.Sub" = "Endodermal Sub")
         ) %>% 
  mutate(Exodermis = recode(Barrier_Name,
                             "En.CS"         = "none",
                             "En.CS-Ex.LC"   = "LC",
                             "En.CS-Ex.Sub"  = "Sub",
                             "En.Sub"        = "none",
                             "En.Sub-Ex.CS"  = "LC",
                             "En.Sub-Ex.Sub" = "Sub")
         ) %>% 
  mutate(kr = kr*1e8)

# Custom order
data2plot$Barrier_Name <- factor(data2plot$Barrier_Name, 
                                 levels = c("En.CS", 
                                            "En.CS-Ex.LC", 
                                            "En.CS-Ex.Sub", 
                                            "En.Sub", 
                                            "En.Sub-Ex.CS", 
                                            "En.Sub-Ex.Sub")
                                 )

data2plot$Exodermis <- factor(data2plot$Exodermis, 
                                 levels = c("none", 
                                            "LC", 
                                            "Sub")
                                 )

data2plot <- data2plot[order(data2plot$Barrier_Name),]

# ============================================================================ #
library(ggsignif)
p_Barriers <- ggplot(data = data2plot, 
                     aes(x = Exodermis, 
                         y = kr)
                     ) +
  
  # # ADD VIOLINS
  geom_violin(aes(fill  = Barrier_Name),
              # fill  = "lightgrey",
              color = "white",
              alpha = 0.2) +

  # ADD BOXPLOTS
  geom_boxplot(width = 0.5,
               alpha = 1) +
  
  # ADD POINTS
  geom_jitter(aes(x = Exodermis, 
                  y = kr,
                  color = Barrier_Name)
              ,width = 0.1
              ,size = 1
              ) +
  
  facet_wrap(~Endodermis, scales = "free") +
  
  # ADD SIGNIFICANTS
  geom_signif(comparisons = list(c("none", "LC"),
                                 c("none", "Sub"),
                                 c("LC", "Sub")
                                 ),
              map_signif_level = F,
              test = "wilcox.test",
              # test.args = list(formula = "kr ~ Barrier_Name"),
              y_position = c(15, 17, 19)
              ) +
  
  # CUSTOM LABELS
  xlab("Exodermis") +
  ylab(expression(k[r] ~ "[" ~ 10^{-08} ~ m ~ MPa^{-1} ~ s^{-1} ~ "]")) +
  ylim(1, 20) +
  
  # OTHER PARAMS
  # scale_fill_manual(values=c("white","white","white", "grey", "grey", "grey")) +
  # scale_color_viridis() +
  scale_color_manual(values = color_scale2) +
  scale_fill_manual(values = color_scale2) +
  
  theme_few() +
  theme(legend.position = "none"
        ,axis.line = element_line()
        ,panel.border = element_blank()
        ) +
  theme(axis.text.x = element_text(angle = 90))

# =========================================================================== #
p_Barriers

ggsave(filename = "plots/MECHA_results_barriers.svg", 
       plot = p_Barriers, 
       device = "svg", width = 5, height = 5)

svg(filename = "plots/MECHA_results_barriers.svg", width = 4, height = 4)
p_Barriers
dev.off()
```





