---
title: "MPIPE"
format: html
editor: source
---

# SET UP

Here we load functions and data.
Simulations_ID, RSA.IDs and Scenarios_ID are mannually encoded XLXS containing metadata.
We also define conversion rates from cm HPa-1 d-1 to m MPa-1 s-1.

```{r, include=F}
# knitr::opts_chunk$set(echo = FALSE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # Set working directory to the current file
rm(list = ls())
# options(rstudio.help.showDataPreview = FALSE) # Prevent Bug

# ============================================================================ #
# DEFINE PATHS
CRBM.path    <- "./src/CRB-MARSHAL/"
path.results <- "C:/Users/mdagostino/OneDrive - UCL/T-ROOT/ANALYSIS/RESULTS/CRB-MARSHAL/"
path.plots   <- "./plots/CRB-MARSHAL/"
# ============================================================================ #
libs <- c("pander", 
          "readxl", 
          "EnvStats", 
          "FactoMineR", 
          "factoextra", 
          "data.table", 
          "reticulate", 
          "xml2",
          "tidyverse", 
          "dplyr", 
          "viridis", 
          "Hmisc", 
          "ggplot2", 
          "gridExtra", 
          "Matrix", 
          "emmeans", 
          "ggthemes")

for(pk in libs) {
  library(pk, character.only = T)
}
# ============================================================================ #
# LOAD CRB-MARSHAL FUNCTIONS
source(paste0(CRBM.path, "Get_SUF.R")) # MARSHAL
source(paste0(CRBM.path, "SUF.R"))
source(paste0(CRBM.path, "CRBM_functions.R"))
# ============================================================================ #
# LOAD CUSTOM TROOT FUNCTIONS
TRoot_path <- "./src/FUNCTIONS/T-Root/"
for (i in list.files(TRoot_path, pattern = ".R")) {
  print(i)
  source(paste0(TRoot_path, i))
}
# ============================================================================ #
# LOAD DATA TABLES
Simulations_ID <- read_xlsx(paste0(CRBM.path, "inputs/Simulations_ID.xlsx"))
Scenarios_ID   <- read_xlsx(paste0(CRBM.path, "inputs/Scenarios_ID.xlsx"))
RSA.IDs        <- read.csv(paste0(CRBM.path, "inputs/RSA_id.csv"))

# ============================================================================ #
# define colors 
S_colors <- c("WT"    = '#0F9ED5', 
              'kAQP'  = '#4EA72E', 
              'Sub'   = '#E97132', 
              'SubSG' = '#FFC000')

# LOAD PRE-PROCESSED RSA
RSA.all <- read.csv(paste0(CRBM.path, "inputs/RSA_all.csv"))

# Set conversion rates
kr.conv   <-  1.157407e-3
kx.conv   <-  1.157407e-9
krs.conv  <-  1.157407e-7
```

# LOAD ROOT SYSTEM ARCHITECTURES

We generated raw Root System Architectures (RSA) from CRootBox online interface and stored them in `./src/CRB-MARSHAL/inputs/RSA/raw/ folder`. \ 
We need to process them, and then we store them in `./src/CRB-MARSHAL/inputs/RSA/` folder. \
Each RSA is associated with a RSA_id and we create a table `RSA_id`. \

## [ONLY DO IT ONCE!] Load and process raw RSA files

We loop through each RSA in *.txt* format, we format it and than we store everything in one big table called *RSA.all.csv*
 
```{r}
# process.RSA <- F
# 
# if(process.RSA){
#   
#   RSA.path     <- "./src/CRB-MARSHAL/inputs/RSA/"
#   RSA.path.raw <- paste0(RSA.path, "raw/")
#   RSA_list     <- list.files(RSA.path.raw, pattern = ".txt")
#   RSA.all      <- tibble()
#   RSA.IDs      <- tibble()
#   
#   for(RSA_i in RSA_list){
#     # Load and process temp RSA
#     RSA_id_i        <- unlist(strsplit(RSA_i, split = ".txt"))[1]
#     RSA_temp        <- read.table(paste0(RSA.path.raw, RSA_i), header = T)
#     RSA_temp        <- reconnect.nodes(RSA_temp)
#     RSA_temp$RSA_id <- RSA_id_i
#     write.csv(x = RSA_temp, 
#               file = paste0(RSA.path, RSA_id_i, ".csv"), 
#               row.names = F)
#   
#     # Update RSA.IDs table
#     RSA_id_i_df     <- tibble(planttype = 
#                                 unlist(strsplit(RSA_id_i, split = "_"))[1],
#                               age       = 
#                                 unlist(strsplit(RSA_id_i, split = "_"))[2],
#                               rep       = 
#                                 unlist(strsplit(RSA_id_i, split = "_"))[3],
#                               RSA_id    = 
#                                 RSA_id_i)
#     RSA.IDs         <- rbind(RSA.IDs, RSA_id_i_df)
#   
#     # Add RSA to global RSA.all table
#     RSA.all         <- rbind(RSA.all, RSA_temp)
#   }
#   
#   # Write files
#   write.csv(x = RSA.all,
#             file = paste0(CRBM.path, "inputs/RSA_all.csv"),
#             row.names = F)
#   
#   write.csv(x = RSA.IDs,
#             file = paste0(CRBM.path, "inputs/RSA_id.csv"),
#             row.names = F)
#   
# }
```

## Plot pre-processed RSA

```{r}
# RSA_plot <- ggplot(RSA.all) +
#   geom_segment(aes(x = x1, xend = x2, 
#                    y = z1, yend = z2, 
#                    color = branchID)
#                ) +
#   facet_wrap(~RSA_id, nrow = 2) +
#   scale_color_viridis(option = "plasma") +
#   coord_fixed() +
#   theme_few()
# 
# RSA_plot

# ggsave(filename = paste0(path.plots, "RSA_raw.png"), 
#        plot = RSA_plot, device = "png", 
#        width = 10, height = 5, dpi = 300)
```

# Define conductivities

Here we build and plot conductivity curves that we will apply in MARSHAL. \
First, load coefficients of kr and kx regressions computed in TROOT_ANALYSIS \
* kr is converted from $m s^{-1} MPa^{-1}$ to $cm d^{-1} HPa^{-1}$ \
* kx is converted from $m^4 s^{-1} MPa^{-1}$ to $cm^4 d^{-1} HPa^{-1}$ \

Let's define 3 scenarios :

-   WT : \
    -   SG     = T \
    -   Ex.LC  = T \
    -   Ex.Sub = T \
    -   kAQP   = constant \
-   -AQP : \
    -   SG     = T \
    -   Ex.LC  = T \
    -   Ex.Sub = T \
    -   kAQP   = decreasing \
-   -Sub : \
    -   SG     = T \
    -   Ex.LC  = T \
    -   Ex.Sub = F \
    -   kAQP   = constant \
-   -SG-Sub : \
    -   SG     = F \
    -   Ex.LC  = T \
    -   Ex.Sub = F \
    -   kAQP   = constant \

## General parameters

```{r}
source("./src/CRB-MARSHAL/CRBM_functions.R")
source("./src/FUNCTIONS/T-Root/Functions_Misc.R")

# Load statistical models that we built in TROOT_ANALYSIS.qmd
lm_kr <- readRDS("./Results/kr_model.rds")
lm_kx <- readRDS("./Results/kx_model.rds")
lm_r  <- readRDS("./Results/radius_model.rds")

# DEFAULTS PARAMETERS
nmin           <- 0
nmax           <- 60         # Maximum number of iterations

# SG TIMING (default 7 - 20)
SG_timingWT    <- c(7, 25)
SG_timingkAQP  <- c(7, 25)
SG_timingSub   <- c(7, 25)
SG_timingSubSG <- c(100, 101)

# MS TIMING (default 1 - 7) # for En.CS | timing[1] | En.CS-Ex.LC | timing[2] | En.CS-Ex.Sub
MS_timingWT    <- c(1,   7)
MS_timingkAQP  <- c(1,   7)
MS_timingSub   <- c(1,   101)
MS_timingSubSG <- c(1,   101)

rmin           <- 0.198      # minimum radius (default = 0.198 from data)
rmax           <- 2          # maximum radius

kx.min         <- 0
kx.max         <- 1e-7

# ============================================================================ #
# SCENARIO WT
Conds_WT <- create.conds(S_ID = "WT"
                          ,nmin          = nmin
                          ,nmax          = nmax
                          ,SG_timing     = SG_timingWT
                          ,MS_timing     = MS_timingWT
                          ,radius_pred_f = lm_r
                          ,kr_pred       = lm_kr
                          ,kx_pred       = lm_kx
                          ,kAQP_start    = 5e-4
                          ,kAQP_end      = 5e-4
                          ,rmin          = 0.198
                          ,rmax          = 2
                          ,kx.max        = kx.max
                          )

mparam_WT <- tibble(SG_timing = SG_timingWT,
                    MS_timing = MS_timingWT,
                    rmin      = rmin,
                    rmw       = rmax,
                    S_ID      = "WT")

# ============================================================================ #
# SCENARIO -AQP
Conds_kAQP <- create.conds(S_ID = "kAQP"
                          ,nmin          = nmin
                          ,nmax          = nmax
                          ,SG_timing     = SG_timingWT
                          ,MS_timing     = MS_timingWT
                          ,radius_pred_f = lm_r
                          ,kr_pred       = lm_kr
                          ,kx_pred       = lm_kx
                          ,kAQP_start    = 5e-4
                          ,kAQP_end      = 1e-16
                          ,rmin          = 0.1988
                          ,rmax          = 2
                          ,kx.max        = kx.max
                          )

mparam_kAQP <- tibble(SG_timing = SG_timingkAQP,
                      MS_timing = MS_timingkAQP,
                      rmin      = rmin,
                      rmw       = rmax,
                      S_ID      = "kAQP")
# ============================================================================ #
# SCENARIO Sub
Conds_Sub <- create.conds(S_ID = "Sub"
                          ,nmin          = nmin
                          ,nmax          = nmax
                          ,SG_timing     = SG_timingSub
                          ,MS_timing     = MS_timingSub
                          ,radius_pred_f = lm_r
                          ,kr_pred       = lm_kr
                          ,kx_pred       = lm_kx
                          ,kAQP_start    = 5e-4
                          ,kAQP_end      = 5e-4
                          ,rmin          = 0.198
                          ,rmax          = 2
                          ,kx.max        = kx.max
                          )

mparam_Sub <- tibble(SG_timing = SG_timingSub,
                    MS_timing = MS_timingSub,
                    rmin      = rmin,
                    rmw       = rmax,
                   S_ID       = "Sub")
# ============================================================================ #
# SCENARIO SubSG
Conds_SubSG <- create.conds(S_ID = "SubSG"
                          ,nmin          = nmin
                          ,nmax          = nmax
                          ,SG_timing     = SG_timingSubSG
                          ,MS_timing     = MS_timingSubSG
                          ,radius_pred_f = lm_r
                          ,kr_pred       = lm_kr
                          ,kx_pred       = lm_kx
                          ,kAQP_start    = 5e-4
                          ,kAQP_end      = 5e-4
                          ,rmin          = 0.198
                          ,rmax          = 0.198
                          ,kr.min        = 1e-10
                          ,kr.max        = 1.5e-7
                          ,kx.min        = 0
                          ,kx.max        = 2e-10
                          )

mparam_SubSG <- tibble(SG_timing = SG_timingSubSG,
                   MS_timing = MS_timingSubSG,
                   rmin      = rmin,
                   rmw       = rmax,
                   S_ID = "SubSG")
# ============================================================================ #
# Rbind all scenarios together
Conds.tot <- rbind(Conds_WT, Conds_kAQP) %>% 
  rbind(Conds_Sub) %>% rbind(Conds_SubSG) %>% 
  gather(radius, kAQP, kr, kx, key = "type", value = "y")

mparams   <- rbind(mparam_WT, mparam_kAQP) %>% 
  rbind(mparam_Sub) %>% rbind(mparam_SubSG)

Conds.tot$S_ID <- factor(Conds.tot$S_ID,
                         levels = c("WT", "kAQP", "Sub", "SubSG"))


# Convert kr and kx to cm d HPa
# Conds.tot$y[Conds.tot$type == "kr"]   <- Conds.tot$y[Conds.tot$type == "kr"]/conv_kr
# Conds.tot$y[Conds.tot$type == "kAQP"] <- Conds.tot$y[Conds.tot$type == "kAQP"]/conv_kr
# Conds.tot$y[Conds.tot$type == "kx"]   <- Conds.tot$y[Conds.tot$type == "kx"]/conv_kx

# ============================================================================ #
p <- ggplot(Conds.tot) +
  geom_line(aes(x = age, y = y, color = S_ID),
            size = 1,
            alpha = 0.5) +
  scale_color_manual(values = S_colors) +
  facet_grid(type~S_ID, scales = "free") +
  theme_test()

p
svg(filename = "./plots/Mutant_Conds.svg", width = 7, height = 5)
p
dev.off()
# ============================================================================ #
# Add root types
roottypes <- tibble(order_id = c(1, 2),
                    order    = c("Taproot", "Lateral"))

Conds.tot <- merge(Conds.tot, roottypes)
```

# LOOP MPIPE

So we want to loop MARSHAL for each S_ID of Conds.tot

```{r, include = F}
source("./src/CRB-MARSHAL/CRBM_functions.R")

# ============================================================================ #
# DEFINE SIMULATIONS MACRO PARAMETERS
tmin          <- 10
tmax          <- 60
it_length     <- 10
S_list        <- unique(Conds.tot$S_ID)
gif.delay     <- 50
radius.range  <- c(0.75, 2)
# SG_timing     <- c(7, 25)
# ============================================================================ #

# LOAD RSA FILES AND CREATE A META FILE
RSA_list      <- unique(RSA.IDs$RSA_id)
RSA.all       <- read.csv("./src/CRB-MARSHAL/inputs/RSA_all.csv") %>% 
  filter(RSA_id %in% RSA_list & time <= tmax)

# RSA_plot <- ggplot(RSA.all %>% filter(time <= tmax)) +
#   geom_segment(aes(x = x1, xend = x2, 
#                    y = z1, yend = z2, 
#                    color = branchID)
#                ) +
#   facet_wrap(~RSA_id, nrow = 2) +
#   scale_color_viridis(option = "plasma") +
#   coord_fixed() +
#   theme_few()
# 
# RSA_plot

# ============================================================================ #
# RUN MPIPE FOR EVERY SCENARIO
for(S_ID_i in S_list){

  Scenario_ID_i  <- S_ID_i
  # print(Scenario_ID_i)
  
  Conds          <- Conds.tot %>% filter(S_ID == S_ID_i)
  Conds$x        <- Conds$age
  
  SG_timing      <- mparams$SG_timing[mparams$S_ID == S_ID_i]
  MS_timing      <- mparams$MS_timing[mparams$S_ID == S_ID_i]
  rmin           <- min(Conds$y[Conds$type == "radius"])
  rmax           <- max(Conds$y[Conds$type == "radius"])
  
  path.out       <- paste0(path.results, S_ID_i, "/")
  
  S_ID           <- S_ID_i
  
  # UNLEASH MARSHAL PIPELINE !
  source("./src/MPIPE.R")
}
```

# PROCESS RESULTS

## Load all files and create a Macro table

```{r}
# ============================================================================ #
# PROCESS RESULTS
# ============================================================================ #
Macro_full <- tibble()
RSHA_full  <- tibble()
S_list     <- c("WT", "kAQP", "Sub", "SubSG")

for(si in S_list){
  print(si)
  
  temp_path              <- paste0(path.results, si, "/")
  
  temp_Macro             <- read.csv(paste0(temp_path, "Macro_all.csv"))
  temp_Macro$Scenario_ID <- si
  Macro_full             <- rbind(Macro_full, temp_Macro)
  
  temp_RSHA              <- read.csv(paste0(temp_path, "RSHA_all.csv"))
  temp_RSHA$Scenario_ID  <- si
  RSHA_full              <- rbind(RSHA_full, temp_RSHA)
}

Macro_full <- Macro_full %>% 
  mutate(Sim_ID = paste0(RSA_id, "_", Scenario_ID)) 

write.csv(x = RSHA_full, file = paste0(path.results, "RSHA_full.csv"), row.names = F)
write.csv(x = Macro_full, file = paste0(path.results, "Macro_full.csv"), row.names = F)
```

# LOAD AND ANALYSE RESULTS

## Load directly RSHA_full and Macro_full

```{r}
RSHA_full  <- read.csv(paste0(path.results, "RSHA_full.csv")) %>% 
  mutate(Scenario_ID = factor(Scenario_ID, 
                              levels = c("WT", "kAQP", "Sub", "SubSG")))

Macro_full <- read.csv(paste0(path.results, "Macro_full.csv")) %>% 
  mutate(Scenario_ID = factor(Scenario_ID, 
                              levels = c("WT", "kAQP", "Sub", "SubSG")))
```

A nice plot of k_r

```{r}
data2export <- RSHA_full %>% 
  filter(age == max(RSHA_full$age) & Scenario_ID == "WT")

data2export <- data2export[c("node1ID",
                             "node2ID",
                             "branchID",
                             "x1","y1","z1","x2","y2","z2",
                             "radius","length","R","G","B", "age",
                             "time","type","RSA_id","kr","kx","SUF")]

write.csv(x = data2export, file = "src/CRB-MARSHAL/RSHA_WT_30d_export.csv", row.names = F)

data2export <- read.csv("src/CRB-MARSHAL/RSHA_WT_30d_export.csv")

p <- ggplot(data2export) +
  
  geom_segment(aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = kr, 
                   size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2export$radius), 
                                   max(data2export$radius))) +
  
  scale_color_viridis_c(breaks = c(min(data2export$kr),max(data2export$kr)),
                        labels = c("low", "high"),
                        direction = 1
                        # , limits = c(0, max(RSHA.all$SUF[RSHA.all$RSA_id == RSA_id_i]))
                        ) +
  
  facet_wrap(~ RSA_id, nrow = 2) +
  coord_fixed() +
  theme_test() 

p

ggsave(filename = paste0(path.plots, "data2export_plot.png"),
       device = "png", plot = p, dpi = 300, width = 10, height = 7)
```

## Krs

### Boxplot 

```{r}
# ============================================================================ #
# ANALYSE KRS
# ============================================================================ #
data2plot <- Macro_full %>% 
  filter(age %in% c(10, 20, 30, 40, 50, 60)) 

p <- ggplot(data2plot) +
  
  geom_line(aes(x     = as.factor(age), 
                y     = Krs, 
                group = Sim_ID,
                color = Scenario_ID
                # linetype = Scenario_ID
                ),
            # color = "black",
            alpha = 0.2) +
  
  geom_boxplot(aes(x    = as.factor(age),
                   y    = Krs,
                   fill = Scenario_ID
                   ),
               # fill = "#0070C0",
               width = 0.5,
               outlier.shape = NA)+
  
  scale_fill_manual(values = S_colors) +
  scale_color_manual(values = S_colors) +
  
  xlab("Age [d]") +
  ylab(expr(K[rs] ~ "[" ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]"))     +
  theme_few()


p

# ggsave(filename = paste0(path.plots, "Krs_full.svg"), 
#        plot = p
#        ,device = "svg"
#        ,width = 5, height = 3)

svg(filename = paste0(path.plots, "Krs_full.svg"), 
    width = 5, height = 3)
p
dev.off()

# ============================================================================ #

PD <- 2

data2plot2 <- data2plot %>% 
  group_by(age, Scenario_ID) %>% 
  summarise(Krs_mean = mean(Krs),
            Krs_sd   = sd(Krs)
            )
  
p2 <- ggplot(data2plot2) +
  
  geom_point(aes(x     = age, 
                 y     = Krs_mean,
                 color = Scenario_ID
                ),
             position = position_dodge(width = PD),
             alpha = 1) +
  
  geom_line(aes(x     = age, 
                y     = Krs_mean,
                color = Scenario_ID
                ),
            position = position_dodge(width = PD),
            alpha = 1) +
  
  geom_errorbar(aes(x = age, 
                    ymin = Krs_mean - Krs_sd,
                    ymax = Krs_mean + Krs_sd,
                    color = Scenario_ID),
                position = position_dodge(width = PD),
                width = 1
                ) +
  
  scale_fill_manual(values = S_colors) +
  scale_color_manual(values = S_colors) +
  
  xlab("Age [d]") +
  ylab(expr(K[rs] ~ "[" ~ m^{3} ~ MPa^{-1} ~ s^{-1} ~ "]"))     +
  theme_few()


p2
svg(filename = paste0(path.plots, "Krs_full_2.svg"), 
    width = 4, height = 2)
p2
dev.off()
```

### Statistics

Here, for each RSA age, we conduct a linear model to investigate the effect of the scenario on K_rs

```{r}
ages <- c(10, 20, 30, 60)

for(age_i in c(30, 60)){
  cat("================= \n")
  cat("Age = ", age_i, "\n")
  cat("================= \n")
  temp_df <- Macro_full %>% 
    filter(age == age_i)
    
  temp_lm <- lm(temp_df, formula = Krs ~ Scenario_ID)
  # plot(temp_lm)
  pander(summary(temp_lm))
  
  e <- as_tibble(emmeans(temp_lm, ~Scenario_ID))
  
  # print(e)
  
  mean_WT    <- e$emmean[e$Scenario_ID == "WT"]
  mean_SubSG <- e$emmean[e$Scenario_ID == "SubSG"]
  diff       <- (mean_WT - mean_SubSG)*100/mean_WT
  
  cat("==>> Krs : SubSG shows a reduction of ", diff, " % compared to WT \n \n")
  
  # anova(temp_lm)
}
```

make a LM with Scenario_ID and age

NB : We checked the normalization by lookind at the QQplot of the residuals of the fit.
Despite having outliers, most of the data is normal and good.

```{r}
data2stat   <- Macro_full %>% 
  filter(age >= 20)

# CHECK NORMALITY -> to implement for each group !
# par(mfrow = c(1, 2))
# qqnorm(data2stat$Krs)
# qqline(data2stat$Krs)
# hist(data2stat$Krs)  
# shapiro.test(data2stat$Krs)

# ============================================================================ #
# 1. LINEAR MODEL OF DIRECT K_RS
Krs_lm_full1 <- lm(data = data2stat, 
                   formula = Krs ~ Scenario_ID + age + age:Scenario_ID
                   )

par(mfrow = c(2,2))
plot(Krs_lm_full1)[1]
summary(Krs_lm_full1)

data2stat$Krs_pred <- predict(Krs_lm_full1, data2stat)
p1 <- ggplot(data2stat) +
  geom_point(aes(x = age,
                 y = Krs,
                 color = Scenario_ID),
             position = position_dodge(4)
             ) +
  geom_line(aes(x = age, 
                y = Krs_pred,
                color = Scenario_ID),
             # shape = 2,
             position = position_dodge(4)) +
  # geom_smooth(method = "lm") +
  scale_color_manual(values = S_colors)+
  theme_few()
p1

# Choose wich plot to export
svg(filename = "./plots/CRB-MARSHAL/Krs_LM_predict.svg", width = 5, height = 4)
p2
dev.off()
```

## SUF

```{r}
# ============================================================================ #
# ANALYSE SUF
# ============================================================================ #
data2plot <- RSHA_full %>% 
  filter(age %in% c(10, 30, 60)) 

SUF_df <- data2plot %>% 
  # filter(age >= 30) %>%
  select(c("SUF", "RSHA_id", "age", "Scenario_ID", "z1", "type")) %>% 
  mutate(zr = round(z1/2.5, digits = 0)*2.5) %>% 
  group_by(RSHA_id, zr, Scenario_ID, age) %>% 
  summarise(SUF_sum = sum(SUF)) %>% 
  ungroup() %>% 
  group_by(zr, Scenario_ID, age) %>% 
  summarise(SUF_sum_mean = mean(SUF_sum),
            SUF_sum_sd   = sd(SUF_sum)
            )

SUF_plot <- ggplot(data = SUF_df) +
    
  # geom_bar(aes(x = zr, y = SUF_sum_mean, fill = Scenario_ID),
  #          stat = "identity", 
  #          position = "dodge", 
  #          alpha = 0.75) +

  # geom_ribbon(aes(x = zr
  #                 ,ymin = SUF_sum_mean-SUF_sum_sd
  #                 ,ymax = SUF_sum_mean+SUF_sum_sd
  #                 ,fill = Scenario_ID),
  #             alpha = 0.5
  #               ) +
  
  geom_point(aes(x = zr
                 ,y = SUF_sum_mean
                 ,color = Scenario_ID
                 # ,shape = Scenario_ID
                 )
             # ,position = position_dodge(0.5)
             ,size = 1
             ) +

  geom_errorbar(aes(x = zr
                    ,ymin = SUF_sum_mean-SUF_sum_sd
                    ,ymax = SUF_sum_mean+SUF_sum_sd
                    ,color = Scenario_ID
                    )
                ,width = 0.4
                ,size = 0.3
                ,alpha = 0.5
                # ,position = position_dodge(0.5)
                ) +
  
  geom_line(aes(x = zr
                ,y = SUF_sum_mean
                ,color = Scenario_ID
                # ,linetype = Scenario_ID
                )
            # ,position = position_dodge(0.5)
            # ,size = 1
            ) +
  
  scale_color_manual(values = S_colors) +
  # scale_fill_manual(values = S_colors) +
  # scale_fill_viridis(discrete = T) +

  ylab("Standart Uptake Fractions [-]") +
  xlab("depth [cm]") +
  
  facet_wrap(~age, 
             scales = "free_x",
             nrow = 1) +
  coord_flip() +
  # ggtitle(paste0("Sum of SUF per scenario")) +
  theme_few() +
  theme(axis.text.x  = element_text(size = 8, angle = 90, hjust = 1, vjust = 0.5)) +
  theme(legend.position = "none")
  
SUF_plot

# ggsave(filename = paste0(path.plots, "SUF_sum_full.svg"), 
#        plot = SUF_plot, 
#        device = "svg", width = 5, height = 5)

svg(filename = paste0(path.plots, "SUF_sum_full.svg"), 
    width = 4, height = 4)
SUF_plot
dev.off()
```

### Statistics

```{r}
for(age_i in unique(SUF_df$age[order(SUF_df$age)])){
  
  cat("================= \n")
  cat("Age = ", age_i, "\n")
  cat("================= \n")
  
  temp_SUF   <- SUF_df %>% filter(age == age_i)
  p <- ggplot(temp_SUF) +
    geom_point(aes(x = zr, y = SUF_sum_mean, color = Scenario_ID)) +
    geom_line(aes(x = zr, y = SUF_sum_mean, color = Scenario_ID)) +
    geom_errorbar(aes(x = zr, 
                      ymin = SUF_sum_mean-SUF_sum_sd, 
                      ymax = SUF_sum_mean+SUF_sum_sd,
                      color = Scenario_ID)
                  
                  ) +
    theme_bw()
  
  plot(p)
  
  distrib_WT     <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "WT"]
  distrib_kAQP   <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "kAQP"]
  distrib_Sub    <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "Sub"]
  distrib_SubSG  <- temp_SUF$SUF_sum_mean[temp_SUF$Scenario_ID == "SubSG"]
  
  # plot(distrib_WT)
  # plot(distrib_SubSG)
  
  ks_test    <- ks.test(distrib_WT, distrib_SubSG)
  print(ks_test)
}
```

Okey so now we can run a t.test for every soil layer 

At 30 days old

```{r}
data2stat <- data2plot %>% 
  # filter(age >= 30) %>%
  select(c("SUF", "RSHA_id", "age", "Scenario_ID", "z1", "type")) %>% 
  mutate(zr = round(z1/2, digits = 0)*2) %>% 
  group_by(RSHA_id, Scenario_ID, age, zr) %>% 
  summarise(SUF_sum = sum(SUF)) %>% 
  filter(age == 30)

for(zr_i in unique(data2stat$zr)[order(unique(data2stat$zr))]){
  
  cat("==================================================== \n")
  cat("zr = ", zr_i, "\n")
  cat("==================================================== \n")
  
  temp_df <- data2stat %>% filter(zr == zr_i)
    
  temp_lm <- lm(temp_df, formula = SUF_sum ~ Scenario_ID)
  # plot(temp_lm)
  pander(summary(temp_lm))
  
  e <- emmeans(temp_lm, specs = ~ Scenario_ID)
  print(e)
  means     <- as_tibble(e)
  
  mean_WT    <- means$emmean[means$Scenario_ID == "WT"]
  mean_SubSG <- means$emmean[means$Scenario_ID == "SubSG"]
  diff       <- (mean_SubSG - mean_WT)*100/mean_WT
  
  cat("SubSG is ", diff, " % higher than WT \n")
  
  # anova(temp_lm)
}
```

And the same for 60 days old

```{r}
data2stat <- data2plot %>% 
  # filter(age >= 30) %>%
  select(c("SUF", "RSHA_id", "age", "Scenario_ID", "z1", "type")) %>% 
  mutate(zr = round(z1/2, digits = 0)*2) %>% 
  group_by(RSHA_id, Scenario_ID, age, zr) %>% 
  summarise(SUF_sum = sum(SUF)) %>% 
  filter(age == 60)

for(zr_i in unique(data2stat$zr)[order(unique(data2stat$zr))]){
  
  cat("==================================================== \n")
  cat("zr = ", zr_i, "\n")
  cat("==================================================== \n")
  
  temp_df <- data2stat %>% filter(zr == zr_i)
    
  temp_lm <- lm(temp_df, formula = SUF_sum ~ Scenario_ID)
  # plot(temp_lm)
  pander(summary(temp_lm))
  
  e <- emmeans(temp_lm, specs = ~ Scenario_ID)
  # print(e)
  means     <- as_tibble(e)
  
  mean_WT    <- means$emmean[means$Scenario_ID == "WT"]
  mean_SubSG <- means$emmean[means$Scenario_ID == "SubSG"]
  diff       <- (mean_SubSG - mean_WT)*100/mean_WT
  
  cat("==>> SubSG is ", diff, " % higher than WT \n")
  
  # anova(temp_lm)
}
```



# OTHER PLOTS

## Select only one to make a figure

### Plot SUF

```{r}
age_i <- 60

data2plot <- RSHA_full %>% 
  filter(age == age_i & RSA_id == unique(RSA.IDs$RSA_id[1]) & Scenario_ID == "WT")

p <- ggplot() +
  
  # geom_segment(data = data2plot_main,
  #              aes(x = x1, xend = x2,
  #                  y = z1, yend = z2,
  #                  size = radius),
  #              color = "blue") +  
  
  geom_segment(data = data2plot,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = SUF, size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2plot$radius), 
                                   max(data2plot$radius))) +
  
  scale_color_viridis(option = "magma",
                      breaks = c(min(data2plot$SUF),
                                 max(data2plot$SUF)
                                 ),
                      labels = c("low", "high"),
                      direction = 1
                      # , limits = c(min(data2plot$SUF), max(data2plot$SUF))
                      ) +
  
  # facet_wrap(~ Scenario_ID, nrow = 1) +
  coord_fixed() +
  theme_void() 

p

ggsave(filename = paste0("RSHA_suf_example_", age_i, ".png"), plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 4, height = 4)
```

### Plot kr

```{r}
data2plot <- RSHA_full %>% 
  filter(age == 60 & RSA_id == unique(RSA.IDs$RSA_id[1]) & Scenario_ID == "WT")

p <- ggplot() +
  
  geom_segment(data = data2plot,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = kr, 
                   size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2plot$radius), 
                                   max(data2plot$radius))) +
  
  scale_color_viridis_c(breaks = c(min(data2plot$kr),max(data2plot$kr)),
                        labels = c("low", "high"),
                        direction = 1
                        # , limits = c(0, max(RSHA.all$SUF[RSHA.all$RSA_id == RSA_id_i]))
                        ) +
  
  # facet_wrap(~ Scenario_ID, nrow = 1) +
  coord_fixed() +
  theme_void() 

p

ggsave(filename = "RSHA_kr_example.png", plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 4, height = 4)
```

### kx

```{r}
data2plot <- RSHA_full %>% 
  filter(age == 60 & RSA_id == unique(RSA.IDs$RSA_id[1]) & Scenario_ID == "WT")

p <- ggplot() +
  
  geom_segment(data = data2plot,
               aes(x = x1, xend = x2,
                   y = z1, yend = z2,
                   color = kx, 
                   size = radius)) +
  
  scale_size_continuous(range = c(0.5, 1), 
                        limits = c(min(data2plot$radius), 
                                   max(data2plot$radius))) +
  
  scale_color_viridis_c(breaks = c(min(data2plot$kx),max(data2plot$kx)),
                        labels = c("low", "high"),
                        direction = 1
                        # , limits = c(0, max(RSHA.all$SUF[RSHA.all$RSA_id == RSA_id_i]))
                        ) +
  
  # facet_wrap(~ Scenario_ID, nrow = 1) +
  coord_fixed() +
  theme_void() 

p

ggsave(filename = "RSHA_kx_example.png", plot = p
       ,device = "png"
       ,path = path.plots
       ,width = 4, height = 4)
```


